
% Chapter 1
\fancychapter{26 August}{Remus Lupin’s life changed on a Wednesday, of all days.
}

REMUS LUPIN’S LIFE CHANGED ON A WEDNESDAY, of all days.

By all accounts, it should have changed on a Monday; that’s when he’d originally planned to return to work after his short summer holiday. He’d been visiting his father, Lyall, in his Welsh hometown and had only intended to stay for a three-day weekend. As Sunday came and went, though, things kept cropping up that delayed Remus’s departure: the internet connection needed fixing, some fencing around the garden needed replacing, an oversized play tower Lyall bought for the cats had to be hauled out of the boot of his car and assembled...it went on like that for ages. Every day, Remus would declare half-heartedly that he really had to get back to work, but he was secretly glad to have excuses to spend more time with his father. He only got back home a few times a year, busy as he was, and knew the missing was mutual.

So it was Wednesday when Remus gave Lyall a long hug goodbye on a platform at Cardiff Central before catching an early morning train back to London. He had just enough time to stop home, change, and sort out his mail before hopping on his bike and heading into work.
The first thing he noticed was the paint job.

Remus locked up his bike in its usual place on a rack that stood a few meters from his shop’s front doors. He was adjusting his rucksack on his shoulder when he looked up at the building next door to his and stopped, staring curiously. When he’d left last week, the brick facade had been painted an off-white; not unattractive, although years of neglect on the upkeep followed by nearly a full year of abandonment had left it cracked and peeling in places. It had received a makeover in Remus’s absence, now painted a slate gray that gave the place new life. It had also gotten a new sign; white with red bordering, and bold, black letters spelling out BLACK DOG TATTOOS.

His own shop, Fedelius Flowers, looked the same as he’d left it, with its pale yellow paint and assortment of blooming plants in window boxes and terra cotta pots. A bell jingled softly as he pushed open the door. Alerted by the noise, a young woman looked up from the thick textbook she had cracked open on the front counter next to the register. “Wotcher, Remus,” she said with a smile. “Welcome back. As you can see, I haven’t burned the place down.”

“Hello, Alice,” Remus replied, grinning back. “I didn’t doubt you for a moment. What’d I miss? The delivery for the Dearborn wedding went off alright?”

Alice filled him in on the events of the past six days; the wedding delivery had indeed gone smoothly, and they’d received a thank-you note and a generous tip from the mother of the bride for fulfilling their order on such short notice. The rest of the week had been business as usual. August was a steady but not overly busy time for the shop, with the occasional wedding or engagement party supplementing their regular orders, such as the small arrangements they did for meetings of the local garden club, historical society and woman’s club.

After he’d gotten caught up on news, Remus made his way to his tiny back office, putting an ancient kettle on a hotplate as his official first order of business for the week. Sorting through his desk, he noticed Alice had been keeping up with the shop’s emails and had jotted down any phone calls he’d missed with name, date, time and reason for calling. Bless that Alice Longbottom, he thought as he steeped tea for them in a pair of mugs. Remus didn’t know what he’d do without the help of his sole full-time employee.
Reemerging in the front of the shop, Remus leaned a hip on the edge of the front counter and passed one of the drinks to Alice. “So, I’ve noticed we have new neighbors next door,” he said before taking a sip of his own.

“Oh my god, that’s right, you missed it!” Alice said in a rush, setting down the mug she’d raised halfway to her mouth as Remus was talking. Her blue eyes sparkled with excitement. “Have you had a look at the owners?”

“Er...no,” Remus said, a questioning lilt at the end of the word. Alice clearly had something she wanted to say about them, whoever they were. “But I saw the building. Are they open already?” Before he’d left, the only indication they’d had that the place would soon have tenants was the removal of the “To Let” sign. Remus was surprised and more than a little impressed at how much work had been done in just six days; the exterior looked like new, and the inside looked at least partially set up, from the brief glance he’d taken through the tall front windows.

“I don’t think they’re fully up and running, no; they’ve still got workers coming and going,” Alice replied. “They showed up literally the morning after you left.” She paused, leaning in conspiratorially. “You’re going to want to go over there, Remus. The people who own the place are famous.”

“Famous tattoo artists?” Remus asked, quirking an eyebrow. He couldn’t think of many.

Alice pulled out her mobile from the pocket of her linen jumpsuit, tapping quickly with the hand not holding her tea. “Instagram-famous, at least. Look!” She turned her phone around and Remus peered down at Black Dog Tattoos’ Instagram feed. Scanning the screen, he learned that they had a few hundred posts already of various finished pieces, shot as closeups without clients’ faces—not a new business, then, Remus thought. The most interesting bit was their follower count: 2.7 million. He also noticed their bio included a line about having just moved to a new location.

“Right, well, they’ve got us beat,” Remus said, looking back up from the screen to Alice. “Why move here, though? I mean, it’s a nice area, but...doesn’t seem like the ideal location for a tattoo shop.” Fedelius Flowers was one of only a few businesses on that particular avenue in Maida Vale. The quiet, affluent residential district was characterized by its leaf-lined streets, trendy cafes and a picturesque canalside. Most of Remus’s clients were community-minded retirees and well-to-do families that looked like they’d stepped out of a Pottery Barn catalog. It didn’t seem to him the right demographic for the services offered next door.

Alice shrugged, tucking her phone back into her pocket and wrapping both hands around her warm mug. “Seems like they have enough of a following to move just about anywhere,” she said. Then she threw Remus a smirk, waggling her eyebrows. “Besides, you know the grannies that come in here are cheekier than they look.”

“You’re right,” Remus mused, grinning. “Maybe Mrs. Gadsby will be first in line!”

“Oh, she would do, yeah, definitely,” Alice laughed before leaning forward again in that same conspiratorial manner. “But Remus. Remus. They aren’t just famous; they’re gorgeous.”

“Oh? What, you’ve been checking them out through the windows all creeper-like?” Remus teased.

“Duh,” Alice replied, unruffled. “Frank spotted them, too, when he was picking up for the Dearborn wedding on Saturday. He fully agrees.” She was referring to her husband, a nursery school teacher who also worked as part-time driver for Remus, handling the larger deliveries. “It’s a man and a woman; they could be married, but they sort of look related. Both of them look like supermodels, but like...punk-rock supermodels.” She gave Remus a pointed look. “The guy is absurdly hot, Remus. You should say hi.”

Remus laughed, shaking his head. “Well, I’ll be saying hi regardless. They’re new neighbors, it’s the polite thing to do.”

“You know what would be even more polite? Taking your ‘new neighbor’ to dinner,” Alice said with a carefully schooled expression of innocence. With her short stature, round eyes, playful pixie cut and a face that looked younger than a 28-year-old’s, it was almost believable. But then she winked.

“Christ, you’re shameless.”

“I’m telling you! One look at him and you’ll be agreeing with me, too.”

“I’ll be sure and wear my best dress,” Remus deadpanned before tapping his finger on the open textbook between them. “Now tell me how exam prep is going. Do I need to supplement your tea with espresso?”

The rest of the day was unexpectedly busy and Remus, who’d shown up already tired from the early train ride, was grateful when four o’clock rolled around and it was time to close. He left ten minutes after Alice did, locking the door behind him and slinging his rucksack over his shoulder before cycling home. Instead of relaxing once he’d arrived back at his rented studio flat, though, Remus headed to the kitchen to throw a batch of brownies together. Remus was an excellent baker and had a massive sweet tooth; it came as no surprise that he had all the ingredients he needed even after being away for nearly a full week. An hour later, he was wrapping up the brownies for transport (after eating one himself—for quality control, of course).

He checked his reflection in the bathroom mirror before leaving to make sure he wasn’t covered in flour or cocoa powder. Despite the warm summer weather, he had on a cream-colored jumper, tan trousers rolled at the ankles and boots. He ran a hand through his soft brown hair to tame some of the wilder curls. His eyes inevitably found the long, white scar that cut diagonally over the freckles across his nose and right cheek and he frowned at it, pulling back to look himself over from head to foot and shrugging when he decided he was presentable enough to meet the new business owners.

It was nearing six when Remus arrived back in front of Black Dog Tattoos, but the lights were still on and there was movement inside. Remus opened the door with one hand, carrying the package of brownies in the other, and found himself in a waiting room with a main reception desk, two sofas, a handful of chairs and a long, wood-and-metal coffee table with a stack of binders on it. The furniture was modern with an industrial flair; the room nicely lit and spotless. The exposed brick walls housed tons of artwork, from black-and-white photographs and modern paintings to the rows and rows of tattoo sketches which showcased more styles than Remus had known existed. He could see several private rooms straight back behind the front desk. The Kinks were playing over the sound system. It sort of felt like someone’s very cool flat, and Remus liked how inviting it was.

He was still looking around when one of the most striking people he’d ever encountered walked up from one of the back rooms. “Hi there. We’re not open just yet, love,” she said with an apologetic smile. Alice had not been exaggerating when she’d described this woman. Sleek black hair tumbled all the way down to her waist, punctuated by a few streaks of silver. Her dark brows arched elegantly above almond-shaped brown eyes, a slightly pointed nose and high cheekbones. Her makeup was flawless, from her plum lipstick to her winged eyeliner. She looked like royalty. If not for her piercings (small, black gauges in her ears, studs through her left brow and a ring through her bottom lip) and outfit (a form-fitting, ribbed black tank top, high-waisted trousers with a black and white striped pattern and black heels), Remus thought she could have been pulled from a dinner scene in Downton Abbey.

“Oh, no—I’m not here for an appointment, actually,” Remus replied, turning to face her fully. “My name’s Remus, I own the flower shop next door. I wanted to welcome you to the street.” He held the brownies out in front of him.

“Oh!” Her eyes lit up and her smile lost its sympathetic slant. “That’s very sweet of you, thanks. Andromeda Black.” She extended a hand. “I’m co-owner. Nice to meet you, Remus.”

“Likewise,” Remus said with a smile, handing the brownies over. “I would have come over sooner, but I’d just gone on holiday the day before you moved in.”

Andromeda waved away the implied apology, setting the brownies down on the front counter and oohing over them appreciatively. “I’m just happy you came in at all. I think most of the neighbors are scared of us.”

Remus laughed a bit at that. “Well, they’re not as prudish as you might think.” Andromeda raised an eyebrow. “Okay, maybe they are, but it’s a nice neighborhood. They’ll come ‘round.”

“I hope so,” she said, breaking off a bite-sized piece of brownie and popping it in her mouth. “Oh no, these are way too good! You’re a very dangerous person to work next door to.”

“That’s what they call me, yeah. Remus Lupin: Very Dangerous Florist.”

She returned his grin. “You said you’re the owner? You look like you’re barely out of uni.”

“Not quite. Just turned thirty in the spring. But I’ve run the shop for about six years now, so basically since I was just out of school, yeah.”

“That’s fucking impressive,” Andromeda said. “My cousin Sirius—he’s co-owner with me—he’s the same age as you. It takes a lot of nerve and a lot of hustle.”

Cousins, Remus thought. So they were related, not a couple, like Alice had guessed. “I’m sort of married to the place at this point,” he said with a laugh and nod of agreement. “We’re open six days a week, 8-4. Sundays are my off day. I have one full-timer and some part-time help but, yeah, it’s a lot of work.” He paused, gesturing to the tattoos on the wall. “Are these yours?”

“Oh, no,” Andromeda said, looking over at them for a moment then back at Remus. “Sirius is the artist. This whole place was his vision, really. But he’s shit at the business side of things, so I make sure bills are paid and appointments are set up and all. I do the piercings, too.”

Remus opened his mouth to reply but at that moment, they were joined in the front room by Sirius himself. And, oh. Alice was very, very accurate in her description of him, too. He stood about a head shorter than Remus (not a big surprise there; Remus was six foot two) and was obviously quite fit under his leather jacket, well-worn Sex Pistols t-shirt and jeans that hugged his lower half in ways that were borderline inappropriate. He was also wearing heavy, black motorcycle boots that should have looked ridiculous but somehow worked. Black hair fell in carelessly gorgeous waves to his shoulders—sex hair, Remus’s brain unhelpfully supplied—and he had the same aristocratic bone structure as Andromeda. His jaw was more defined, though, more masculine, with just a hint of five o’clock shadow. The most striking difference between them was his eyes; instead of Andromeda’s brown, they were gray, just a few shades lighter than the paint they’d used on the building. Those eyes flicked from Andromeda to Remus, who took what he hoped was a subtle, steadying breath.

“Speak of the devil,” Andromeda said, glancing between them. “Sirius, this is Remus Lupin. He owns the flower shop next door and came to say hello. With baked goods, I might add.”

“Yeah? Well, you’re officially my favorite neighbor, Remus Lupin,” Sirius said with a devastating smirk, offering a hand. Remus could see the hint of a dragon’s tail peeking out from the sleeve of his jacket and tried very hard not to imagine how many tattoos Sirius had, and where.

“That’s all it takes, huh? I should’ve brought some to my landlord’s when I was late with the rent,” Remus replied, shaking his outstretched hand for perhaps a second longer than was absolutely necessary.

Sirius’s smirk widened into an even more devastating smile. “Booze also does the trick, in my experience.” He walked over to the counter, pilfered half a brownie from the tray and popped it in his mouth while dodging a swat from Andromeda with an easy, loping grace. “I take it back,” he said after swallowing, looking at Remus with raised eyebrows. “Sod the booze. These are heaven.”

Remus laughed, warmed by the praise. “My landlord’s sort of a dick, but I’ll try it next time.”

“Live around here, then?” Sirius asked, propping an elbow on the counter.

“Mhm. Studio flat, about ten minutes away by bike. It took ages to find; rent is insane around here.” Remus always joked it was the smallest piece of property in Maida Vale, but it was worth not having to take the Tube or a taxi to work in the morning.

“You’re telling me,” Sirius agreed. “But I was already paying out my arse in Soho, so when we moved the shop here, I moved upstairs.” He pointed to the ceiling. “Bit small, but it’s got a decent kitchen and little lounge that’s separate from the bedroom. Andy’s up in Canonbury with an excellent sofa she never lets me crash on.”

“Take it up with your niece; she’s always got friends over. Besides, I see enough of your ugly mug at work,” Andromeda said, grabbing her purse and the brownies before Sirius could do more than shout in protest and snatch one or two as she passed by him. “Right lads, Canonbury calls. Don’t be a stranger, Remus!”

“Fucking thief!” Sirius said in lieu of goodbye as the door closed behind her. He grinned at Remus again, taking him in with those gray eyes. “So. As a local expert, can you tell me where I can find decent takeaway? The deli on the corner is shit.”

He didn’t know when it happened, but Remus found himself sat in one of the chairs across from Sirius, who was leaning back in his own with a foot resting on his opposite knee and listening. Remus told him about his favorite chip shop, the best places for curry, Chinese and pizza and where to find the cheapest beer. Sirius was easy to talk to; Remus almost felt like they’d already been friends for a while with their comfortable banter. He was also quite literally the most gorgeous man Remus had ever laid eyes on, but that was just an added bonus. He was sure Sirius had a significant other who was probably just as unreasonably attractive.

The sun began to set outside the windows of the shop, catching Remus’s attention. “I’ve probably kept you too long,” he said, getting to his feet reluctantly. Sirius didn’t seem to be in any hurry, either, standing slowly and stretching his arms above his head as he gave a huge yawn. He glowed in the golden evening light; Remus was reminded of a lion getting ready to sleep in the warm savannah.

“Bloody knackered from the week,” he said, rolling his shoulders a bit. “Andy’s a slave driver. But I want to get up and running, too. Monday, I think.”

Remus nodded, a mental image of Sirius hauling boxes in nothing but his tight jeans and t-shirt dancing through his mind, unbidden. “The place looks great, really,” he said with a smile. “And anything you need, just pop over. I’m in around 7:30 every day except Sundays.”

“I’ll take you up on that,” Sirius replied, and was Remus imagining things or was his (already sexy) voice just a tiny bit lower as he said it? Remus made his way to the front door, Sirius hanging back a bit.

“Hey,” Sirius said suddenly as Remus put a hand on the door handle. Remus turned back around and was met with a playful grin. “I thought of something I need.”

“Oh?” Remus swallowed hard.

“Yep. I had this really badass cactus for the front counter—tall and pointy with red flowers on—but it was a casualty of the move. And now that I know a plant guru…”

Remus’s heart skipped. “I have some like that, yeah. Never heard anyone call a cactus ‘badass’ before, though, I’ve got to tell you.”
“But I’m not wrong,” Sirius said, grin widening. “I’ll come by tomorrow, then?”

“Sure.” Remus grinned wryly. “You can discuss the badassery of various plantlife with all the little old church ladies.”

“Sounds like an excellent use of time. See you, Remus.”

“Goodnight, Sirius.”

Remus didn’t even mind cycling home in the dark. He dreamt of dragons and bright gray eyes.

\newpage

%Chapter 2 
\fancychapter{27 August}{Sirius makes a visit next door; Remus goes to the pub.
}
SIRIUS WAS TRUE TO HIS WORD; he came strolling into Fedelius Flowers the next day around lunchtime. The late August heat was stronger than the day before, and he was sans leather jacket—this time wearing a black v-neck t-shirt and ripped, light-wash jeans—but he still had on the clunky motorcycle boots. His hair was tied up in a loose bun, a few loose strands framing his face in a carelessly perfect way that should have taken effort but hadn’t at all.

His face lit up when he spotted Remus, and he waved, grinning, as he walked further into the shop. “Hey, Lupin,” he said in greeting. “Ready to help me find an unkillable plant?”

Both Remus and Alice had stopped dead in their tracks at Sirius’s entrance. Remus recovered first, tugging on his light blue button-down shirt in an attempt to smooth it out and meeting him halfway in the middle of the shop. “I’ll do my best,” he said, returning Sirius’s grin. He felt Alice’s eyes boring into the back of his skull, and added, “Oh, Sirius, this is Alice Longbottom, my full-time staffer and genuine superhero. Alice, this is Sirius Black. He owns next door with his cousin, Andromeda.”

Alice set down the pots she was carrying, wiped her hands on the smock she had tied over her sundress and shook Sirius’s. “Nice to meet you,” she said emphatically.

“Pleasure’s mine,” Sirius said, smiling warmly as he took her hand. He looked around at the different display tables and shelves before commenting, “It smells amazing in here.”

“Usually does, yeah,” Alice agreed. “It’s especially nice right now because we’ve got a load of jasmine arrangements packed up by the door there for delivery...and here’s our driver, hey, goodlookin’!”

A man about the same age as the three of them—looking a bit disheveled with shaggy brown hair and a beard just this side of scruffy, but with a handsome, kind face—had walked into the shop, saying hello to Remus and giving Alice a kiss on the cheek.

“My husband, Frank,” she explained to Sirius. “This is Sirius, he’s our new neighbor.”

“Hey, mate,” Frank said with a friendly handshake. “About time someone moved into that building. Beautiful old place, tenants never took care of it properly.”

“Come have a look ‘round whenever you want,” Sirius replied. “We saved the original ceiling beams, they look so cool with the brick walls.”

“Oh, really?” Frank’s eyes lit up. “I always said it just needed someone willing to put a little love into it, with an eye for preservation—”

“Alright, don’t start, you’ll be here all day,” Alice said, laughing as she put a hand on his elbow. “Nerd out about architecture later. You’ve got to get those boxes—”

“—Across town, I know,” Frank said with a smile.

“And then you’ve got to pick up—”

“—Neville from his gran’s, yep, I’m on it. Later!” He gave Alice’s hand a squeeze before loading up the boxes for transport and taking them out to the van.

As Sirius turned around to hold the door open for Frank, Alice shot Remus a meaningful look, pointed a thumb at Sirius and mouthed, oh my god. Remus rolled his eyes, mouthing back, stop it, but the tips of his ears were pink.

Once Frank was gone and Alice had reluctantly returned to her work, Remus led Sirius over to their selection of cacti. He’d sort of expected Sirius to just grab one he thought looked cool, but ended up answering a bunch of questions put to him about the differences between plants and what kind of care was involved for them. Sirius settled on a container of three pincushion cacti for the front counter and a rat tail cactus, crowned by its trademark magenta blooms, to hang in a basket by the windows.

“These are brilliant,” Sirius said, grinning hugely, as he brought the plants up to the counter to pay for them. Remus waved him off. “It’s a gift,” he said over Sirius’s protests. “A welcome gift.”

“You already gave me a welcome gift last night,” Sirius pointed out, raising a brow. Remus heard Alice cough into her hand from across the store.

“Okay, yes, but plants are what we do. It’s...like free advertising for me, really, having these in your shop,” Remus said. It was a load of crap and they both knew it, but Sirius just smiled, looking from the plants to Remus’s honey-brown eyes.

“Alright, alright. Thanks, then, Remus,” he said, and god, did it sound good when Sirius said his name like that, Remus thought. “But you’re making me feel like a bloody freeloader. Gonna have to come up with something to give you.”

Alice coughed conspicuously again, and Remus turned his head so only she could see his glare. “Dusty back here!” she said with undisguised glee.

Remus pulled the door open for Sirius, whose arms were now laden with plantlife. “You always this polite?” Sirius said, pausing halfway out the door to look back at Remus with a crooked grin.

“Oh no,” Remus replied. “On my days off I’m usually robbing banks, stealing candy from babies, that sort of thing.”

Sirius’s eyes crinkled as he laughed. “Thought so. Always the ones you least expect. Later, Lupin.”

“Yeah,” Remus said softly as the door to his shop swung shut behind Sirius. “See you.”
Alice’s voice carried from the back of the shop. “Holy shit,” she said, pausing after each syllable.

Remus threw up his hands in mock surrender as he ducked past her to return to cleaning the back office. “Yes, I know, you were right, I need to get back to work!”

Next door, Sirius was faring no better with Andromeda. She was filling out paperwork behind the front counter when she eyed Sirius walking in the door with his new purchases. “Saw something you liked, then?” she said archly.

Sirius set the basket of flowering rat tail by the windows before putting the trio of pincushion cacti down on the counter next to Andromeda with a flourish. “If you’re referring to these cool plants, then yes,” he replied. “Look at that one! It’s meant to be a hanging basket, I’ve got to get a drill, hang on.”

He disappeared to one of the back rooms and Andromeda grinned in amusement as she started filling out forms again. “I meant the handsome bloke selling the plants, actually,” she said without looking up as Sirius reemerged in the front with tools and a stepladder.

“Yeah, well,” Sirius said, trailing off as he put his back to her to get on the ladder and measure from the ceiling. “Impossible not to like him, isn’t it?”

“He’s sweet,” Andromeda agreed, glancing up briefly from her writing and adjusting the tie at the back of her plum-colored halter top. “Funny, too. Fucking tall. I’d ask him out myself if I wasn’t married and he wasn’t throwing an obvious gay vibe.”

Sirius snorted and shook his head, and it seemed he wasn’t going to respond beyond that as he put the measuring tape down and picked up the drill and a hook to hang the basket from. But then he turned his head to the side and muttered, “You think?” before going quickly back to the task at hand.

Andromeda’s smirk widened into a knowing smile as Sirius finished the drilling and picked up the colorful plant. “Oh yeah,” she affirmed. “He’s got the vibe. Definitely.” She paused, writing another sentence before adding, “And he definitely liked the looks of you.”

Sirius gave a soft hum, brow furrowing and tongue peeking out from between his lips in concentration as he hung, adjusted, inspected. When he was satisfied with the placement, he hopped off the ladder and grinned at it proudly, hands on hips. “Home sweet home.” He turned to glance at his cousin as he snapped the ladder shut and tucked it under his arm. “Course he did. I’m fucking gorgeous.”

“Ugh, don’t make me vomit all over these forms, I’ve just spent an hour on them,” she said, throwing a spare pencil at him. “He could be a good match for you, you know? He owns a business, too, he knows what that demands of a person. Unlike the last idiot you dated.”

Sirius sighed, letting his hair down from the bun and running a hand through the loose strands. “Andy…”

“I mean it, Sirius,” Andromeda pressed. “When was the last time you had a relationship that lasted longer than a couple of months?”

“I bring you plants and you repay me by shading me on my dating record?”
“If there were a record for me to shade…”

“Fuck off.” Sirius threw the pencil back at her. “He’s probably that nice to everybody. He’s like the goddamn Lorax over there.”

Andromeda raised a skeptical eyebrow. “Don’t think the Lorax would be keen on killing plants in the name of floral arrangements, really. Did you read that book or just look at the pictures?”

“Bold of you to assume I learned how to read,” Sirius joked as his cousin rolled her eyes. “And you’re a bloody menace. I really don’t know if you’re actually trying to set me up with Remus or if you want to date him vicariously through me.” He paused, thinking. “Hey, if you walk out on your family to have a torrid affair with him, do I get to keep Ted? He’s just so dreamy.”

“Your crush on my husband remains one of the most sensible things about you,” Andromeda said before a delivery driver walked in and they settled back into tackling their long to-do list.

Four o’clock came and went with the familiar sight of Remus closing the flower shop and cycling up the avenue, but he wasn’t heading home yet; he was on his way to a local pub to meet Peter Pettigrew and Mary Macdonald, two friends from university. They’d badgered him in a group text earlier that afternoon until he’d finally caved, agreeing to go out for a pint.

The last few times they’d hung out, Peter and Mary had been the ones to come to him, as was the case this time. Remus felt badly about it. He knew he hadn’t been reciprocating their effort lately—they’d had to persuade him to come out after telling him they’d take the Tube to Maida Vale—and was generally not as good as they were about making plans. It wasn’t that he didn’t want to spend time with them, but an introvert who works long hours didn’t exactly go hand-in-hand with a booming social life.

Still, Remus knew he’d run out of excuses not to go out. He looked around the noisy pub until he spotted Peter waving at him from a high-top table. “Look what the cat dragged in! Hiya, Remus!” Peter declared, pushing a full pint of beer over to Remus once he’d sat down beside him. “Finally got you out of seclusion. How you doing, mate?”

“I’m fine. You know, heading up the London chapter of Hermits United,” Remus replied, paraphrasing an old episode of Doctor Who while waving to Mary as she walked over from the bar. “We meet up every few years, swap stories about caves. It's good fun, for a hermit.”

They finished two pints each as they caught up on one another’s news. Peter talked about his job managing a cinema, his overbearing parents and his latest idea for an app he’d never develop; Mary discussed her new, fancy marketing gig, her landlord troubles and her two dogs. Remus filled them in on his accidental weeklong holiday and how things were going at the shop. They swapped a few dating stories as well before Mary eyed Remus over her water glass, flicked her dark, shoulder-length curls over her shoulder and said, “You’ve been suspiciously quiet.”

Pete snorted. “It’s Remus.”

Mary rolled her eyes. “I mean about his love life.”

“It’s Remus.”

“Yeah, and he’s a total catch!”

“I’m not saying he’s undateable,” Peter said, blue eyes darting between the two of them. “I’m saying he doesn’t exactly kiss and tell, does he?”

Remus took the last sip of his second beer and cleared his throat pointedly. “I have nothing to tell. No time for kissing, lately.”

“Remus,” Mary said gently, frowning. “I know you work a lot, I get it.” No, you don’t—you get six bloody weeks of paid holiday, Remus wanted to say. He swallowed it. “But you can’t just never go out with anyone again.”

“I think I can, actually,” Remus replied curtly, unable to stop himself this time. “I don’t need a relationship to survive.”

Mary sighed, undeterred by his tone. “Okay then, are you saying you want to be single forever? Because if you do, I won’t mention it again.” After a moment’s sullen silence, she continued, “That’s what I thought. If you want to find someone, you’ve got to put yourself out there a bit.”

“And if you have an awful date, it’ll at least make for a good story,” Peter added, clinking his water glass to theirs in a cheers and grinning. “Round three on the beers, or no?”

“Only if Mary stops harassing me,” Remus said, but the corner of his mouth turned up in a small smile.

Peter headed to the bar to order for them and Mary nudged Remus’s foot with her own under the table. “I want to see you happy, Re,” she said sincerely, her smile a bit sad. “And I’m worried that after Michael—”

Remus groaned, looking up at the ceiling. “Please, Mar, don’t start—”

“After everything that happened with Michael,” she continued, leaning forward as though trying to drive the point further into Remus’s head, “I’m worried that you’ve given up on the idea of finding real love. Don’t let one bastard do that to you.”

Remus brought his gaze back down to meet Mary’s, considering her for a long moment. He knew she genuinely wanted him to be happy. They didn’t always get him completely and grated on his nerves at times, but Peter and Mary meant well and they cared about him and they dealt with his bullshit, so Remus said, “You should really charge me for these pub night therapy sessions.”

He was smiling, and Mary smiled, too, more warm than sad this time. “Add it to my tab. I should’ve been a psych major.”

After they’d finished their drinks and some gloriously greasy burgers, Remus hugged them each goodbye and headed home. It was a balmy, picturesque summer night; the sun was just beginning to sink lower in the sky, casting a pink-orange glow amidst the deepening blue. En route home, Remus cycled down the avenue his shop was on, glancing at its cheery exterior as he rode by. His heart doubled its pace as he caught sight of Sirius locking the door of his own shop and doing that same huge, lion-like stretch from the day before, his t-shirt riding up slightly over his stomach as he threw his arms over his head.

It was only when Sirius spotted him, giving him a grin and a salute, that Remus realized he’d slowed down so much the bike was nearly wobbling in the road. He waved back quickly before heading off at a normal pace again, but his heart kept beating faster than usual long after he’d arrived at his flat.

\newpage

%Chapter 3
\fancychapter{10 September}{Fish and chips are consumed and a friendship is formed.
}

AFTER HIS THIRD APPOINTMENT OF THE DAY, Sirius was standing on a stepladder by the windows of Black Dog Tattoos and carefully pouring water into the plant hanging there until he was confident it had received the proper amount. Andromeda, thoroughly convinced her cousin would kill said plant within days, had been amazed and more than a little amused at his diligence in caring for each cactus he’d gotten from next door. Sirius had been following Remus’s instructions to the letter, and the cacti, for their part, seemed happy with the attention.

It had been two weeks since Remus had given him the plants, and one week since the tattoo shop had been open for business. Sirius’s schedule was packed, and Andromeda had had to start a waiting list which was growing by the day. Their move across town hadn’t hurt their popularity; if anything, even more people sought out the enigmatic, talented cousins since they’d gotten some coverage by the local news for opening their new location.

“Be honest—do I look as dead as I feel?” Sirius said to Andromeda as he started watering the cacti on the counter. His hair was half up, half down with a small bun in the back, and he had his beloved leather jacket on over an old Ramones t-shirt. His jeans were black and torn up at the knees.

“You look like your usual disastrous self,” Andromeda replied, firing off another email in reply to a client, “But don’t tell me you aren’t loving this.”

Sirius’s eyes were bright and he grinned in spite of himself. “Okay, yeah, I do.” He set the water bottle on one of the shelves behind Andromeda. “I bloody love this job, but I miss sleep. I haven’t seen her in ages. I’m forgetting what she looks like. I’m done for the day, yeah?”

“Nope. Sorry, love,” Andromeda said as he groaned and thudded his forehead on the counter. “One more, and it’s a long one. But you’ve got time for a kip beforehand if you want.” She paused, watching him walk off. “You’ve got an hour, set an alarm!” she added as he waved to her, went outside and up the back stairs to his flat.

Fedelius Flowers was similarly slammed. The Dearborns had been so pleased with Remus’s arrangements for their wedding that they’d recommended him to their soon-to-be-married friends—friends who’d reached out in a similar last-minute fashion, offering quite a high rate to compensate for the rush. He and Alice has spent all day on the phone with their supplier working out what they could get in on time that would be suitable for a formal wedding.

“I don’t understand why people can’t plan ahead,” Remus grumbled to Alice for the dozenth time that day. “I mean, they knew they were getting married months ago. Did they think flowers were just going to fall out of the sky the day of, perfectly arranged for them?”

“Some people are just stupid,” Alice said solemnly, refilling their mugs with the strongest black tea she could find in the back office. “A girl in my business class thought a market analysis was a Yelp review of the local Tesco.”

The sunny September afternoon became a cool, breezy evening. It was nearing six, but Remus was still in the shop catching up on everything he’d pushed off for the sake of the wedding. He sighed deeply, scrubbing a hand over his face and blinking blearily around the empty shop.

“Right—that’s as sorted as it’ll get for the day,” he mumbled. He’d been working in nothing but jeans and a soft, gray t-shirt since the last customer had left, but he tugged a flannel shirt back on before flicking the lights off and locking up.

He went over to the bike rack and noticed a light was still on inside Black Dog Tattoos. Remus’s feet carried him to the windows of their own accord and he peered in, eyes finding Sirius’s in seconds. Sirius grinned widely at him, beckoning him inside.

“Evening, Lupin,” he said as Remus joined him by the sofas. “You’re working late. Business is good?”

“Hi, Sirius. Yeah, we’ve been so busy—I shouldn’t complain, but…”

“But you wish you could clone yourself so you could fuck off to Ibiza and get drunk on the beach while the clone does your work for you.”

Remus laughed. “Pretty much, yeah.” He knew Sirius understood on a level that most people couldn’t, and it was nice not having to try and explain what it was like to run a business.

Sirius tilted his head to the side, regarding Remus for a moment. “You hungry? I can’t be arsed to cook tonight, and I’ve been meaning to hit that chip shop you recommended.”

“Starving,” Remus replied with a nod and a grin.

“Good.” Sirius returned the grin, biting at his bottom lip unconsciously. “Let me close the place up.”

Five minutes later, they were chatting to each other about their days as they walked beneath the cloudless sky toward their destination. Once beers and heaping baskets of fish and chips had been acquired, the pair settled across from each other at a tiny metal outdoor table. They didn’t say much for the first few minutes, hungry as they were, but then Sirius popped a chip in his mouth and pressed his palms together as though in prayer.

“You were so right about this place,” he said. “This grease is giving me life right now.”

“I think it’s shortening our lives, actually,” Remus replied. He wondered if he’d stopped grinning since Sirius had waved hello.

“But what a way to go!” Sirius declared around a mouthful of chips.

Suddenly, two girls who looked no older than university first years slowed their pace on the pavement as they passed by Sirius and Remus’s table. They whispered to each other, giggling and gawking very obviously at Sirius before scurrying on their way. Remus looked at Sirius, eyebrows raised, and said, “Happens to you often, does it?”

Sirius leaned back in his chair, smirking at Remus. “What can I say? I have that effect on people.” He waited a beat. “But that might’ve had something to do with the Buzzfeed article on us that went up yesterday.”

Remus had nearly forgotten about Sirius and Andromeda’s notoriety. The tattoo shop’s Instagram page with its millions of followers floated into his mind’s eye. “Alice said you were famous. I’ll have to read the article.”

“Oh, but it was so boring,” Sirius said, waving a dismissive hand. He cleared his throat, putting on a sing-song voice. “Sirius Black graduated from University College London, where he studied fine art.” He dropped the impersonation. “They left out all the good bits, there. We’re talking schoolwide pranks, three arrests, the most legendary parties that campus will ever see...”

“Three arrests?” Remus bit the inside of his cheek to keep from smiling. “You really take your whole ‘anarchy-in-the-UK’ persona seriously.”

Sirius put his elbows on the table, leaning back in toward Remus with intent. “Remus, there’s one thing you should know about me,” he said solemnly. A long pause, then; “I’m always Sirius.”

“Oh my god,” Remus groaned, shaking his head as Sirius’s lips twitched once, twice, then broke into a toothy grin. “That’s fucking terrible. Jesus.”

Sirius just waggled his brows. “My parents cursed me with this name, it’s my duty to make puns until I die.” He fished his phone out of his jacket pocket, leaning his wrist on the table between them and angling the screen toward Remus. “They did include a really cool shot of the place, though, let me show you.”

Sirius’s lock screen was a photo of a two-year-old boy with unruly, jet-black hair and green eyes smiling hugely at the camera and clutching a stuffed lion in his hands. “Is that your son?” Remus asked.

“What? Oh, no. Christ, me as a parent.” Sirius laughed. “That’s Harry, my godson. His dad’s my best mate. Cute kid, isn’t he?”

Remus felt relief unfurl in his gut, followed immediately by a wave of guilt. “He is,” he said, focusing instead on how endearing Sirius’s obvious attachment to his godson was. Sirius unlocked his phone and Remus just about melted when he saw that the background of his home screen was another picture of Harry—this time laughing in Sirius’s arms, grabbing fistfuls of his godfather’s hair while Sirius winced at the camera.

Remus looked on as the article was pulled up, and he saw the wide shot Sirius liked of the waiting area. “Did you go into this straight out of art school, then?” he asked as Sirius pocketed his phone and had a sip of his drink.

“Pretty much, yeah. I was 23, working a few odd jobs here and there. Andy’d already been at me for a while about making a living doing what I liked. Then our Uncle Alphard died, left Andy and me a pile of money, and we dumped every last pound of it into leasing a storefront in Soho to do tattoos and piercings.” He stretched his arms out at his sides as he finished, grinning proudly. “Eight years later, we’re still in business.”

There were a lot of questions Remus wanted to ask after that—about the uncle, about getting the shop off the ground, about everything—but he heard himself say instead, “I was 24.”

“When you opened the flower shop?”

“Yeah. Well, when I took it over.”

Sirius eyed him curiously as Remus took a bite of fish. “Go on then, shut me up. I want to hear your tale of success. Did you study to become a florist? Is that a thing?”

Remus laughed. “That is a thing, but no, I didn’t. I had a boss who taught me everything. He was more like a mentor, I guess you could say.”

Sirius let him take a sip of his drink before prompting him to keep talking. “Come on, I want to know. There once was a wee lad called Remus Lupin, who was obviously born in Wales on account of his accent.” He grinned, then added, “Do you have a middle name?”

“You want me to go that far back?” Remus said incredulously. Sirius raised his eyebrows, clearly not going to say more until he went on. “Right, okay. I was born in Wales, you’re right—Remus John Lupin. It’s not an especially notable story, really: dad’s a factory worker, mum was a seamstress.” He felt a pang at the change in tense, but didn’t say anything more about it. “Came to London on a scholarship to King’s College, where I made the extremely practical decision to study comparative literature and classics.”

This got a chuckle out of Sirius. “I mean, art major here. All the least employable subjects are the most fun, wouldn’t you say?”

“You used what you learned, though. My Latin only comes in handy with crossword puzzles.”

“A Welsh lad who does crosswords and reads Latin. Now we’re getting somewhere.” Sirius’s eyes were crinkled as he drained his beer. They’d cleared their baskets of food, and Remus finished his beer as well before Sirius brought them two more. Sirius looked like he belonged out at night, Remus thought as he watched him walk back with the drinks; all dark hair and leather to match the inky sky, broken up by flashes of white teeth. He put an elbow on the table, resting his chin on his knuckles and waiting for Remus to continue. “Where do the flowers come in?”

Remus wrapped both hands around the cool glass of his own drink. He wasn’t used to talking about himself this much. “During uni. I always had a load of odd jobs, too. In my second year I was hired as a part-timer by the owner of Fedelius Flowers. He was an elderly bloke, eccentric but brilliant. Albus Dumbledore.” He grinned a little wistfully, looking down at his glass for a moment before meeting Sirius’s eyes again. “It was really just meant to be ringing up customers, straightening shelves, that sort of thing. But he said I had an eye for color and...I don’t know, he used to say I could ‘intuit’ what a customer wanted by talking to them.” He shook his head, embarrassed to repeat the compliment.

“Well, obviously he was right,” Sirius said, and Remus was taken aback at his tone, softer than he’d heard it before. “So he showed you the ropes?”

“Yeah, he taught me how to design arrangements, order stock, coordinate deliveries, even bookkeeping. I worked for him all through school except after my acci—er, basically all through school,” Remus covered quickly. “Worked there full-time for about two years after I graduated. And then Dumbledore died.” Remus paused, turning his mouth up in a half-smile. “Which, this is a bit weird, the parallel.”

“Spooky,” Sirius agreed. “Don’t tell me you had a cousin you went into business with, too. I might sue you for identity theft.”

That pulled a laugh out of Remus. “No cousin. Dumbledore was an eccentric bloke, like I said, and he left me the shop in his will. Found out from his solicitor over the phone, I made her check three times.” He knew he could leave it at that, but he heard himself adding, “I was 24 and suddenly I just...had this place. This business. And I felt totally unprepared. I really didn’t know how the hell I’d be able to keep it from going under. It was like…” he trailed off, trying to come up with the right words.

“Like standing on the edge of a bloody massive cliff and then having some guy shove you off without a tether?” Sirius offered.

“Yes,” Remus said in a rush of breath, eyes bright where they met Sirius’s own. He understood; of course he did. “Yes, exactly like that. Every day I’d go in and work until I could hardly stand up, and every day I’d go home and debate with myself over selling it.”

“What stopped you?” Sirius asked.

“Alice. She answered a part-time ad I’d put out; I desperately needed a second pair of hands for the day-to-day. I told her it might be temporary, that I was thinking of putting the place up for sale, but she just...believed in me. Believed we could do it. Aggressively so. I think us making it was due to her sheer force of will.” He laughed. “It took probably six months of nonstop encouragement before I decided to keep it. As soon as I was able to afford it, I asked her to stay on full time. She’s never left for six years; not when she had her son, not when she decided to go back to school at night.” Remus felt a rush of affection for Alice as he trailed off. He hadn’t thought about their beginnings in a while, and he couldn’t remember ever telling someone the whole story from start to finish like this. He remembered filling in his father, Pete and Mary as things happened—in snippets, and even then, only when they’d pulled it out of him—but this was different. He was shocked at how natural it felt to tell all this to Sirius.

Sirius hummed, smiling at Remus as he broke for a drink. “And you brought her husband on, too, yeah?” he said.

“Yep, Frank came in like a knight in armor a couple years ago to run deliveries when we started getting bigger orders—weddings and things. Honestly don’t know what I’d do without them.”

Remus felt his cheeks warming as Sirius searched his face for a long moment before sitting back and smiling. “I knew I picked the right street. We outgrew our original place in Soho. I was out for a ride a few months ago when I saw the sign next door to yours. Had a good feeling about it.” Remus felt his stomach flip as Sirius, still smiling widely and holding Remus’s gaze, sunk his teeth into his lower lip in that same unconscious gesture from earlier. “I was definitely right.”

They stayed there, slowly finishing their drinks and chatting about other, more mundane things, until a couple waiting for a table started eyeing them irritably. They took their time walking back, too, Sirius even stopping altogether to pet three different dogs walking by.

“I’m starting to see how well the name suits you,” Remus said after the last one had trotted away with its owner. “Black Dog. Black for your surname, and dog—Sirius is the dog star, isn’t it?”

“I’m impressed,” Sirius said with a smirk. “He knows Latin and astronomy.”

“I knew Andromeda was a galaxy, and Sirius sounded familiar, so…” Remus cut himself off, realizing how embarrassing what he was about to say was.

“So…? Oh,” Sirius’s smirk turned into a toothy grin. “You googled me, didn’t you?”

“I googled your name, shut up,” Remus muttered, ears burning red as Sirius chuckled. “But I see now that it’s not just a name; you are truly one with your canine brethren.”

A shit-eating grin was still plastered on Sirius’s face. “Woof.”

They stopped at last on the pavement outside the darkened tattoo shop, and Sirius glanced briefly up at the second floor where Remus knew his flat was. “Welp, this is me,” he said, but made no move to leave.

Remus hummed in agreement, putting his hands in his pockets and not moving either. A pause, then;

“Hey, do you—”

“We should—”

They laughed at they started to speak simultaneously. “You first,” Remus said.

“Was gonna say, we should hang out again soon. When you aren’t robbing banks or some such, that is.” Sirius replied, smirking.

Remus felt himself smile back. “And when you aren’t getting hauled off to jail for being a massive punk-rock rebel.”

“That was one time! Okay, three times, but it’s been a while.”

“Mhm. Well, when we aren’t busy with all that.”

Sirius pulled out his phone and handed it over to Remus. Heart racing, Remus added his number and passed it back. Sirius looked infinitely pleased, and knocked his elbow playfully into Remus’s upper arm before walking backwards toward the building. “Night, Remus!”

Remus nodded, murmuring goodnight and waiting until Sirius was up the back stairs and into his flat before fetching his bike.

By the time he got home, Remus had two texts from an unknown number waiting for him: a dog emoji, followed by,

\textbf{Chinese next time?
}
Standing in his bathroom with his toothbrush held between his teeth, Remus tapped out a reply.

\textit{Sure, but don’t think you’re getting away with paying for everything again.
}

He glanced up at the mirror and rolled his eyes at the goofy smile plastered across his face. “Get a hold of yourself, Lupin. You’re thirty years old.”

Still, he couldn’t help the upturn of his lips as he looked down and read,

\textbf{That’s what you think. It’ll be over and done with before you can catch me. I’ve got catlike reflexes, for a dog. x}


\newpage

%Chapter 4
\fancychapter{19 October}{Sirius fancies Captain America, Regulus has regrets, and Remus still doesn't like motorbikes.}

SEPTEMBER ROLLED INTO OCTOBER, and Remus was talking to Sirius more than ever. Texting had become a regular occurrence. It had started out small—Sirius sending a few funny dog videos and Remus rating them on a 1-10 scale—but quickly grew into an ongoing chain of banter, their conversations longer at night and on days they weren’t working.

Last week, for instance, Sirius had sent two pictures of the cacti Remus had given him, clearly happy in their new environment with new growth visible.

\textbf{Our plant children are looking good.
}

\textit{They grow up so fast. But I hope by “our” you’re referring to you and Andy. I gave them up for adoption, remember?
}

\textbf{No way, you and I have joint custody.
}

\textit{I agreed to nothing of the sort.
}

\textbf{Don’t make me take you to court, Lupin. Think of the kids.
}

\textit{They clearly prefer living with you, at any rate. Staying up past curfew, eating ice cream for dinner.
}

\textbf{Only on Saturdays.
}

\textbf{Wait. Holy shit. We never named our children!
}

\textit{Why do I get the feeling you name everything?
}

\textbf{Rusty the Tattoo Gun detects your snark and does not appreciate it.
}

\textit{That’s a terrible name for a piece of sanitary equipment! I don’t trust you to name our kids.
}

\textbf{Aha, so you’re accepting parental responsibility!}

\textit{As the person who gave them to you, I feel I must stop you from calling them something like Spiky and Spiky Jr.}

\textbf{I wasn’t going to call them Spiky and Spiky Jr.}

\textbf{But now that you mention it...}

\textit{I’ll see you in court.
}

\textbf{Fine, fine. Are we talking boy or girl names? Both? Neither? Don’t let me misgender our kids!
}

\textit{They’re cacti, Sirius. The plants are basically genderless, and the flowers have both male and female parts.
}

\textbf{Now I’m just picturing Frank-N-Furter, for some reason.
}

\textit{I can assure you I did not order those plants from Transsexual, Transylvania.
}

\textbf{Ha! If you had done, you could’ve weaseled your way out of custody, you know.
}

\textit{Shit}.

\textbf{I’m calling the one on the counter Frank.
}

\textit{Alice’s husband will be flattered.
}

\textbf{Damn. Too many Franks. Riff Raff, then?
}

\textit{That’s actually pretty good.
}

\textbf{All Riff Raff ever wanted was your approval!
}

\textit{The hanging one could be Magenta, it’s covered in pink flowers.
}

\textbf{Done. Expect the birth certificates in the post.
}

\textit{Oh, joy. I’ll phone my dad, let him know he finally has grandchildren.
}

They’d also grabbed dinner a few more times—including Chinese, the bill for which Remus sneakily paid before Sirius could react—but most often they saw each other when Sirius would drop by Fedelius Flowers between clients and Remus, if he wasn’t busy himself, would make him a cup of tea. He’d done it the first time out of polite habit, but then Sirius had sung his praises and groused about the bitter coffee Andromeda made next door, and it had turned into something Remus looked forward to more than he’d ever admit.

On a cloudy, chilly Friday, Remus found himself with some free time around lunch. He hadn’t seen Sirius yet that week and decided to bring some tea next door so he could say hello to Andromeda, too, and have a look around the place. (Sirius was always fiddling with the layout here and there, trying to get things perfect; Andromeda let him follow his vision, for the most part.) He walked out of the back office with two steaming mugs and nodded to Alice as he headed toward the door.

“Back within the hour,” he said.

“Unless you get lost in a certain pair of mysterious gray eyes,” Alice replied, pitching her voice low for drama.

“Oh Christ, don’t start,” Remus groaned. “We’re friends.”

Alice folded her arms, giving him a look of pure skepticism. “Right, just friends. Just a friend bringing a friend a cuppa in the exact same mug you always give him because he said he fancied it one time.”

It took effort, but Remus did not glance down at the mug he knew was currently in his right hand—an old one, pale green and slightly chipped, that Sirius had chosen from the handful on Remus’s desk a month ago. “Goodbye, Alice,” he said pointedly, keeping his expression neutral as he left.

Andromeda was ringing up a customer when Remus walked in. “Hi, love!” she said, gesturing to the sofas. “With you in a tic. Is that for me?”

Remus lifted a mug, nodding, and took a seat to wait. She was with him a minute later, sitting in an armchair next to him and taking a sip of tea. They chatted about how business was going for each of them and Andromeda told him about the latest prank Dora, her daughter who was a student in upper sixth, had pulled with a few of her classmates.

“She sounds a bit like Sirius,” Remus said, smiling.

“Oh, they’re cut from the same cloth alright,” she agreed, rolling her eyes but grinning a little. “I reckon this is payback from the universe for all the times I got him out of trouble growing up.”

“So you come from a whole family of troublemakers, then?”

Andromeda’s smile fell, turning into a sad twist of dark red lips. “A few of us,” she said quietly, glancing down at the mug in her hand. “Our late uncle called us ‘the Black sheep.’ Thought himself quite funny for that.”

Alphard? Remus was about to ask, but his attention was diverted to Sirius, who’d just strolled over to join them. “Remus Lupin,” Sirius said in greeting, plucking the green mug he knew was for him off the table and sitting cross-legged on the sofa next to Remus. He pushed his dark hair away from his face, taking a long sip and leaning back against the cushions. “To what do I owe this door-to-door delivery service?”

“I was making a cup for myself and thought, why not,” Remus said. “And I reckoned you’d need it with the week you’ve been having.”

“He told you about all the press, then?” Andromeda asked as Sirius hummed and took another sip. Sirius had recently tattooed a few of the Avengers cast members before their premiere in London. After Black Dog Tattoos was tagged by the actors in a few thank-you posts on social media, the shop’s phone had been ringing off the hook with interview requests. Reporters had been disappointed by Sirius’s playful but firm refusal to drop even the smallest crumb of gossip about his clients; he’d worked with A-listers before and always respected their privacy.

“He did. And he ranked all the Avengers’ arses from most to least swoon-worthy,” Remus said with a wry grin. “The entire cast, mind you, male and female.”

“But it’s only the males I care about. Might have to see those Captain America films, now,” Sirius said, smirking. There was a swooping feeling in Remus’s gut as he processed that, but he said nothing, wishing he’d brought a cup of tea for himself to duck his face into.

“Wait, is that why you were on your phone for most of the Guardian photoshoot?” Andromeda interjected. “You were texting Remus?”

“Remus was more interesting,” Sirius said simply, shrugging. Remus bit his bottom lip to keep from grinning like a fool.

Andromeda was in the middle of scolding Sirius for being rude to reporters when the shop door opened. The man who walked in was wearing a dark green, expensive-looking dress shirt and black trousers and was carrying a briefcase. He looked like an executive who’d just left his high-powered job downtown, but his face was quite young—Remus figured he couldn’t be older than 25. He was broodingly handsome, his dark hair strikingly similar to Sirius’s but cut much shorter and neatly styled. On the hand holding the briefcase, Remus spotted a silver ring with a snake insignia, its two tiny emerald eyes catching the light from the windows.

As Sirius and Andromeda looked over at the stranger, the easy, comfortable atmosphere Remus had been enjoying with them was gone instantly; it was as though all the air had been sucked out of the room, and Remus found himself unable to look away from Sirius’s face, which went hard after his eyes widened briefly in shocked recognition.

The young man seemed as tense as the other two, and stood stiffly by the front desk, his gaze flickering between them. Finally, he said, “Andromeda. Sirius.”

The cousins got to their feet, tea forgotten on the table. Remus stood, too, feeling distinctly like he was dropping in on something private. He looked to the front door, debating.

“Hello, Regulus,” Andromeda said, expression unreadable. “It’s been a long time.” Sirius followed her over into the middle of the room but said nothing, entire body radiating tension as he glared down the younger man.

Regulus opened his mouth, closed it, glanced at Remus, then opened it again to say, “If you’re with a client, I’ll wait.”

Remus picked up the two half-empty mugs, giving an apologetic half-smile and saying, “Oh, no, I’m just visiting. I’ll get out of your hair.”

Sirius kept his eyes boring into Regulus’s but shot an arm out in Remus’s general direction, palm up. “No, stay. He’s the one interrupting.” Remus almost wanted to wince at the sheer awkwardness of the situation, but sighed instead, sitting down again and pretending to busy himself with the binders on the coffee table.

Regulus looked annoyed, but schooled his expression into something more neutral before saying, “This won’t take much time. I’ve just come to collect something from Sirius, and then I’ll be on my way.”

“Collect what?” Sirius asked, addressing him directly at last.

Clicking open his briefcase, Regulus produced a stapled sheaf of papers, holding them out between himself and Sirius. “Mother and Father have taken inventory of all their assets,” he said, and Remus could sense the young man’s hesitation despite his carefully even tone and expression. “And they have been tracking down a few of the more valuable missing items.”

Sirius snatched the papers, eyes scanning the first page briefly before he looked back at Regulus. “Still alive and kicking and hoarding their little treasures? Bully for them,” he sneered. He looked so different from the open, smiling, carefree Sirius that Remus had grown used to. “Did I miss the part where I’m supposed to care?”

Again, Remus sensed a second’s hesitation before Regulus continued. “Among what’s missing is a gold locket encrusted with twelve rubies.”

This made Sirius’s expression waver. “What? No, that was Uncle Alphard’s.” He seemed to recover himself, jeering, “And seeing as he was so kindly cut off the family tree, I’d say he could do whatever the hell he wanted with it.”

“No. It was lent to him years ago by Father, but Alphard was told to return it once he’d been estranged from the family.” Regulus paused, looking pointedly at Sirius’s chest before meeting his gaze again. Remus noticed for the first time a very thin, gold chain around Sirius’s neck, peeking out from under his dark hair. “And as Alphard had no legal right to it, nor did he leave it to you in his will…”

“Regulus,” Andromeda cut in, disappointment written clear across her face. “Surely this isn’t necessary. Your parents have vaults full of jewelry, I don’t see why they’d have any need for one measly locket.”

For one brief moment, regret shone through on Regulus’s masked expression as he glanced at Andromeda, but disappeared just as quickly. “If Sirius refuses to return the stolen item, they intend to pursue legal action.”

“Stolen?” Sirius roared, looking about two seconds away from wrapping his hands around Regulus’s neck. He stepped in menacingly toward the other man, who didn’t back down.

“Sirius, that’s enough,” Andromeda said, holding out a hand between them as she tried to keep the tension from boiling over. “You heard him. It isn’t worth facing them in court. They’ll be taking it either way.”

There was a long, terrible silence. They all watched as Sirius grabbed the chain at his neck with the hand not holding the papers and pulled viciously, breaking the clasp. He lifted the locket out from under his shirt and stared down at it with a tight jaw. Under different circumstances, Remus would have found it funny that Sirius was keeping jewelry worth more than both their flats put together hidden under an old Siouxsie and the Banshees t-shirt; as it was, though, he just looked on in distress as Sirius shoved the locket and documents at Regulus.

“Satisfied? Go run back to Mummy and Daddy and tell them what a good job you’ve done,” he snarled, expression thunderous.

Regulus dropped both items into his briefcase without ceremony before looking back up at Sirius. He was frowning deeply, but said, “Thank you. And...congratulations. On your business.”

As he turned to make his way out of the shop, Andromeda said quietly but clearly, “You aren’t a little boy anymore, Regulus. You can make your own decisions about what’s right and what’s wrong.”

His back to them, Regulus hesitated for a long moment. Then without a word, he strode out the door and into a black car, not looking back as he drove away.

For a few seconds, no one moved; it seemed as though no one even dared to breathe. Then Sirius let out a muffled “fuck!” and stormed over to the far windows, lifting his arms to grab fistfuls of his hair in a gesture of such pure, helpless frustration that it brought Remus halfway across the room before he stopped himself.

He looked at Andy, who shook her head and gave him a small, sad smile. “Sorry about all that, Remus,” she murmured. “Thanks again for the tea.”

“Don’t worry about it,” he managed. He knew he should leave; this was obviously a family matter that Remus wasn’t meant to have been privy to in the first place. But he looked over at Sirius again and, seeing the tense hunch of his shoulders, went against his better judgment by setting the mugs down on the front counter and walking the rest of the way over to Sirius, putting a gentle hand on his shoulder. The little involuntary jolt Sirius gave at the contact pulled at Remus’s heart.

“You alright?” he asked softly.

Sirius looked back over his shoulder at him before huffing out a breath, muttering, “Yeah. Fuck. No.” He began pacing about the room, teeming with pent-up emotion. “I can’t believe the fucking nerve of him to come in here and—”

“Sirius, he was sent here by your parents—”

“His parents,” Sirius cut Andromeda off, tone vicious. “They’re his fucking parents. Who knew I had that locket all these years and never cared until, what, they sensed I’d been too happy for too long? Time to rear their ugly heads again, knock me down a peg?”

Not knowing if he’d be making matters better or worse but wanting to try and help any way he could, Remus suddenly said, “Hey.”

This was enough to get Sirius to pause mid-stride and look over at him. Taking it as a good sign, Remus continued, “What do you normally do? When you’re stressed like this. What helps?”

Sirius blinked at him, brow knitting in confusion, before finally replying, “I...go for a ride. On my motorbike. Helps sometimes.”

“Okay,” Remus nodded. “Okay. Take me for a ride, then.”

“What?”

Remus bit the inside of his cheek to keep from smiling at the utter confusion on Sirius’s face. “Look, you’ve got clients to see in a bit and you’ll be useless to them in this state. So,” he allowed himself a small grin, “Take me for a ride. I’ve never been on a motorbike before.”

This got the corners of Sirius’s mouth quirking upward in a ghost of a smile. “Really? Never?” Remus shook his head. “Right, well. We have to fix that.”

He looked to Andromeda, who waved them off with a warm smile. “You have half an hour. Go on, get out of here.”

Standing on the pavement next to Sirius’s parking space, it suddenly occurred to Remus that A) he’d never ridden a motorbike before because of several very legitimate safety concerns, and B) if he’d wanted to try it out, he probably should have waited until Sirius was somewhat calmer. Sirius came down from his flat with a second helmet for Remus and his jacket, which he shrugged on before meeting the other man’s worried gaze. “Don’t worry, I’ll get you back in one piece,” he said. He was still acting off, frowning and looking tense whenever he wasn’t looking directly at Remus, but he was less frantic than he’d been right after Regulus had left, preoccupied now with their spontaneous trip.

Remus looked from the helmet to the bike and back again. “Er, when I said I’d never done this…”

Sirius stepped in close, helmet in his hands. “You’ll be a natural at it, Lupin,” he said with a small smile. He faltered for a moment. “Unless you’ve changed your mind?”

“No, I want to,” Remus said quickly. “Just...tell me how to get on this thing.”

The smile was back as Sirius strapped Remus into his helmet and put on his own. He got on the bike with practiced grace and, per his instructions, Remus maneuvered himself until he was straddling the seat behind Sirius. He placed tentative hands on Sirius’s shoulders, but Sirius moved them down to his waist, under his jacket. Remus’s heart pounded, feeling the heat of him seeping into his palms through the t-shirt.

“You’re gonna want to hold on tight,” Sirius said over his shoulder before he twisted the key in the ignition and the bike sputtered and roared to life. Remus’s hold on Sirius tightened into a death grip as they took off, too panicked to be self-conscious as his knees pressed solidly into Sirius’s thighs and his helmet clacked against the other’s.

“Alright?” Sirius shouted after a few minutes, competing with the noise of the engine and the helmet over Remus’s ears.

“Getting there,” Remus shouted back. It was another few minutes before his hands were no longer in a death grip on Sirius’s waist, his body starting to relax as they whizzed around the neighborhood Remus was so familiar with. The leafy streets felt different to him at this speed, a little more exciting; it helped being shoved up this close to Sirius, the warmth and solid weight of him serving as reassurance.

Sirius relaxed, too, his shoulders dropping as he enjoyed the feeling of freedom his motorbike offered him. They didn’t speak much, but Sirius pointed out a few hidden spots he’d found while out riding, giving Remus a glimpse of the town through his eyes. Remus wished he could see Sirius’s face as he talked; his eyes lit up in a way that always made Remus lean in and listen closer.

He had no idea how much time had passed, but Sirius must’ve, because he turned back toward their avenue after reaching a certain traffic light. He only let go of the other’s waist when they slowed to a stop in the same parking space and Sirius killed the engine. He swung off the bike easily before extending a hand to help Remus back on his feet. Remus felt some wobbling in his knees, but was smiling as he tugged off his helmet.

“What’d you think?” Sirius asked, shaking his hair out after freeing it from his own helmet.

“I think I’ll stick with my own bike for now,” Remus replied, “But that was...not terrifying. Approaching fun, even.”

Sirius grinned at that, but it fell as the encounter with Regulus crept back to the front of his mind. “Look, I should probably—”

“You don’t have to,” Remus assured.

“No, I should,” Sirius said. “Because you probably think I’m a bloody lunatic, now.”

“If I thought that, I wouldn’t have gotten on the bike with you.”

Sirius huffed out a breath, smiling a little. “Okay, okay. It’s just—well, obviously, I have a fucked up family.” Remus said nothing, waiting for Sirius to go on if he wanted to. “My uncle...he was really the only one I could talk to growing up who got me, apart from Andy. And that locket was the only thing I had left of him.”

“Andy said he called the three of you the Black sheep,” Remus supplied.

“Yeah.” Sirius looked over Remus’s shoulder, squinting into the sun for a moment before continuing, “We were the three who got tossed out. Andy, for marrying a day labourer—he’s lovely, by the way—Alphard, for moving in with his partner—also a lovely bloke—and me for about a million reasons. All the rest of ‘em hate my guts, and believe me, it’s mutual.”

“I’m sorry, Sirius. That’s awful.” Sirius waved the apology away. Remus hesitated before adding carefully, “Listen, it’s definitely none of my business, but. Regulus—your brother?—he didn’t seem like he hates you. He seemed more like he hated what he was doing to you.”

Sirius gave a noncommittal grunt, running a hand through his hair. Remus looked from him to the facade of the tattoo shop, considering it. “You said the locket was the only thing of your uncle’s you have left, but that’s not really true, is it? I mean, you have this place. You built all this with his help. He’s a part of this shop, and no one can take that away from you, you know?”

A complicated look flitted across Sirius’s face as he turned to regard the building as Remus had done. Then he took a long look at Remus, gray eyes darting over brown, before dropping his helmet on the seat and pulling the other man into a tight hug. Caught off guard, Remus didn’t react for a second, but in the next he was putting his arms around Sirius’s back, his own helmet dangling awkwardly from his fingers. He tried not to think too hard about the fact that they had the perfect height difference for this; Remus was just tall enough to rest his chin comfortably on top of Sirius’s head, breathing in the spicy scent of his hair as he was held close.

The embrace ended just as abruptly, Sirius pulling back and chewing at his bottom lip. “Thanks, Remus,” he said at last. “For the ride. For being a good mate.”

“Course,” Remus said, feeling a wave of fondness for the way Sirius wore his heart on his sleeve for better or worse. It brought out something protective in him; he wanted to shield Sirius from anything that could make his face tighten the way it had done during his encounter with his brother.

A woman walked up the pavement and into Sirius’s shop, catching his attention. “That’ll be my 2 o’clock,” he said regretfully, turning his gaze back to Remus.

“I’d better go relieve Alice, anyway,” Remus nodded. “See you later, yeah?”

“Yeah. Later.” Sirius took the spare helmet from Remus’s hand, flashing him a small, private smile before heading off.


\newpage

%Chapter 5
\fancychapter{31 October}{James loves Halloween, Sirius loves his friends, and Remus is going to have a hangover in the morning.}

HALLOWEEN HAD BECOME SOMETHING OF A TRADITION for Sirius Black and James Potter. James had gone on a family trip to New York during the fall of year eight and had come back to school with a fascination for the holiday that never really went away. Halloween wasn’t much of a thing in England when they were kids, but it quickly became one in their circle of friends, with Sirius immediately jumping on board with his best friend’s enthusiastic scheming and the rest of their group following in the fun. By year ten, the 31st had become a schoolwide day of mischief and revelry, because James Potter Made it a Thing, and such things tended to stick.

Then James and Sirius had gone off to university together and pulled off four of the most epic Halloween parties ever to take place in the UK, all of them only shutting down when the police were called. After they graduated and moved on, however reluctantly, to adulthood, the parties shrunk until they faded completely, but the pair still went out for a drink every year in central London and watched the pub crawlers in sexy costumes, zombie makeup, and the like. Sometimes James’s wife, Lily, came too, as well as their oldest friends and former schoolmates, Marlene McKinnon, Dorcas Meadowes, and Fabian and Gideon Prewett.

This year, Lily, Marlene, and Dorcas were joining James and Sirius at a bar in Soho—so chosen for its cheesy decorations and themed drink specials. Sirius hopped straight on the train to meet up with the foursome once he’d closed up the shop. His dark hair hung loose to his shoulders, and he wore black jeans and a maroon shirt with the sleeves pushed up just below his elbows, making visible some of his tattoos and the spare hair ties on his wrists. He also had a new necklace—a handworked Tibetan horn pendant on a silver chain—around his neck, the pendant resting above his heart.

After getting to the bar, he sidled up to the table his friends had occupied and threw one arm around James and the other around Lily, grinning hugely. “Prongs, Lils. Where’s Bambi? You could’ve done him up as a pumpkin or something.”

“Harry’s with the Weasleys, and his mum and dad are having a well-deserved night off,” Lily declared, giving Sirius’s hand on her shoulder a brief squeeze. “Besides, he’d be the only one of us in costume.”

“Not true. McKinnon here is rocking a spot-on Kristen Stewart getup,” Sirius said, grinning across the table at Marlene. With her closely cropped blonde hair, white tee and a flannel tied at her hips over loose boyfriend jeans, he wasn’t too far off base.

“Bite me, Black,” she said, flipping him off as he laughed, said hello to Dorcas and took a seat next to James.

There was an empty sixth chair on Sirius’s other side, and James caught him glancing at it a bit too intently. “So,” he asked, eyes sparkling mischievously behind his glasses as he drew the word out. “Where’s your date, Pads?”

“He’s not my date,” Sirius insisted, eyes darting over the drink menu as he tried to find the most ridiculous Halloween cocktail to order for everyone. “He’s just coming to hang out. As one of the lads, you know.”

“Right, sure,” Dorcas said, raising a skeptical eyebrow at him. Her dark locs were piled in a bun high atop her head, a few loose strands swaying as she leaned in, her elbow on the table and her chin resting on her knuckles. “Because you, who’s had the same friends for, like, twenty years, are in the habit of bringing someone round ‘just to hang out.’”

“Can I help it if most people who come round want to be more than friends with me?” Sirius said, feigning innocence. “I didn’t ask to be born beautiful.”

Marlene rolled her eyes. “You look better than Potter, anyway. He looks like he’s stuck his head in a blender.”

James reflexively rubbed at the back of his head, ruffling his wild hair even further. “Yeah, but in a sexy, he-could-be-a-rockstar sort of way,” he said, grinning crookedly. He glanced sideways at Lily, who shook her head.

“Nope, you know to go to Sirius for your daily affirmations,” she deadpanned, which Sirius quickly followed up with, “It’s working for you, mate. If there were a Britain’s Hottest Dad Award, you’d win it, no contest.”

“Obviously,” James nodded, chin jutting proudly upwards. “But my hair can never hope to reach your hair’s level of fabulousness, Padfoot.”

“I want to say I hope Remus is prepared for the these two idiots together,” Dorcas muttered to the other women as James and Sirius continued to fawn over each other. “But it’s really just not possible.”

“Honestly, you’d think they’d have run out of ways to compliment each other by now,” Marlene said in agreement. “It’d be impressive if it weren’t so annoying.”

Lily eyed Sirius across the table, brushing her long, red hair back from her shoulders. “You’re not fooling any of us, you know,” she told him. “You’ve been going on about him for weeks. ‘Remus lent me his favorite book. Remus made me a cup of tea. Remus loves Big Brother and the Holding Company, too.’ I don’t think you even realize you’re doing it.”

“Oh, shut up,” Sirius huffed, his hands fidgeting with the menu. “He’s just...a cool guy. He’s been a good mate since I moved the shop in. And he works all the time, hardly ever goes out. So,” he gestured vaguely to the group of them sat around the table. “I thought he’d have fun with the lot of us.”

“That he will!” James declared, thumping Sirius on the back. “We’re a guaranteed good time. Now, are we doing the purple fizzy drink in the skull first, or the orange and black one in the cauldron?”

A few blocks down from the bar, Remus was walking out of the Tube station and checking his phone. He had one text from Sirius that just said, purple or orange? He blinked at the screen for a moment before he sent back orange, hoping this wouldn’t result in being given an embarrassing costume or, even worse, something pumpkin-flavored. It was a cold night; he’d layered a knit jumper over the collared shirt he’d worn to work, but his breath was still visible in white puffs as it left his lungs.

He made it halfway to his destination before his phone rang. He answered without checking who was calling, saying, “Alright Sirius, what have I signed myself up for?”

“What? Hello? Remus?” His father’s voice said on the other end of the line.

“Oh, hi, Dad. You alright?”

“Yes, yes, I’m fine. Tried ringing you this morning, thought I’d try again before I turned in for the night.”

Remus had forgotten about the missed call, too distracted by work and the thought of meeting Sirius’s closest friends that evening. “I meant to call you back after closing, sorry.”

“It’s alright, lad, I was only saying hello,” Lyall chuckled. Their conversation was momentarily drowned out by a passing police car, siren blaring. “Oh, are you out? We can chat tomorrow.”

“It’s fine. I mean, I am out, but I’m just walking to a bar now.”

“Are you? On a weeknight and all?” Lyall said teasingly. Remus filed it under one of those things that lets a person know they’re truly an introvert: getting nagged by their parent to go out more often. Remus was about to reply when his father added, “Does this mean you’ve finally got a girlfriend?”

Remus’s stomach tightened at that, and he was silent for a few seconds as he walked faster, adjusting his grip on the phone pressed up to his ear. “Nothing like that,” he replied, his tone deliberately casual. He would not think about Sirius Black right now, he would not. “Just meeting up with some friends.”

Lyall sighed. “Ah, well, a father can dream. You have fun then, lad, and I’ll speak to you later.”

“Yeah, alright. Goodnight, Dad.” Remus hung up, pocketed his phone, and looked up at the star-dotted sky for a moment, inhaling deeply and letting it out in a long, weary sigh. Then he hurried the rest of the way down the road to the bar, the warmth of the place settling over him like a blanket as he walked in and looked around for a familiar head of dark hair.

After a moment he spotted Sirius talking animatedly to the rest of his table. He’d nearly made it into the empty chair that was clearly saved for him before Sirius’s eyes landed on his, his entire face lighting up in a way that made warmth unfurl in Remus’s chest. He greeted him with an enthusiastic “Remus!” before introducing him to the other four people at the table. He committed their names to memory as they said their hellos: Dorcas, Marlene, Lily, James.

“So, you’ve been putting up with this git as your next door neighbor?” James said to him, pointing a thumb toward Sirius.

“Unfortunately,” Remus joked back. “But I can always commiserate with Andromeda if he gets really annoying.”

“Excuse you, I am a delight,” Sirius sniffed.

“Modest, too,” Remus quipped. James shot Lily a private look, both of them smiling at each other as Remus and Sirius bantered. Remus suddenly remembered the pictures of the smiling toddler on Sirius’s phone and turned his attention back to the couple. “Are you Harry’s parents?”

“He’s our boy, yeah,” James said, obviously brimming with pride as he placed a hand on Lily’s shoulder.

“Sirius showed me some photos of him. He looks exactly like you.” It was true; the boy’s hair, skin tone, and features were near-perfect matches for James’s, except for his eyes—they were the same striking green as Lily’s.

“We’re hoping he got Lily’s brains,” James said with a grin. “So he can grow up and be a badass, Earth-saving scientist like his mum.”

“I won’t be saving the planet tomorrow, not with the hangover I’ll have from this sugary mess,” Lily said, grimacing after taking a sip from her cauldron-shaped glass.

Remus glanced down as Sirius pushed a full drink toward him. Now he understood the orange-or-purple question, at least. “You’re properly into this Halloween stuff, aren’t you?” Remus said to him. He took a tentative sip of the orange liquid, which had some sort of black edible glitter on top, and pulled a similar face as Lily. It was sickly sweet and would surely give them all banging headaches in the morning.

“We all owe our love of Halloween to James here,” Sirius said after taking a swig of his own drink. “He saw the big costume parade in New York City when we were kids. He came back obsessed, got all of us into it...” he made a swooping gesture between them all. “The rest is history.”

“God, remember all the stupid costumes we wore?” Marlene said, smiling despite herself as she thought back to their school days. “The dead rock star year was a good one.”

“That was good, but the best of all time was when we all went as teachers,” Dorcas added. “I’ll never forget the look on McGonagall’s face when she saw Sirius sashaying down the hall.”

“She was flattered, I could tell,” Sirius chimed in. “And maybe a bit jealous. I looked fucking fantastic in that green dress.”

Remus laughed at the mental image. He listened as the group swapped a few more stories while sipping on their cocktails before he asked, “So you’ve all known each other since you were kids? Did you all go to uni together, too?”

“That’s right,” Dorcas said. “We were all in the same class at Hogwarts—one of those old, posh all-through boarding schools in middle-of-nowhere, Scotland. They start you at age eleven and you can stay there all the way ‘til you’re eighteen, when you’ve finished with your A-levels. Me, Lils, and Marlene roomed together; we were all scholarship kids, so we bonded, like, instantly.” The three of them put their hands out and wiggled their fingers at each other in their version of a secret handshake.

“And then we met these two rich arseholes,” Marlene added, gesturing to James and Sirius. “And somehow became this weirdly close, dysfunctional little family...which only got weirder when we ended up at UCL together.”

“Somehow?” James said with mock incredulity. “I’ll tell you how. You lot saw me and Padfoot establishing our legacy and thought, ‘Oh my god, they’re so hot and clever, they’re gonna be kings of the school by next term. We have to be friends with them.’”

“Oh, you wish, Potter,” Marlene scoffed. “Shall we recount all the embarrassing stunts you pulled in the hopes of getting Queen Lily’s attention?”

“Padfoot?” Remus asked Sirius quietly.

“That’s me,” Sirius said. “James is Prongs. Old codenames from our Hogwarts days. Over the years they sort of stuck.”

“You had codenames for each other,” Remus said, shaking his head and grinning despite himself. “Of course you did.”

Suddenly, Marlene grabbed Dorcas’s arm, gesturing over to the other side of the bar. “Oi, those dudebros finally gave up the billiards table. Let’s go humiliate them.”

Her eyes lighting up with mischief, Dorcas finished her drink before saying, “Back in a bit,” taking Marlene’s hand, and letting herself be led away from the table.

Once they’d gone, Lily looked across the table at Remus and gave him a sympathetic smile. “We’ve been carrying on for ages, Remus, sorry about that. I know we can be a bit much when we’re all together like this.”

“No, you’re fine,” Remus said honestly. “And you’re a lot more fun than I am. I can’t remember the last time I went out for any kind of holiday. I usually avoid crowds like the plague.”

“Trust me, we aren’t that fun,” Lily replied. “With a baby at home, you’re lucky to see James and I out past eight. Even Sirius stays in most of the time, these days.”

“I had no choice,” Sirius said, shaking his head. “Have you ever had to stand for hours doing a tattoo for somebody while nursing a hangover? Fucking rough, let me tell you.”

That was the only explanation he gave, but Remus had seen firsthand how much Sirius loved his job and how professional he was about it. Watching Sirius interact with his clients—the way he immediately put everyone at ease, listened to their wishes closely, and was always more generous with his time than Andromeda would prefer—was one of the things that had endeared Sirius to him in the first place.

The silver chain around Sirius’s neck caught in the light and Remus followed it down with his eyes, stopping on the curved pendant. “You got a new necklace,” he said carefully. He didn’t want to bring up Alphard’s locket and ruin the group’s good mood. “It’s nice.”

“Oh—yeah,” Sirius said, turning the pendant over in his fingers. “James’s mum gave it to me the other day. Picked it up in...Tibet, was it, Prongs? They travel all the time, his parents.”

“Our parents,” James corrected. His tone was casual, sliding the words in as easily as though he were giving the time of day, but there was something in his eyes as he and Sirius exchanged a look that suggested it was more significant than that.

Remus realized there was a lot being communicated between the two friends in that look; possibly an entire conversation, one he couldn’t hope to follow. He glanced at Lily, who smiled at him and shrugged as if to say, Don’t worry, I can’t always follow it, either.

After a moment, James turned his gaze to Lily. “Right, round two’s on us. The purple drink this time, yeah?”

As the two of them got up from the table and made their way over to the bar, Remus turned to look at Sirius. Now that they were alone, he said, “I shouldn’t have brought it up. I’m sorry.”

“No, don’t be,” Sirius waved it off. “I thought a lot about what you said: about my uncle, and about the shop. I’m...not alright with what happened, obviously, but.” He gave Remus a small smile. “It helped.”

“Oh. Good.” Remus’s eyes fell to the table for a moment, the tips of his ears warming at the softness in Sirius’s tone. He looked back up at the other man, one corner of his mouth turning up as he added, “Thank you for inviting me out. This is fun. Horrible cocktails aside.”

This drew a chuckle out of Sirius. “Yeah?” he said, eyebrows raising slightly.

“Yeah.” Remus glanced over at the bar, where James and Lily were chatting and waiting for drinks, and then across the room at Marlene, bent over the billiards table in concentration, and Dorcas, smirking triumphantly at the group of unhappy-looking men they’d been keen on defeating. “You’re so close with your friends,” he remarked, looking back at Sirius.

Sirius hummed, nodding, and ran a hand through his hair. “Like McKinnon said, we’re more like family at this point.”

“Is that what James meant about his parents?” Remus asked before he could stop himself. “Er, you don’t have to answer that.”

Sirius huffed out a laugh, taking the straw out of his glass to poke Remus’s hand with it. “It’s okay, Remus. Take off the kid gloves.” Remus rolled his eyes, and Sirius smirked at him before continuing. “You know we got tossed out, Alphard, Andy, and me. I was still living at school most of the year—I got to stay because the tuition was already paid for, which I’m sure pissed off my dear, sweet mother to no end—and James invited me to stay at his for Christmas and summer hols.”

Remus felt a coldness settle in his stomach as he processed what Sirius was saying. “Do you mean—they literally threw you out of the house? When you were still a child?”

“I was fifteen, I wasn’t really a child,” Sirius said, but it didn’t do much to dispel Remus’s horror. “And technically I ran away—I’d had enough. But, yeah, they disowned me after that. Legally and all.”

Remus clenched his jaw, feeling a swell of that protectiveness he’d first felt when Sirius was cut up about his brother and the locket. After a long moment, he said, “I really like James Potter.”

Sirius let out a surprised bark of laughter. “Me, too. All the Potters are brilliant. His mum and dad took me in, no questions asked. Treated me like a second son.”

“Is that why she gave you this?” Remus asked, touching the pendant over Sirius’s heart lightly with his fingertips. They were close, now, having leaned toward each other unconsciously while they were talking. Remus could just tilt his head down a bit, tip himself forward in his chair and… “Because she knew you lost your locket?”

Sirius’s tongue poked out to wet his bottom lip, his gray eyes darting over Remus’s for a moment before he spoke again. “Yeah,” he said, voice a bit quieter than before. “Her way of reminding me I’ve still got a mum who gives a shit.”

Remus felt a pang of self-pity as he pictured his own mother. He knew she would’ve done exactly what Mrs. Potter had done if he’d brought home this bright, charismatic boy who needed a family. He let himself imagine, briefly, introducing her to Sirius before pushing all his thoughts of her to the back of his mind. He realized he was still touching the locket and moved his fingers away to the hem of his own jumper. “You have a lot of people who give a shit about you,” Remus said, and because he had to make sure Sirius knew, he added, “Including me.”

“Yeah?” Sirius said, smiling so widely his nose scrunched a little before his mouth settled into what Remus had come to think of as his trademark grin. “It’s a good thing we get on so well, you know. For the kids.”

Remus grinned back, feeling the mood easing into something lighter. “Mhm. It’s important to give Riff Raff and Magenta a stable home life.”

As if on cue, James and Lily made their way back to the table. Marlene and Dorcas joined back up with them not too long after, Marlene bragging loudly about their victory and Dorcas quietly counting the money they’d hustled from their rivals. They stayed chatting until their drinks were done and Lily declared that she and James had to start making their way home to collect Harry.

On their way out, James stopped Remus by the door, letting everyone else pass them. “Hey, mate. What you did for Sirius after the run-in with his brother? That was ace.”

Taken slightly aback, Remus replied, “Oh. It was nothing, really. Well, his motorbike might’ve shaved a few months off my life, but.”

“Ha, yeah. Lily still refuses to get on the thing. But really, though. He’s put a lot of it behind him, the stuff with his family, but Regulus is a sore spot. Probably the biggest. They were really close when they were kids.”

Remus nodded, frowning in thought for a moment. “Maybe it’s not too late for them,” he said.

“Yeah.” James seemed to consider the likelihood of that, shrugging as he added, “Maybe.” He gave Remus a pointed look as he continued. “Thing is, he’d normally have been in a strop for days over something like that. He was still upset, but—whatever you said to him straight after, it helped loads. There aren’t too many people who could do that.”

Remus looked away briefly as he tried to process what James had said. He was obviously telling Remus something important; he’d waited until they were alone to have this heart-to-heart. Whether James was simply thanking him for being a good friend to Sirius, or was implying something beyond that, though...Remus couldn’t be sure.

“Anyway,” James said lightly before Remus could come up with a response. “Let’s get out of here before they catch a train without us.”

They caught up with the others on the street, walking to the station together before saying their goodbyes. Remus laughed and waved as Marlene, Dorcas, Lily, and James broke out in a final chorus of “come and hang out again!,” “next round’s on you!,” and, from James, “just wait ‘til our American Thanksgiving feast!” before they rounded the corner for their platform.

He fell into step beside Sirius as they walked off to wait for their own train. “Does James have a fascination with every U.S. holiday?” he asked.

“Remus, if I didn’t know better, I’d say you weren’t excited to try a fried turkey wrapped in bacon.”

“A what?”

“And cranberry sauce in a can!”

“Every day, we stray further from God’s light.”

When they reached their platform, Sirius suddenly rummaged through his pockets as if just remembering something. He brandished two chocolate bars with triumphant flourish, handing one to Remus. “Best part of Halloween,” he said, unwrapping his own. “The candy.”

Remus had finished half the bar in the two minutes it took for the train to arrive. “Now the brownies make sense,” Sirius said slyly as they got on. He leaned on a pole, crossing one ankle over the other as Remus took hold of the one opposite him. “You’ve got a sweet tooth, Lupin. Didn’t like those drinks, though, eh?”

“I like chocolate,” Remus corrected, trying to sound dignified with his mouth full. It made Sirius laugh.

“I can see that. You’ve got a bit, er,” he gestured toward the corner of his mouth. “Just there.” Remus’s hand flew up to his face, swiping at it until the smudge was gone.

They got off in Maida Vale. Remus’s flat was walking distance from the station, but Sirius had taken his bike there. “Ah, fuck. I don’t have the spare helmet on me. Could’ve driven you home,” he said regretfully.

“It’s okay,” Remus replied. “It’s a short walk.”

“...I’m never getting you on my bike again, am I.”

“Anything’s possible.”

Sirius huffed out a laugh. “We’ll work on that. ‘Night, Remus.”

This time, it was Remus who drew Sirius into a hug. It wasn’t fierce like Sirius’s had been, and it was over far too soon, but Remus met his eyes and smiled softly as he pulled away again. There was a lot he wanted to say, but he settled for, “‘Night, Sirius.” Before he left, Sirius beamed back at him, biting his bottom lip lightly, and Remus thought he might’ve said enough after all.


\newpage

%Chapter 6
\fancychapter{29 November}{Remus is filing this day under "Reasons Why I'm Single."}

IT WAS A COLD FRIDAY AFTERNOON in late November—properly cold, the kind of chill that worked its way under every layer of clothing to settle in one’s bones. Remus rubbed his hands together after setting the last crate in the back of Frank’s van, trying to stimulate the feeling back into his fingers. Beside him, Frank snapped the back doors shut and fished his keys from his coat pocket, breath leaving him in white puffs.

“That’s everything, yeah?” he asked, turning to look at Remus. The apples of his cheeks and tip of his nose had gone pink from the bitter wind.

Remus nodded, giving up on the rubbing tactic in favor of shoving his hands deep into the pockets of his own winter jacket. He deeply regretted not bringing a pair of gloves to work that morning. “Thanks, Frank. Headed home after this?”

Frank opened the driver’s side door and turned the key, switching the heat on as soon as the engine purred to life. “Yep. Cooking dinner, watching Moana for the hundredth time, the usual.” He was smiling, though, like there was nothing else he’d rather be doing. It made Remus smile, too; he imagined Frank and Alice curled up on their sofa with Neville, the two-year-old entranced by the movie as his parents watched on fondly. “What about you? Any plans?”

“Er, yeah,” Remus said. “I’ve sort of got a date.”

“No way, you finally asked Sirius out?” Frank clapped him on the shoulder, excitement lighting up his face. “Good on ya, mate! He did give me a tour of his shop, did I mention? Even dug out the original building plans for me to look at. Cool guy, just a real cool guy.”

“No, no,” Remus said quickly. He’d been trying very hard all day not to imagine exactly that. “It’s not with—it’s a blind date. Mary set me up with one of her coworkers at the marketing firm.”

A sheepish look passed over Frank’s face as he realized his mistake. He rubbed at the back of his neck as he said, “Oh. Well. This is a bit awkward.”

Remus had to laugh a little at that. “It’s okay. I should go lock up, at any rate. See you later.”

“Later, Remus,” Frank said, climbing into his van and pressing his hands against the vents on either side of the wheel, letting the warm air blast over him for a moment before shifting from park to drive. He stuck his head out the window, added, “Good luck!” and pulled away.

Truth be told, Remus was still trying to muster up some excitement about said date. He still wasn’t sure why he’d even said yes to Mary in the first place. They’d met up for coffee last week and, while on the topic of her job, she’d sung the praises of one of the young executives she worked with, lamenting the fact that he was apparently gay.

“He’s so handsome,” she’d said, stirring sugar into her coffee and sighing wistfully. “His smile is, like, blinding. And he’s got great hair. And he’s a published author and motivational speaker, did I mention that? He was on Graham Norton a few months ago.”

In the end, Remus had agreed to meet the guy for dinner. He didn’t have any good reason to say no, after all; he was very much single (despite having spent the past two weekends with a certain hot tattoo artist and his band of rowdy, lovely friends), and Mary would probably leave the subject of his love life well enough alone for at least a couple of months after this. It was only dinner. Maybe this published author would even offer to pay, Remus thought wryly as he closed up shop.

It was only half past four. Thinking he’d kill a little time before going home and then onto the restaurant, Remus popped into Sirius’s shop, the familiar front room putting him at ease. Andromeda was swapping out a few of the framed photos on the far wall, but stopped when she caught sight of Remus, setting the frame in her hands down on a nearby sofa and going over to greet him.

“Hello, darling,” she said cheerfully, brushing her long hair away from her face. “Sirius just popped out, I’m afraid. Getting his shopping done. Did you need anything?”

Remus shook his head, trying to keep the disappointment off his face. “No, just saying hi before I get going.” He glanced at the framed pictures scattered about, and added, “Want a hand?”

And that was how Remus ended up on a stepladder in Black Dog Tattoos, hanging photos of Sirius’s—well, artwork, really, just the kind that went on people’s skin—on the brick wall of the shop while Andromeda dictated where each one should go.

“You’re a hero,” she said as Remus straightened a particularly high-up frame. “I couldn’t even reach that with the ladder. You’re so bloody tall!”

“Comes in handy from time to time,” Remus said with a laugh. Andromeda began sweeping up by the front door as Remus got down and adjusted the lower rows of pictures. He noticed that, while there were several new pieces he’d seen on their Instagram, there weren’t any photos of the Avengers cast tattoos Sirius had done a few months back.

“I suggested it, believe me,” Andromeda said with a sigh when Remus asked. “That job got us so much attention. But,” she shrugged. “Sirius nixed it. Said he didn’t want to use their fame for his own benefit, or something of the sort. He can be annoyingly noble about the weirdest things.” A small smile tugged at her lips despite her complaints. “At least he let me repost some of the actors’ pictures on social.”

Remus felt a rush of fondness for Sirius. He was glad his back was to Andromeda; god knows what his face was doing. “Eh, he’s probably just hoping for a date with Captain America,” he joked, which pulled a laugh out of Andromeda.

“I must admit, he has good taste in men. He’s constantly fawning over my husband,” she replied. “Never can tell if he’s joking.”

After a few minutes, they perched on the sofa next to each other, tasks completed. “How did you meet?” Remus asked. “You and Ted, I mean.”

Andromeda smiled softly as she glanced down at her wedding ring. “I saw him standing outside my window.” She chuckled as Remus raised an eyebrow. “I was sixteen, home from school for the summer holiday—I went to Hogwarts, too, my whole family did. My parents were having their gardens redesigned, and there were landscapers roaming about for what felt like the entire summer. Ted was working for them at the time; he was on holiday from school as well.”

Remus could picture it: a young Andromeda, beautiful and bored on her family’s sprawling estate, suddenly catching sight of one of the boys working under the summer sun. “That’s quite...fateful,” he said. He wasn’t sure if he believed in fate, not really, but it was at least...unlikely, their meeting.

Andromeda hummed in agreement. “We spent that summer sneaking about, trying to keep my parents and both my sisters from finding out. I got very good at climbing in and out of windows.” She shook her head, smirking. “The middle sister of a stuffy old English family who was meant to marry for status, not love, and the handsome working-class bloke who stole her heart. It was all very Jane Austen.”

Remus wondered about her sisters—if they’d also strayed from the path their parents set out for them to follow their hearts. But Sirius had told him that he, Andromeda, and Alphard were the only three to be disowned from the Black family, hadn’t he? That there were only three Black sheep. He wondered how Andromeda had weathered the fallout that came with her choice in husband. Was it a slow unraveling, or did they just shut her out, point blank? Did her sisters secretly miss her the way Regulus (Remus suspected) missed Sirius?

Whatever the case, one thing was clear: “He must’ve been more than just handsome, for all that trouble,” Remus said with a small smile.

“You’re right,” she agreed. “He was...dorky, really, is what he was. But he pulled it off somehow. Part of his charm. It didn’t hurt that he looked at me like I was Venus standing in the seashell.” She paused, tucking some of her dark, silver-streaked hair behind her ear and pursing her red-painted lips. Her eyes were clear and sure as she added, “Ted was worth all the trouble. Every bit of it. When you find someone who makes your heart sing like that, it’s worth all the trouble in the world.”

She said it lightly, but her words hit Remus square in the chest, and he blinked at her for a moment, lips parted, as he tried to come up with something to say to that. He’d spent years doing the exact opposite—avoiding trouble wherever he could. He was doing it even now, today, as he left to have dinner with a stranger rather than waiting for Sirius.

Which reminded him. He checked the time on his phone, jumping to his feet and telling Andromeda apologetically, “Shit, I’m going to be late. So sorry, Andy, but I have to run.”

She walked him to the door, giving him a goodbye cheek kiss before he ducked out into the cold evening air. He had just enough time to stop home and change into a decent pair of jeans, a checked shirt, and a black cardigan under his coat (and gloves, which he remembered this time) before taking a train to the gastropub where he was meeting his date. The place was gratingly trendy, the overpriced food and ultra-modern decor designed to look good on social media. Remus had never been there; he doubted he’d ever be back.

He was just about to text Mary and ask for a picture of the man he was meeting when he found himself suddenly staring down a head of professionally styled, platinum-blond hair and a pair of blue eyes. “Remus Lupin, I presume?” he asked. He smiled, revealing two rows of perfectly straight, white teeth.

“Oh,” Remus said, a little startled by the sudden invasion of his personal space. “Yes. That’s me. And you’re...Gilderoy, right?”

“Gilderoy Lockhart,” the other man said, shaking Remus’s hand with confident firmness. His hand lingered just a moment too long for Remus’s liking. “But I’m sure you know that. Shall we sit?”

He strode toward an empty table without waiting for an answer. Remus followed, taking in Gilderoy’s outfit; the man was wearing a plum suit that looked custom-made with the intention of showing off how fit he was. His trousers were cropped, showing a lot of ankle and—were those yellow suede loafers? They sat down across from each other and Remus offered the other man a small, polite smile.

“So,” he started. “Mary says you’re writing books or giving lectures when you aren’t consulting at the firm. Sounds quite busy.”

This, he soon realized, was the wrong thing to say. Gilderoy took the question as an open invitation to talk about himself, without pause, until the server arrived to take their drink orders. As Remus found out, he’d written three books; two that fell into the self-help genre and had sold extremely well (he made sure to emphasize that point) and an autobiography which had made the bestseller list last year and spurred all the media attention. Attention which Gilderoy seemed to have taken to like a fish to water.

“Once I started giving interviews for the book, people just wanted more and more of me,” Gilderoy said with a chuckle and a little head shake that Remus thought might have been an attempt at modesty. “I was a guest on a few podcasts—I’ll send you the links—before I realized that wasn’t my preferred medium. I wanted people to see me, not just listen to a disembodied voice on their phones. My message comes across so much clearer that way.”

Yes, it’s very obvious you want people to see you, Remus replied in his head. What he actually said was something far less snarky—something along the lines of, “Do you travel often, then? As a speaker.”

“Oh, here and there,” Gilderoy replied. “My agent keeps insisting on another book, then a book tour, but the firm keeps giving me these projects I just can’t turn down! They fall apart without me. So it’s been dreary old London for months on end, I’m afraid.”

Remus felt a smidge of defensiveness on his adoptive city’s behalf. “I don’t know, London can be quite nice,” he replied. “Freezing at the moment, but. Nice.”

The server came back with their drinks—a complicated herb-infused sparkling water concoction for Gilderoy, and regular water with a slice of lemon for Remus. “Are you ready to order?” the young woman asked, flipping open a pad and clicking a pen.

Neither of them had given more than a cursory glance of the menu, as Gilderoy hadn’t let up talking since they’d sat down. The blonde man didn’t seem to need to familiarize himself with it, though, and looked up at the server to say, “We’ll have the kelp noodles with a side of roasted sunflower seeds.” He glanced back over at Remus. “I haven’t had carbs in two years. The camera adds ten pounds, as they say!”

Remus, who’d immediately bristled at the thought of someone ordering for him—particularly someone who knew nothing about what he liked and disliked—took his turn anyway, looking up at the still-hovering server by their table. “I’ll have the burger,” he deadpanned, watching Gilderoy’s confident expression waver in the corner of his vision as their order was scribbled down and the server left them alone again. He was going to have a chat with Mary very soon about setting him up on any more blind dates.

“A man who knows what he likes,” Gilderoy said, fixing Remus with a beguiling smile once more. “I like that.” The annoyance in his eyes said otherwise. He continued, “What is it about London that attracts you?”

Remus paused for a moment, considering the question. “It’s always felt like home, from the day I moved here. It’s been ten—hm, no, twelve years?” It was true; he liked the anonymity of the busy streets and the familiar friendliness of his neighborhood, he liked the noise and the pulse of life that never seemed to ebb, he liked the hidden corners and major landmarks and everything in between. Except, perhaps, trendy gastropubs. “Living and working in Maida Vale, by the canal, is lovely.”

“Yes, Mary mentioned you’re a business owner. A flower shop, is it?” Gilderoy said. Remus nodded, but Gilderoy carried on before he could get a word in edgewise. “Well, I do like a bouquet of fresh roses. They do tend to turn up in my dressing rooms. When I did Graham’s show in January—” Remus had to physically stop himself from rolling his eyes at the first-name-only name drop, “—Some of my fans had sent a few dozen backstage. I left a few for the crew, absolutely made their day.”

If Remus took more than a little satisfaction in sinking his teeth into his dripping hamburger while Gilderoy pretended to enjoy his bowl of kelp, he couldn’t be bothered to feel badly about it. The man was insufferable. Remus might’ve gotten up and left altogether, politeness be damned, if he hadn’t been Mary’s coworker. He didn’t want to cause any awkwardness in the office for her, even if she had set him up with a human peacock.

“Tell me, Remus, do you date much?” Gilderoy said halfway through their meal. At Remus’s raised eyebrows, he added, “Mary mentioned something about you keeping a busy schedule, and I know it’s been a hell of a challenge for me to find time in my life for someone special.”

“Well, I do run my own shop, humble as that may be,” Remus replied dryly. “Tends to keep a person occupied.”

Gilderoy nodded solemnly like he understood exactly what Remus meant. “Yes, of course. I know what it feels like to have people demand so much of your time. It…”

“Makes you want to clone yourself so you can get drunk in Ibiza while the clone stays here and does your work for you?” Remus said, paraphrasing something Sirius had said a few months back.

This startled a short laugh out of Gilderoy, but he looked at Remus with a funny expression afterwards, like he didn’t quite know what to make of him. “Hm, Ibiza. It’s a nice place to spot Ronaldo in very tiny speedos, but I prefer Mykonos myself.”

Remus instantly regretted saying it, because quoting Sirius led to thinking about Sirius, which led to imagining what it would be like to be sitting here with Sirius on a dinner date, surrounded by influencers and £20 avocado toast. He would hate the place, too, Remus thought. He’d propose they get out of there before they’d even ordered a drink, and he’d take them to some Chinese takeaway with two folding tables and peeling paint inside. Or they’d order a pizza and eat it while walking along the canal, Sirius singing Bowie loudly and off-key, Remus jokingly threatening to wipe his pepperoni-greased fingers on Sirius’s leather jacket.

Blinking, Remus realized Gilderoy had stopped talking and was now looking across the table at him expectantly. “Oh, er,” he fumbled. “Sorry. What was that about Mykonos?”

But Gilderoy just chuckled, leaning in slightly and gazing at Remus fondly. “No need to apologize, Remus,” he said with a knowing smile. Remus’s eyes widened as he tried to discern whether Gilderoy knew—how he could possibly know—that Remus had been thinking about someone else. “I’ve seen that faraway look more than a few times. I’m flattered.”

Oh. Of course. Remus almost wanted to laugh, because of course Gilderoy thought he’d been ogling him.

“You’re rather handsome yourself,” Gilderoy added to Remus’s mild surprise. But Remus’s “thank you” was lost as Gilderoy followed up with, “You’d catch my eye in any crowd, even with the scars. You have more than enough going on to make up for them.”

Remus’s stomach dropped to the floor. It had been so long since anyone had even mentioned his scars—never mind with that level of insensitivity—that it threw him off-balance. He stared numbly at Gilderoy for a long moment. In addition to the long, thin scar that ran across Remus’s nose and left cheek, a few others were visible or partially visible to Gilderoy; three short, thick gashes under his jaw by his ear, and another on the side of his neck, trailing down beneath the collar of his shirt.

“How did you get them?” Gilderoy asked, undeterred by Remus’s silence.

“Bar fight,” Remus lied, just to shock him. His eyes flashed with anger even as he smiled. “You should see the other guy. You’ll have to visit him in prison, but I’m sure he’ll give you the story.”

Unsurprisingly, the date ended rather quickly after that. Gilderoy did pay the check in full, at the very least. They parted under the awning of the restaurant with nothing more than a handshake, and Remus marched to the Tube station, cramming himself in the last available seat on his train home. By the time he’d reached his flat, he was flipping between letting himself be upset and scolding himself for allowing the bad date to ruin his day.

You are an adult, he thought chidingly as he slowly shed his clothes in the dim light of his bedroom. You aren’t letting a ponce like Gilderoy Lockhart fuck with your head.

After pulling on his oldest and most comfortable hoodie and a pair of sweatpants, Remus padded into his lounge, curling up on the sofa with a cup of chamomile tea and a book he’d read a dozen times before. He flipped through the dog-eared, slightly yellowed pages and sighed, feeling distinctly off. Gilderoy Lockhart was a self-obsessed twat, yes, but he’d also struck several nerves. Remus had had his scars for close to ten years, but he was still sensitive about them. But even worse than what Gilderoy had said about that was the implication he’d be dating Remus despite his scars. Despite his baggage. He’d been told that once before, which made the subsequent abandonment all the worse...

He flipped to another chapter, stubbornly pushing away the train of thought. He hadn’t intended to fall asleep on the sofa but an hour later, he was drifting, tea going cold on the table and book dangling precariously in his hand.

Bright lights. Beeping. A throbbing pain behind his eyelids and heaviness in his limbs.

He’s in a hospital, the beeping rising to a fever pitch as panic wells up within him. A nurse, a dose of something, then sleep.

Then his father, purple under the eyes, slumped in the folding chair beside his bed. His voice, scratchy and strained, trying to explain it all to Remus. Drunk driver, he says. Head-on collision. You were crossing the road.

And the nurse, telling him things like: broken femur, fractured radius, cracked ribs, punctured lung. Saying things like: lucky to be alive.

Then Michael’s sitting in the chair. Holding his hand, brushing his lips across Remus’s knuckles. He has a scar on that hand, now. He has scars everywhere.

I’m here, baby, he says.

Until weeks later, when he’s not. Until Remus is off the heaviest of the drugs and aware and in pain. Until he’s struggling to heal his scars, visible and not.

He cries out for his dead mother one night in the hospital bed. Screams and sobs and shakes like a child, craving a comfort he can’t have.

It’s only a few days after that when Michael sits in the chair one last time. Kisses his knuckles one last time. He looks tense, distant. Remus doesn’t understand.

Michael is there, telling him things like: can’t do this anymore, too much, won’t work between us. He’s never been the best at emotional support, and Remus is carrying so much weight, now, his knees are buckling with it.

Michael is there, telling him things like: goodbye, Remus.

And then he isn’t.

Remus bolted upright, gasping for air and covered in a thin sheen of sweat. After a few seconds, reality crept back in and he dropped his head back against the sofa, catching his breath. He hadn’t dreamt of his accident or Michael in ages. Fumbling for his phone, he saw that it was half past two and groaned.

He dragged himself off the sofa and stripped off his hoodie before climbing into bed. He stared at his phone on the nightstand and debated. Alice didn’t get much sleep with a toddler at home. He’d scare his father half to death if he called at this hour. Peter wasn’t the greatest at emotional support, and he was a little pissed off at Mary over the setup with Gilderoy.

His mind went to Sirius, and his phone was in his hands with the message app open before he even really registered the thought. He stared down at their text chain. The last thing Sirius had sent him was a selfie; in it, he was grinning at the camera, face smudged with dirt and some blood from a split lip and James shouting beside him, arms slung around each other. The caption read,

You’re looking at the OFFICIAL Hogwarts alumni football champions!!! LONG MAY WE REIGN.

His thumbs hovered over the screen for a long moment before he shook the thought, setting his phone down and rolling over onto his other side. The remainder of his night’s sleep, when it came, was mercifully dreamless.

\newpage

%Chapter 7
\fancychapter{30 November}{Remus's secrets take their toll.}

“THAT’S A GOOD LOOK FOR YOU, MATE. A real improvement.”

Sirius looked up at the comment and grinned, blowing a few strands of hair that had fallen out of his bun away from his eyes to give James the full effect. He was sitting cross-legged and barefoot on the floor, dressed only in jeans and a loose tank top with the Hogwarts school crest in the middle. His shoes were lying in a pile by the front door of the Potters’ lounge and his hoodie was slung over an arm of the sofa, rays of afternoon sunlight streaming in through the windows and casting the room in a warm glow.

Harry, sitting on the floor beside him, had spent the better part of the past twenty minutes using finger paint to color over the tattoos on his godfather’s arms. Sirius was now covered in the stuff, colors bleeding into each other in places and forming muddy streaks on his skin from shoulder to wrist. His face hadn’t escaped unscathed, either; he had blobs of red on his cheeks and nose and a mudge of blue across his forehead.

“What can I say? The kid has artistic vision.” Sirius ran a hand through the baby-soft tufts of black hair sticking out in all directions on the toddler’s head. “Oi, Harry, your dad looks like he could use some color. What do you think?”

Harry’s fingers stilled where they were smudging green paint against a paw print tattoo just below Sirius’s elbow. He looked from Sirius to James before declaring, “Dada pink!”

Sirius nodded solemnly. “Yeah, pink. That’s his color. C’mere then, Prongsie.”

“Only if you make me look prettier than Uncle Padfoot,” James said as he got down on the floor to join them.

“He’s an artist, James, not a miracle worker,” Sirius replied as James rolled up his sleeves, his son already slamming his tiny fist into the bowl of pink paint.

Lily pushed open the door a few minutes later, keys and a pair of grocery bags in hand, to find her husband, her son, and Sirius sitting in a circle in the middle of the lounge, all of them looking like they’d recently lost a fight with an art supply closet. She started to laugh, shaking her head at the sight of them.

“Oh my god, you three. I was gone for half an hour. Your tattoos have never looked better, though, Sirius.”

“That’s what I said!” James replied, tilting his head back at the same time Lily bent down to catch each other’s lips in a welcome-home kiss. Lily kissed Harry’s nose next, narrowly avoiding his paint-wet hands as they reached out to grab her long hair. She rolled her eyes as Sirius pursed his own lips into a dramatic pucker, but dropped a kiss to the top of his head anyway.

“Right then. Gonna put this stuff away—” Lily said, giving the bags in her arms a little lift, “—then I’ll give this wee monkey a bath so you lot can de-paint yourselves. Staying for dinner, Sirius?”

Sirius nodded, relishing the fact that he could stay as long as he wanted without work pulling him away. It was Saturday, and he’d made the extremely rare move of taking the entire day off, full stop. He hadn’t even checked his emails. Andromeda had promised to do any necessary juggling with his appointments and had all but pushed him out the door Friday night, telling him to get some fucking rest, look at the state of you.

He’d had an indulgent lie-in, rolling out of bed just after eleven. He’d then tackled a few errands he’d been putting off before driving over to the Potters’ Hampstead flat. Even when he was chasing Harry all over the house or helping James and Lily cook, he felt like he was resting, in his own way. It was his favorite place to be apart from his shop, his bed, and his garage, tinkering with his motorbike.

Sirius and James tidied the lounge as Lily put away the shopping. Once she had taken Harry upstairs for his bath, the two men crowded around the kitchen sink to clean themselves up. James coated a sponge in warm water and dish soap and started in on his left arm.

“You’re gonna have an apprentice for the shop someday soon—Harry’s obsessed with mimicking you,” James remarked as he scrubbed his skin. He’d said it lightly, conversationally, but Sirius leaned against the counter and narrowed his eyes, peering at James as if trying to see straight through into his brain. “Oi, what’s with the look?”

“If I’ve got a look, it’s because you’ve got a look.” Sirius gasped suddenly, snapping his fingers. “You’ve got that look.”

“What look?”

“That look! The ‘I’m-about-to-make-a-big-life-decision-and-need-to-tell-Sirius-about-it’ look.”

James flicked his soapy fingers at Sirius. “There’s no way I have a look that’s that specific.”

Sirius swatted a hand through the water running from the faucet, splashing James with the spray. “You do, you do! Remember how I knew you were about to tell me you bought Lily a ring? And how I knew you were about to tell me she was preg—holy shit, is she pregnant again?”

“No, no. Wait, that’s how you knew?”

Sirius nodded smugly. “That same look on your face, both times.”

James glanced over his shoulder toward the front of the house, then grinned at Sirius as he said, “Don’t let Lily hear you. Remember when we convinced her we could read each other’s minds in year six? Pretty sure she still believes it.”

James gave a few more passes of the sponge up and down his arm while Sirius just watched him, knowing any remaining pretense was about to be dropped. James let the sponge fall into the sink as he turned toward Sirius, his eyes bright, and said, “Okay, so.”

“Knew it!”

“Sod off,” James said, huffing out a laugh. He lifted a hand to reflexively ruffle his hair before he caught himself, remembering it was still dripping wet. “So. Lil’s not pregnant, but. We were thinking of giving it a go.”

Sirius’s eyes darted between James’s own as he studied his best friend’s expression. “Yeah?” he asked, a grin slowly spreading across his face. “Bambi the Second? This time planned and all?”

That pulled a loud laugh out of James. He punched Sirius’s shoulder, beaming as his excitement took over. “What do you say, Padfoot? Are you willing and able to render all godfatherly services for two Potters?”

“Fuck yes,” Sirius exclaimed, pulling James into a soapy hug. “Course, Jamie. Course I will.”

The wet handprints on the back of his tank top had mostly dried by the time they’d both gotten cleaned up. He was patting his face with a towel when James said, “Kay, your turn.”

Sirius cracked an eye open to peer over the towel at his best friend’s smirking face. He tossed it aside and pulled out the elastic on top of his head, shaking his head like a dog as his hair fell down around his face and shoulders. Finally, he replied, “I haven’t asked him yet.”

James made a noise of frustration. “Fucking hell, man, it’s been months! He’s met the whole family—well, except our parents, but like, everybody else. You’ve played with Harry together, for god’s sake. You’re practically a couple already.”

“I know,” Sirius groaned, pushing himself up to sit on the counter and throwing his hands in the air. “But he can be so bloody hard to read! Sometimes I think he’s flirting back, but then I think I’m just hearing what I want to hear, you know?”

James nodded and sighed, patting Sirius’s shoulder. “Remus has got that whole mysterious thing going on, I’ll give you that. Nicest bloke in the world, surprisingly wicked sense of humor, but doesn’t really talk about himself unless you pull it out of him.”

“Not about personal shit, anyway,” Sirius agreed.

“Right. But let’s look at his actions rather than his words—or lack thereof. He spends a lot of time with you. He was there for you during the latest Black family drama. He’s told you he lives alone and he’s never introduced you to a boyfriend. And he looks at you like you look at your motorbike.” James, who’d been counting on his fingers, put his hands on his hips as he declared confidently, “Conclusion: he wants a piece of that arse. Lily thinks so, too, by the way. And she thinks you’d be a fool not to go for it.”

Sirius let his head fall back against the kitchen cabinet with a dull thud. “I’m waiting for the right moment. I don’t want to fuck this up, Prongs. Remus is…”

“Special, I know,” James said, nodding at the sentiment he’d heard from Sirius before. “Just don’t wait forever, yeah? You got this, dude. You’re the smoothest motherfucker I know.”

Sirius tipped his chin up, smirking. “Yeah. Yeah, you’re right. I’ll ask him out soon. Maybe when I’m less distracted by those freckles of his. Or that fucking dimple when he smiles, oh my god.”

“Uncle Padfoot has it bad, doesn’t he, love?” Lily crooned to the toddler in her arms from where she was standing in the doorway. “Pa’foot!” Harry cried in surprise, delighted to find his godfather still downstairs.

“That’s a yes, by the way,” James said.

--

Remus, usually an early riser from years of habit, only woke up Saturday morning when his very last emergency alarm went off on his phone. “Fuck,” he muttered into his pillow, knowing he’d have to scramble to leave his flat on time but too tired to move all that quickly.

He’d only gotten a few hours’ sleep after the series of nightmares that had plagued him the night before, and he was feeling it now, blinking blearily at himself in the bathroom mirror as he brushed his teeth and splashed water on his face. He didn’t have time to shave. He was halfway out the door before he realized the dark blue jumper he’d paired with brown shoes and tan trousers was inside out, the tags visible at the sides.

He locked up his bike outside the shop just before eight. Alice was already inside sorting out the register, and she frowned at him as he walked in.

“You look terrible,” she said by way of greeting, a look of concern furrowing her brow.

“Cheers, thanks,” Remus said with a sarcastic wave.

A cup of tea—strong, black, and brewed almost immediately by Remus upon entering his office—wasn’t cutting it on a day like this; he only made it until nine before he was ducking out to pick up a coffee from the cafe two blocks over. His disastrous date with Lockhart the night before and subsequent night of rough sleep had left him worn out, annoyed, and highly distracted. He spent the morning trying to keep himself busy and avoiding Alice’s worried gaze.

Alice finished ringing up an order for Mrs. Lawrence from the historical society around half past ten, leaving the shop empty save for her and Remus. Seeing an opportunity, she looked over at him from behind the counter and said, “Are you ill, Remus? It’s a slow day. I can take care of things here.”

Remus shook his head, continuing to water the shelves of perennials. “I’m fine. Just tired.”

Alice sighed, tilting her head as she considered him. “If I had a pound for every time you said you’re fine when you’re not, I could buy this building.”

Her tone was gentle, but Remus just frowned, still not looking at her as he kept his hands busy with the watering can.

“Does this have anything to do with the date Frank mentioned you were going on last night?” she continued.

That got Remus to pause and look across the room at Alice. “No,” he said. “Sort of. It’s not a big deal. I really am tired, Alice.”

“I can see that you are, but you’re also clearly upset,” Alice replied. She knew Remus had an extremely long fuse; in all the years Alice had known him, she could count the number of times she’d seen him truly upset on one hand. But when his fuse did finally burn out, she’d always pressed and insisted until he came out with whatever it was that was eating at him. “No need to be stoic about it, it’s just me.”

“I’m not being stoic,” Remus said, hating how he sounded like a petulant child even to his own ears. “There’s nothing to talk about. I had a shit night, and I just want to get through the day and go home and sleep.”

A look of alarm passed over Alice face as she lowered her voice to ask, “Remus, he didn’t...do anything to you, did he? I mean, you’re okay?”

“Christ, Alice, I’m fine,” Remus snapped, narrowing his eyes as the last threads of his patience began to unravel. “Can’t you drop it?”

“You don’t have to jump down my throat for worrying about you,” Alice retorted, crossing her arms. “I’m asking if this guy hurt you, Re.”

“Well, he didn’t. He was just your run-of-the-mill insensitive, condescending, narcissistic prat.” Remus set the watering can down forcefully. Water sloshed out from the top of the can, spilling over the shelf. “Oh, fucking hell.”

He pulled a rag from his back pocket to mop up the water, his jaw tight. To his horror, he felt the burn of tears threatening to well up behind his eyes. Alice must have heard it in his voice, because the next minute she was marching over to the front door with purpose.

“Okay, you know what? We’re pressing pause on this day,” she said, turning the lock with a loud click and flipping the “Out to Lunch” sign so it was readable from the street.

“It’s 10:45,” Remus protested weakly as Alice steered him by the elbow until they stood behind the front counter. She slid down to the floor, sitting cross-legged with her back against the wall. She then looked up at him expectantly before he gave a resigned sigh and sat down next to her, mirroring her position.

“This is ridiculous,” he said, shifting so that his long legs lay straight out in front of him. He was grateful for the location despite himself; the counter shielded them from passersby, giving him a sense of privacy.

Alice covered his hand with hers, her eyes sad. “What was he insensitive about?” she asked.

Realizing that Alice would not let it go until he gave some explanation, he recounted the events of the previous night, carrying on mostly uninterrupted except for a few incredulous questions from Alice.

“And then he said he thought I was fit despite my scars,” Remus concluded after a few minutes. Alice tensed beside him. “Oh, and he asked what happened to me. That was basically the end of it.”

“What a fucking arsehole,” Alice said, shaking her head. “What did you say?”

Remus’s lips twitched. “Bar fight. And that the other guy’s in prison.”

Alice blinked at him in surprise before she laughed. “God, I love you.” The levity of the moment gave way to the weight of emotion underneath, and she added, “You know that’s a load of shit, right? Your scars aren’t an entry on some pro/con list. You’re gorgeous, full stop. No footnotes.”

“So you’ve told me,” Remus said, smiling sadly as he looked up at the ceiling. “It’s not even that—it is what it is, I’m getting used to them, mostly—it’s just, I had awful dreams about the accident afterwards.”

He swallowed around the painful lump that had been lodged in his throat since he’d spilled the water. Alice waited in patient silence for him to continue. “I haven’t dreamt about it that vividly in ages. About waking up in hospital and Michael leaving. And my—my mum, too.” He paused for a long moment, looking from Alice’s eyes to her hand where it rested on top of his own. “It woke me up in the wee hours and…”

He trailed off for so long that Alice prompted, “And?”

“I almost texted Sirius,” he quietly admitted at last.

“I see. Have you told him anything about your accident? Or Michael, or your mum?”

“No.”

Alice blew out a long breath, shifting so her body was facing Remus. She studied his face for a moment before she spoke. When she did, her tone was kind but firm. “Remus, you are such an amazing person. No, listen to me.”

Remus, who’d looked away at the compliment, turned his gaze to hers again.

“You hired a 21-year-old runaway with no degree, no job, and no references living on a council estate. You trusted me with this place, and since then you have always been there for me, no matter what. You’ve supported my education more fiercely than anyone, apart from Frank. And after we had a baby and he was looking for a second job, you created a driver position for him.”

“The shop needed someone—”

“I know, but you didn’t have to hire Frank. You didn’t have to shape your entire delivery system around his teaching schedule.” She gave Remus’s hand a squeeze. “You’re so quick to say how much we’ve helped you, but look at what you’ve done for us.”

“You’re my friend. Both of you.”

“That’s my point. You do everything for everybody else, but when you’ve got a burden to bear, you don’t let anyone help you carry it.” She smiled at him sadly. “You bottle it all up until you’re drowning in it, Re. Like right now. You’ve needed to cry for the past twenty minutes, but you just won’t let yourself.”

Remus felt the last pieces of his mental scaffolding crumble and fall away. A tear slid down his cheek, beading on the edge of his jaw before falling onto his jumper. He swore under his breath, scrubbing a hand down his face in one last useless attempt to hold it all back. Alice put a comforting arm around him and let him quietly fall apart, his head bowed and his eyes tightly shut.

Alice, as usual, had surprised him with the depths of her perceptiveness. She was right; he had been bottling up his feelings for too long, far longer than just one night. He filled his lungs with air, holding the breath in for a moment before letting it out in a slow, shaky exhale. When he looked at her again she offered him a small smile. “Feel a bit better?”

“A bit, yeah,” Remus admitted. He gave a watery laugh as he dried his face on his sleeve. “I kind of feel like your second son at the moment, but.”

“Oh, come off it, Remus,” Alice laughed, nudging him as she removed her arm from his shoulders. “Everyone needs a good cry now and then. Even you.”

She watched him as he shrugged, looking noticeably less tense than he had before they’d sat down. “So,” she said with an air of casual interest, looking down as she smoothed out the panels of her striped midi skirt. “Sirius, hey?”

Remus felt his heart pick up speed at the mention of him. He nodded, running absent-minded fingers over the hem of his jumper.

Alice cast him a sideways glance. “Maybe you should go to dinner with him next time.”

Remus felt the familiar refrains of denial bubbling up in his throat: it’s not like that, we’re just friends, I’m not pining. He’d been telling her (and himself) as much since the end of summer. But Alice was looking at him like she was hoping with all her might that he’d say otherwise, and maybe it was that—maybe it was his exhaustion, or the crying jag, or a combination of all those things—but he couldn’t find it in himself to lie about it anymore. Not to her.

“I wanted it to be him,” Remus said quietly. It was the closest he’d come to an admission of his feelings for Sirius since the day they’d met, and Alice has to bite the inside of her cheek to keep from beaming.

“Ask him out, then, you berk,” Alice said. “And maybe let him into your head a bit, too, yeah? So you can call him if you’re ever having another rough night?”

Remus nudged the corner of the counter with his outstretched foot, blowing out a loud breath. “I know, I know I should.”

“Look, I’m not saying you have to tell him everything just because you’re friends, or because you fancy him,” Alice amended. “It’s your own personal shit to talk about when you want to, but...I think if you trust him with this stuff, it’ll help you decide if he’s someone you can rely on.”

“In other words, not Michael.”

“Exactly.” Alice stood up, offering a hand to Remus. He took it and got to his feet, and she smiled at him, tapping his chest. “You’ve got to see if he’s worthy of this heart!”

Remus hugged her briefly, mumbling, “Thanks, Alice,” into her hair. He looked around, blinking, and said, “God, what time is it? You may as well have your lunch, I’ll cover things up here.”

Remus passed by the windows of Black Dog Tattoos just after four o'clock as he walked over to the bike rack. He caught a glimpse of Sirius when he looked in; he was talking to Andromeda, his head thrown back in the loud, barking laughter Remus loved pulling out of him. He hesitated, fiddling with the lock on his bike for a moment as he watched them. He was tired, and he'd looked better, but...

Screw it, Remus thought as he snapped the lock shut. Alice would tell him to do what he wanted, and what he wanted was to laugh with Sirius for a bit before he went home. He walked over to the door, pushed it open, and stepped inside.

\newpage

%Chapter 8
\fancychapter{24-25 December}{Christmas brings feelings, revelations, and loads of toffee.}

IT WAS THE MORNING OF CHRISTMAS EVE, and London looked like a postcard. The city’s buses dotted the streets like red ornaments, cheery against a backdrop of gray sky and the white snow that blanketed the ground in a thin layer after falling overnight. Department stores were bustling with last-minute gift shoppers; pubs were warmed by university students and office workers who’d begun their holiday. The ice rinks in front of the Tower of London and Natural History Museum were alive with skaters young and old, gliding and stumbling along as they basked in the festive spirit that seemed to surround everything this time of year.

Many shops were closed for Christmas Eve, Christmas Day, and Boxing Day, including Fedelius Flowers and Black Dog Tattoos. Remus had enjoyed a breakfast of tea and toast in his favorite spot in his flat—the small reading nook that rested underneath a window in his lounge-slash-bedroom—before throwing a duffel bag on his narrow bed and starting to pack a few days’ worth of clothes. He planned to catch an afternoon train to Cardiff to spend the holidays with his father as per tradition. Christmas was a bittersweet time for Remus; he always missed his mother terribly when he and Lyall sat around the tree with their presents, sweets, and hot cider, but he still enjoyed a lot of things about the season.

He was stuffing a scarf into the side of his bag when his phone buzzed. He picked it up from where he’d dropped it beside the bed and couldn’t help the smile that stretched across his face as he read Sirius’s message.

You better not have skived off to Wales already, Lupin. I have something for you! Can I stop by yours?

He tapped out a quick reply—Still pretending to be English for another few hours. I’ll be in ‘til three—before turning his attention back to packing. And if he was still grinning like an idiot while he did it, well, no one could prove that, could they?

After much internal debate, he’d finally settled on a gift for Sirius last weekend. He didn’t want to get anything too big (potentially embarrassing), but he did want to get Sirius something. In the end, he’d stopped by the local record store and gone home with a copy of the Rocky Horror soundtrack on vinyl. It was now lying on his kitchen table, encased in red and gold wrapping paper and ready to be given to its new owner. Remus was happy with his decision; it was personal (a cheeky nod to their plant “children”) and nice without being flashy. His stomach flipped in not-entirely-unpleasant anticipation as he glanced across the room at it, knowing Sirius would turn up at his doorstep soon with a gift of his own.

Remus had finished packing and traded his pajamas for a black-and-white pair of Converse, jeans, and a sage green jumper by the time he heard the telltale roar of a motorbike engine below his flat. He met Sirius halfway, pulling open the main door of the building as Sirius reached the top step and stood poised with his fist in the air, ready to knock.

“Heya, Remus!” Sirius said cheerfully as they stood suddenly face-to-face.

He flashed a grin wide enough to show teeth, and Remus had to suck in a breath before he could force the “Hey, Sirius” out of his throat in what he could only hope passed for a casual tone. Sirius was wearing his prized leather jacket over a dark gray t-shirt (which had an almost absurdly low neckline, given the weather), faded jeans, and the familiar motorcycle boots. He’d thrown his hair up in a bun for the drive over, and a few loose pieces framed his handsome, smiling face. He carried a rucksack on his shoulders. Remus noticed a pair of black studs in his earlobes and chipped polish on his fingernails. Looking at him standing on his doorstep, Remus thought he’d never seen anyone so beautiful in his life.

“Come in, it’s bloody freezing,” Remus said, leading Sirius up three flights of stairs and down a narrow hallway until they reached his flat. It occurred to him as he opened his door and Sirius stepped inside that Sirius hadn’t been to his place before. He’d given Remus a ride home here and there, but Remus usually dropped by Sirius’s flat if they were going out together or he needed to drop off a borrowed book or record, conveniently located as it was.

Sirius seemed to realize the same thing as he strode into the lounge and looked around at the small sofa and cluttered coffee table, the art prints on the walls, the potted plants in the windowsill, and the bookshelves crammed with used paperbacks and knickknacks.

“Love the flat,” he said appreciatively, leaning forward by the windows to take in the view. He turned to look back over at Remus, smiling. “It’s very you.”

“What, barely contained chaos?” Remus said dryly, returning his smile.

“I was thinking more like—warm,” Sirius mused. “Y’know, like. All lovely and welcoming. Nice to look at. And nerdy—is that an entire shelf of fantasy novels I see?”

“Shove off,” Remus said without an ounce of malice, a small thrill rolling down his spine at Sirius calling his flat—and, indirectly, him—things like lovely and nice to look at. “Are you going up to Andromeda’s today?”

“Yep, for their Christmas Eve party, where I’ll drown my sorrows in eggnog after Ted refuses to snog me under the mistletoe for the tenth year running. Then I’m off to the Potters’ in the morning. James’s parents, I mean. They insist on me, James, Lily, and Harry staying over through Boxing Day every year.”

Remus smiled, imagining the loud, cheerful scene. “Sounds fun. And exhausting.”

Sirius hummed in agreement, fiddling with the turntable beside the bookshelves. He tended to do that, Remus noticed; run his fingers over objects as he looked at them. It made Remus feel like his flat was wholly more interesting than it was. He wasn’t sure what he would do if Sirius started caressing his bedsheets.

“It’s just you and your father, then?” Sirius asked, snapping Remus out of his thoughts. “For Christmas?”

“Me, my dad, the cats, and enough cider for a dozen people,” Remus replied. He scrunched his nose a bit as he thought about Lyall’s trio of beloved pets. “I’ve never liked cats. They know it, too. Pretty sure it’s mutual. But my dad’s become a full-fledged crazy cat parent, bless him. Half the gifts I’m bringing are really for them.”

“Dogs are just so much better,” Sirius agreed. He seemed to remember something suddenly, sliding the rucksack off his shoulders as he said, “Oh! Speaking of gifts.”

He pulled out a wrapped box so large that Remus didn’t know how he’d even fit it into the bag. “Oh god,” Remus said, eyes going wide. “What did you do?”

Sirius just laughed, crossing the lounge to stand in front of Remus. He held the box out between them. “Don’t worry, I got a great interest rate. I’ll have it paid off in no time.”

“Christ, you’re ridiculous,” Remus groaned, pulling another chuckle out of Sirius.

“It’s really nothing much, Remus, I promise,” he said reassuringly. He pressed the package into Remus’s hands. “Don’t open it yet. Wait ‘til tomorrow.”

Remus bit the inside of his cheek to keep his grin from going too wide, reading his own name written on the tag in Sirius’s oddly elegant script before looking back at the other man. “Alright,” he said softly. “Thank you, Sirius.”

Sirius’s gaze, which had fallen to Remus’s lips, traveled back up to make eye contact as Remus spoke. “You’re welcome,” he replied, his own voice going soft, too. “Happy Christmas, Remus.”

They stayed staring at each other for a long moment before Remus cleared his throat suddenly and turned around to carry the box into his kitchen. Sirius followed, and Remus handed him the wrapped record he’d bought. “Happy Christmas,” Remus said as Sirius’s eyes lit up, his fingers running over the wrapping as he turned the gift over in his hands. “It’s just a little thing, really, so—”

“No, it’s perfect. Thank you,” Sirius said emphatically, shaking his head. He looked as though Remus had just handed him the moon.

Remus’s chest was warm as he laughed. “You don’t even know what it is,” he pointed out. “Open it tomorrow? In the interest of fairness.”

“Yeah, yeah, fine,” Sirius agreed, trying to sound annoyed but completely unable to wipe the grin off his face.

There was another long pause as they smiled at each other. “I should, um. Let you get back to it.” Sirius murmured at last. He didn’t move away, though, and didn’t seem in any hurry to do so.

“Hm?” Remus said softly, eyes lowering to where Sirius’s teeth were pressed against his bottom lip. He felt a sudden urge to learn forward and pull that lip between his own teeth, nipping at it gently—and then less gently—before running his tongue across the length of it. He wanted to know what kinds of sounds Sirius might make if he did it slowly enough.

He was half-lost in this train of thought when Sirius said, “You have a train to catch, don’t you?”

Blinking, Remus looked back up at Sirius’s questioning eyes as reality flooded back in. “Oh. Yes. Sorry. Yes.”

He set the gift from Sirius down on the table as Sirius zipped Remus’s gift into his rucksack, and they made their way out of the building and over to where Sirius had parked his bike. Remus squinted as he glanced up; it had started gently snowing again while they’d been inside. Sirius slipped his bag over both shoulders and held his helmet in his hands, but didn’t put it on right away. He turned to Remus and opened his mouth as if to say something, but nothing came.

“What?” Remus finally said, the soft breathiness of his voice sounding strange to his own ears. He'd never seen Sirius hesitate to say anything before.

Sirius cocked his head, regarding him for a moment. There was something in his eyes as he smiled at Remus; something like sadness, but not quite. It was gone as quickly as it had appeared, and there was nothing but fondness on his face as he leaned in, tilted his face up, and pressed a kiss to Remus’s cheek.

Remus’s pulse raced; he held his breath, standing utterly still. Sirius rocked back on his heels and, still smiling, said, “See you later, Lupin.”

Remus found his voice again after Sirius had fitted his helmet over his head and got onto his bike, about to turn the key in the ignition. “See you. Happy Christmas!” He could have kicked himself for that; they’d already covered the holiday well-wishing, and anyway, what he really wanted to do was grab two fistfuls of that ridiculous leather jacket and—

With a nod and a salute, Sirius revved the engine, the sound drowning out anything Remus might’ve tried to say after. Snow gathered in his hair as he watched the bike speed away toward the main road. “Oh, well done, Remus, very well done,” he muttered with a groan, throwing his head back and closing his eyes until his face was cold and dripping from melting snowflakes. He shook out his hair and took one last, longing glance in the direction Sirius had gone before heading inside.

--

“Cyflaith\footnote{Welsh toffee, traditionally made on Christmas Eve.}?”

Lyall held out a square from his tin of toffee in offering. Sitting next to him on the sofa, Remus grinned and rolled his eyes, but accepted it.

“You say that like I haven’t been eating this all day,” Remus said, popping the piece into his mouth. The glossy, brown-sugar-and-butter treat melted as he chewed it, and he let out a small groan, savoring the bite. “Best part of Christmas,” he declared, making Lyall laugh.

Remus wasn’t entirely sure he’d be able to move from his father’s sofa ever again. The fire crackling in the ancient brick fireplace was keeping him warm, and an evening of indulging in lamb roast, gingerbread pudding, rum-spiked hot cider, and bits of toffee had left him happy, full, and sluggish. His eyelids were heavy; he could easily drift off right where he sat and not wake up until the next morning.

The Christmas tree stood in the corner of the room, its lights twinkling merrily. A large ginger cat lay underneath it amongst the handful of opened presents. It stretched luxuriously before curling up, purring, to go back to sleep. On the radio, Kirsty MacColl and Shane MacGowan were belting “Fairytale of New York.” The boys of the NYPD choir / Still singing Galway Bay / And the bells are ringing out / For Christmas day.

Lyall set the toffee tin aside and gazed at the fire. After so many years, Remus could tell just by the tightness around his father’s eyes what—or rather, who—his thoughts had drifted to. He nodded to himself, watching the flames dance up and around the wood in the fireplace as well for a moment. “She’d have eaten more toffee than both of us combined, and somehow not gotten sick.”

Lyall turned his head to look at Remus, startled by his son’s apparent mind-reading abilities, before grinning wryly and giving a one-shouldered shrug. “That obvious, am I?” he said. “Well. You’re absolutely right. Weighed no more than nine stone soaking wet, your mum, but she could eat a shop’s worth of sweets. Could drink me under the table, too.”

A flood of bittersweet memories washed over him, and he smiled a little sadly. “Anyone could drink you under the table,” he teased.

Feeling more awake, Remus got up to pour each of them a glass of cider. Lyall thanked him as he passed one over before reclaiming his seat. He took a slow sip, letting the familiar taste and smell comfort him.

Lyall patted Remus’s knee. “I just thank my lucky stars I’ve got you, fy machgen\footnote{My boy; used as a term of endearment.}, and that you’re happy and healthy and doing so well for yourself. That’s all she wanted.”

“Alright, I’m taking this back, you’re getting sentimental,” Remus said, pretending to reach for the glass in Lyall’s hand. Quiet settled between them after a moment of laughter, and Remus was contemplating whether he should say anything more about his mother before Lyall spoke first.

“I know I’m always on you about dating, and you’re well sick of me asking if you’re going to bring anyone round here one of these days—don’t look so panicked, I’m not asking now—it’s just that...well, I want you to have what I had, you understand?” One corner of his mouth turned up in a wistful smile. “I want you to find a girl who makes you as happy as Hope made me.”

Remus knew he didn’t like girls at age 13 after Emma Bower kissed him on the mouth in the middle of the school playground. He realized he liked boys a year later when Emma’s older brother, Matthew, had jogged past him wearing nothing but a pair of gym shorts and trainers while Remus waited for the bus home. He desperately wanted to talk to his mother about it, but she was already three years gone, and he didn’t want to put that on his father’s shoulders; he was grieving, and Remus was all he had left.

What if this is what breaks his heart for good? Remus would think, scolding himself whenever he struggled under the weight of his secret. He’d carried on like that for years, eventually coming out to his friends and starting to date but never bringing anyone home, always careful not to let the wrong pronouns slip when talking to his father.

Michael was the hardest. He’d been Remus’s longest and most serious relationship, and not being able to talk to his father about their painful ending while he was trying to recover from his accident made him question every choice he’d ever made up until that point. He’d managed to keep his secret anyway, afraid to add to Lyall’s anguish over seeing his son in a hospital bed.

He waited for the familiar clenching of his stomach at Lyall’s mention of him finding a girl, but it didn’t come. Alice’s voice rang out in the back of his mind. You bottle it all up until you’re drowning in it, Re. And maybe it was that—maybe it was the fourth glass of cider, or the comforting blanket of Christmas that had settled over him, or how tired he was of keeping a 16-year secret—maybe it was a combination of all those things, but Remus couldn’t find it in himself to hide it anymore.

“It...wouldn’t be a girl, Dad.” Remus paused, looking Lyall in the eyes. “If I fell in love with someone. It wouldn’t be a woman.”

“Oh.” Lyall said, so taken aback that he physically leaned backwards, blinking. “That’s—are you sure?”

Remus felt suddenly like laughing, but nodded instead. Whatever wild spark of bravery he’d had moments ago gave way to a nauseating roiling in his gut. He put his glass of cider down with a shaking hand and forced himself to meet his father’s gaze again.

“Well, I.” Lyall cleared his throat, still looking a bit gobsmacked. “So, you’re…” he made a vague gesture in the air between them with the hand not holding his drink. “Gay?”

Remus nodded again, not quite trusting his voice.

“Oh.” Lyall repeated. “Sorry, you’ve just, er, shocked me a bit.” He seemed to come back to himself then, and he set his drink down before leaning forward and putting both hands on Remus’s shoulders firmly. “That’s alright,” he said, gruff and affectionate. “That’s alright, Remus. Long as you’re happy. Hey now, no need for tears.”

“What? I’m not—” Remus blinked, touching his fingertips to the delicate skin under his eye. They came away damp. “Shit. Sorry, I’m—it’s just—I’m—” He laughed wetly, his arms and legs shaking as well as his hands, now.

Lyall pulled him into a hug, and Remus let a few more tears escape before taking a series of long, shuddering breaths. When they pulled apart, he was smiling. “I’m just...relieved. That you aren’t upset.”

A black-and-white cat mewled loudly from its perch on a shelf, breaking the tension and sending them both into fits of laughter. “I’m not upset with you.” Lyall said, catching his breath. “It’d take more than that for me to be. You know I love you?”

“I do. I love you, too, Dad.” Remus thought he’d never loved his father more than he did right at that moment.

“Right. That’s that sorted.” Lyall threw Remus a piece of toffee, which he just caught in time to stop it falling on the floor for a cat to devour. “Do you have a boyfriend, then?”

“No,” Remus said before swallowing his mouthful of candy. He thought of Sirius, wild and beautiful and kind. He thought of Sirius’s lips pressed against his cheek in the cold. “But if I meet someone, I’ll bring him round.”

“Good.” They slowly finished their drinks and listened to the radio before Lyall yawned hugely, scrubbing a hand down his face. “I’m shattered. Bedtime for the old man. You alright?”

If he’d been sleepy before his confession, he was exhausted now, drained from the onslaught of emotion. But he meant it when he smiled at his father and said, “Yeah. Yeah, I am.”

“Goodnight, then, lad.” Lyall stopped halfway to the hall and turned, looking back at Remus. “Oh, and it looks like you’ve still got a present over there. Best open it while it’s still Christmas.” He nodded toward the Christmas tree, where Sirius’s gift lay wrapped underneath it. With that and a parting nod, Lyall was off to his bedroom.

Remus knelt in front of the tree, pulling the box toward him. The ginger cat looked disdainfully at him. “By all means, your majesty, keep sleeping,” he muttered. “Don’t mind me.”

He hesitated after removing the wrapping paper, feeling intimidated by the size of the box again. What the hell could Sirius have gotten him? There was only one way to find out; he pried open the cardboard, looked down, and—laughed.

He was looking at a motorcycle helmet; Sirius’s spare one, the one he’d lent Remus for their spontaneous ride around town a few months ago. He pulled it out of the box, cradling it with one hand and pulling out the note inside it with the other. He recognized the graceful scrawl of Sirius’s penmanship.

{\it To the Esteemed Messr. R. J. Lupin—

Consider this an open invitation to take a spin on the bike with me whenever you want. You were a natural last time! I’ll try and turn up in a better mood next time, though.

Oh, and here’s something I thought you might enjoy today, knowing the depths of your sugar addiction as I do.

Happy Christmas, Remus. I’m so glad we met.

Sirius x}

The note was resting on a cellophane bag stuffed with an assortment of chocolates. Remus’s chest burned. He couldn’t stop smiling. He set the helmet and its contents on the sofa before fishing his phone out from between the cushions. He had a message from Sirius that’d been sent a few hours prior; a picture of the record, with the caption,

\textbf{REMUS, this is brilliant!!! I’ve been blasting it in the library since dinner ended, James is ready to kill me.}

He took his phone into his childhood bedroom, where he was spending the night, and lay down under the covers before tapping out a reply.

\textit{Glad you like it. Wasn’t sure if you already had it or not. // The Potters have a library?}

\textbf{I didn’t, but now I can sing the songs of our people to Riff and Mags! // Yeah, they do. Proper one. You’d love it.}

\textit{I should apologize to Andy now. // I think if I had a library, I’d never leave my house.}

\textbf{But then who would bring me tea when all I have is Andy’s shit coffee?}

\textit{Ah, of course. My purpose in life. // The chocolates are lovely, by the way, thank you.}

\textbf{And the rest of it?
}
\textit{Well. I suppose we’ll have to go for another ride sometime soon.}

\textit{YESSSS.}

\textit{I immediately regret this decision. // Tell everyone happy Christmas for me.}

\textbf{James and Lils say the same. Harry says “NO,” but I wouldn’t take it personally.}

\textit{He’s adorable. // Good day?
}

\textbf{Mhm. A great Christmas, all in all. Andy says hi, too.
}

\textit{Did you get your kiss?
}

\textbf{No! That Ted Tonks is such a tease. There’s always next year. // Actually, there was some drama to shake up the family festivities. Regulus came by.}

\textit{Really? How...was that?
}

\textbf{Fucking weird, to be honest. He turned up in the middle of things and it was like, crickets.
}

\textit{What did he do? What did you do?
}

\textbf{I was angry when I saw him walk in the door—I mean, what the fuck, you know? What does he want this time? But I remembered what you said a while back. That you didn’t think he wanted to piss me off last time. So I tried being civil.}

\textit{That’s good, Sirius. And was he?
}

\textbf{Yeah. Don’t get me wrong, the whole thing was bloody awkward, but he said he was passing by and wanted to wish us a happy Christmas. He even brought Andy a wreath for the door. He didn’t stay long, but nobody blew up, so.
}

\textit{Sounds like he wants to make amends. Or he’s at least trying to not be your enemy. That’s something, right?
}

\textbf{Yeah. It’s something. We were in the same room for over five minutes and didn’t kill each other! A true Christmas miracle.
}

\textit{Maybe next year it’ll be ten minutes.
}

\textbf{Since when are you brimming with sunny optimism?
}

\textit{Shut up, it’s Christmas. And I have a bag of chocolates.
}

The last thing Remus read before he gave in to the pull of sleep, his phone in his hand and a smile on his lips, was;

\textbf{Maybe next year it’ll be two bags of chocolates.
}
\newpage

%Chapter 9
\fancychapter{7 January}{An unexpected snowstorm leads to an unexpected sleepover.}

IT WAS A RARE DAY WHEN LONDON SAW A PROPER SNOW—the kind that accumulated more than a fraction of an inch and didn’t melt within minutes—but when it did, the entire city tended to descend into chaos. Remus took the bus into work one early January morning, having temporarily given up his cycling commute until the weather changed back from face-numbingly frigid to cold-but-reasonable. The sky was clear throughout the morning and the day carried on as usual until after lunch.

“Whoa, it’s really coming down!” Alice exclaimed from where she was peering out the shop’s front windows just after two o’clock. “Can’t remember the last time I saw the roads actually covered like this.”

When Frank pulled up in his van twenty minutes later, Remus ushered them both out the door. “Go pick up Neville and get home before the city-wide panic sets in and you’re stuck in traffic,” he insisted over their protests. “Nobody will be coming in here in this.”

“Can we drop you at yours on the way, mate?” Frank offered, but Remus politely declined. The streets would be clear by four, he reasoned, and this was his chance to cross off a few items on his to-do list without being bothered by walk-in customers.

Four o’clock came and went, but the fallen snow hadn’t melted — and still more was coming down. Remus swore under his breath, teeth chattering as he waited at the bus stop in vain. “Come on, where are you,” he muttered. After a few more minutes he dug his phone out of his coat pocket, pulling off one of his gloves and holding it between his teeth as he quickly tapped on the screen. A search of London bus confirmed his fear: the city’s buses hadn’t been running for the past half hour due to the inclement weather.

He trudged back into his shop, standing on the welcome mat as slush dripped from his shoes. “Shit,” he said to the empty room, feeling profoundly stupid for turning down Frank’s offer of a ride home.

He was weighing his options when it suddenly occurred to him: Sirius. He shoved both his gloves in his pocket and got out his phone again, this time to send a text.

\textit{Are you home?}

\textbf{Yeah. Closed up early. No one’s coming in for a tattoo in this shit. You?}

\textit{I’ve been stood up by a bus. Still in the shop.}

\textbf{You’re a madman, Lupin. Come over. Heat’s on, and I’m making a curry.}

Remus almost groaned aloud at how good that sounded. He could think of far worse ways to wait out a storm than having dinner with Sirius in his flat. And if Remus was being honest with himself, he missed spending time with Sirius. They hadn’t seen each other since Christmas Eve, only keeping up through text during the holiday chaos. The banter was nice, but he missed seeing Sirius’s eyes go wide and bright as he was in the midst of telling a story; he missed the wide, toothy grin he flashed when Remus walked into the tattoo shop; he missed Sirius’s loud, barking laugh and his sly smirk and the way he’d lay a hand on Remus’s shoulder as he pointed out a photo of a new piece he’d hung on the wall.

Remus pocketed his phone, not bothering with the gloves as he headed outside and made his way around the back of Black Dog Tattoos. He climbed the slippery stairs up to Sirius’s flat and knocked, heart already beating faster in anticipation. He glanced down at himself as he waited; thankfully, he was wearing a decent coat, with a soft green-and-blue Scotch plaid flannel and a white t-shirt underneath. He could wear this outfit on a date and not look sloppy. Not that this was a date, he thought as he heard approaching footsteps inside.

Remus’s first thought as Sirius opened the door was he looks beautiful. His second was is that a crop top? Sirius looked warm, flushed from cooking, and very much at home. His hair was up and Remus could see those maddeningly hot black stud earrings, and his Ziggy Stardust-era Bowie shirt was cropped to show a couple inches of skin from his navel to the sharp cut of his hips where his jeans began.

“Hey, you,” Sirius greeted, seemingly unaware of the minor heart attack Remus was suffering. “Come inside. Food’s nearly ready.”

Remus loved Sirius’s flat. The rooms were all painted in rich colors—deep reds, purples, greens—album prints and artwork were scattered on the walls, and the furniture was plush and inviting. The house I grew up in was so depressing, Sirius had told him when he’d complimented the flat during his first visit. All gray and severe. Cold. I like warm colors, now.

The place was also heated through as Sirius had promised, and Remus sighed in relief as he took off his shoes and hung his coat on a hook by the door.

“So you took the bus?” Sirius said with a grin. “Half expected you to try and bike in.”

“Oi, I can hear the shade in that question,” Remus said as he followed Sirius into the kitchen. He tried to look stern as Sirius pulled two beer bottles out of his fridge and set them down on the counter before tending to the curry on the stove. “She’s a reliable bike, and I won’t have you slandering her because of her age.”

Sirius snorted, glancing up at Remus and raising an eyebrow. “Remus, you’re fucking repairing her every ten minutes.” His grin widened as he said it, crinkling the corners of his eyes.

Remus pulled a face as he maneuvered around Sirius to fish a bottle opener out from the drawer where he knew it was kept, cracking the first one and passing it to Sirius before opening his own. “Cheers,” Sirius said, raising his bottle and clinking it against Remus’s.

Remus stopped fighting a smile as they each took a swig of their drinks. He leaned against the counter, watching Sirius stir the vegetables and marveling at how easy this felt—like they’d been doing this for ages and would do this again tomorrow, and tomorrow.

After another quick stir and a taste-test, Sirius turned down the heat and pulled out a pair of dinner plates from the counter above his head. “Ready to eat?” he asked.

“God yeah,” Remus said. “It smells amazing.”

He brought their drinks over to the table as Sirius handled the food, and soon they were sat for dinner, cheering with their bottles once more before digging in. The curry tasted heavenly, and Remus was enthusiastic in his praise, thanking Sirius for cooking and declaring how delicious it was.

“If people ever stop needing tattoos, you could open up a restaurant,” he suggested before eating a large spoonful off his plate.

“Oh yeah?” Sirius grinned, swallowing his mouthful and reaching for his beer. “I’ll cook if you bake.”

“Deal,” Remus said, stomach flipping at the implications of that. He hadn’t really recovered before Sirius was adding, “We could have it in some really hidden away corner of London. Fill it with plants and flowers. What would we call it?”

Remus hummed, taking a slow sip of his beer as he tried to brainstorm ideas. It was hard to focus on much more than how good Sirius looked. Every time Remus visited the tattoo shop, he noticed how many heads turned when Sirius swaggered out of a back room. Old and young, men and women—it seemed that Sirius Black was everybody’s type. Not that Remus could blame them, of course. He was looking, too. How could he not?

“I don’t much care what we call it, so long as you make—” Remus stole a cube of aubergine off Sirius’s plate, popped it in his mouth, and sat back in his chair with a cheeky grin. “—this curry!”

“Oi!” Sirius protested. “The aubergine,” he went on petulantly, leaning over to pinch some from Remus’s plate, “is the best bit, you bastard!”

Remus was laughing now, and Sirius broke into a grin like he couldn’t help it. “You’ve got Mama Potter to thank for teaching me how to make this,” he said. “She learned it from her mum, Nani Prisha. Only met her once but whoo, what a woman. Tiny but formidable.”

“Sounds like Alice,” Remus joked, taking another bite. They ate in comfortable silence until their plates were empty, throwing everything in the sink to soak before going to sit in the lounge to finish their drinks.

Sirius was rifling through a stack of records when Remus said softly, “I’m glad you had James’s mum. You know, when you were younger. Now, too, obviously, but. Especially then.”

Sirius set the needle down and the room filled with music. “Me, too,” he said with a smile, joining Remus on the sofa. “She’s the best. So’s his dad. Big fan of the Potter brood in general.”

Remus’s first instinct was to shift the topic of conversation to avoid any personal questions, but he ignored it, looking at Sirius instead and saying, “My mum...I wish you could meet her. She was so much fun, always dancing. And so kind. She jumped out in traffic to herd a turtle off the road, once. She was that sort of person.”

Sirius sat up straighter, blinking in surprise. “She sounds great,” he said. He kept opening his mouth on an inhale and stopping, as though he were trying to speak carefully but wasn’t used to having to do it. Finally, he settled on, “Were you a kid when she…?”

“Just after I turned eleven,” Remus said, nodding as he felt the old, familiar pang in his chest. “Cancer. It’s just been me and my dad since then.”

He turned his gaze up to Sirius’s face slowly, reluctant to see what was written there. Sirius was frowning, eyes grim, but he didn’t have that pitying look Remus hated. “That fucking sucks, Remus,” he said earnestly, and Remus could have kissed him for it.

“It does,” he agreed with a sad half-smile. “I got really close with my dad after that, which was nice, but it also…” he sighed, shrugging. “It made me keep to myself a lot more. Like, I got used to...not really telling people how I feel, because my dad was so torn up, you know? I didn’t want him to worry about me.”

Sirius was quiet for a long moment, gray eyes searching the brown of Remus’s. Finally, he said, “I get it, Remus. I mean, I know I’m like, loud and brash and whatever, but. I get not wanting to bother people with your shit. The real shit, the dark shit.” His voice was softer than Remus had ever heard it, and his chest tightened as he heard it. “I’m glad you told me.”

“Me too,” Remus said, and meant it.

A car horn blaring loudly outside roused them out of the quiet spell they’d fallen under together. Remus realized he hadn’t once checked if the buses were running again. Sirius went over to the window, peering out at the blurry night sky. “Still snowing,” he said. He spun around, grinning. “Looks like you’re stuck here, mate. What better night to finally watch Rocky Horror together?”

“Oh my god,” Remus said, shaking his head and laughing. “I haven’t seen it in ages. Right, okay, stop your excited wiggling and put it on.”

Sirius insisted on watching the movie in total darkness for the “full experience,” but he left the bathroom light on so Remus could find it. They had a second drink. They reheated some curry and popped popcorn Sirius scrounged from the back of his pantry. They talked about the movie and other musicals they loved, and Remus laughed so hard he nearly knocked the popcorn bowl off the sofa as Sirius stood on his coffee table to sing along to “Sweet Transvestite,” his dance moves becoming increasingly ridiculous as the song went on.

As the credits rolled at half past nine, they had a joking argument over what to watch next. Remus wandered from Sirius’s movie collection to his record collection, and they ended up listening to music, each of them swapping out albums and talking about the songs they loved best.

There was a moment when Remus grinned wryly at Sirius and said, “I can’t believe my dad didn’t know I was gay when I was in school. I listened to this album in my room all the time.” He gestured to the record player, where Robyn was singing “With Every Heartbeat.” Sirius laughed, but an odd expression crossed his face as their gazes met. Remus flushed; he distantly realized it was the first time he’d actually confirmed it to Sirius. Sirius didn’t look surprised exactly, but—there was something there in his expression, something Remus couldn’t quite place but sent a thrill through him from scalp to toes.

“I think I got the message across to my dear old mother when she walked in on me with my tongue down Jack Cromwell’s throat in year nine,” Sirius joked, but his grin was softer than Remus expected. Something had shifted between them, and they’d both felt it. Remus’s heart pounded with the possibilities.

Sirius brought a blanket for the sofa and a pair of sweatpants for Remus around midnight. He was met with no protest; there was no reason for Remus to try and go home, and he didn’t want to, anyway.

“Sure you don’t want the bed?” Sirius asked as they stood in the middle of the lounge, halfway between the sofa and Sirius’s bedroom. He’d said it innocently enough, but Remus prayed to all things holy to keep the resulting heat he felt from creeping up his face.

“Uh, no,” he stammered. “No, that’s fine. I’m good here.”

Sirius cocked his head to the side, regarding Remus for a moment. He nodded just as Remus started to worry his hammering heart was visible through his chest. “Okay.”

He was grinning, but Remus thought it looked a little deflated around the edges. Remus had meant it as a polite refusal—as an, It’s fine, I’m not making you sleep on the sofa in your own flat. But as he watched Sirius’s face, he suddenly wondered if he’d got it wrong.

“‘Night, Remus,” Sirius said after a pause. His voice was low and his eyes were warm, and he lingered for just a second longer than necessary after Remus gave him an answering “Goodnight.” Remus stood still and watched his retreating back until Sirius disappeared into his room with a soft click.


\newpage

%Chapter 10
\fancychapter{15 February}{A tattoo and a beginning.}

REMUS LUPIN, SWORN ENEMY OF ST. VALENTINE.

Every year as January gave way to February, Valentine’s Day orders would come piling in. Which wouldn’t be so bad for Remus, if not for the veritable stampede of boyfriends and husbands rushing into his shop the week of, frantically buying what was left of his stock. The 13th and 14th were especially, unsurprisingly mad, and Remus always emerged a little battle-worn on the other side of it.

“Valentine’s Day, Mother’s Day, weddings, and funerals,” Alice said as she did every year, pressing a hot coffee into Remus’s hands the morning of the 15th. Remus groaned, hoping she’d take that as agreement enough as he took a long sip. Those events were undeniably the lifeblood of the business, as they were for most florists. He was grateful for it, of course, but—yeah, Valentine’s Day was a chore.

“If I never see another red rose again, it’ll be too soon,” Remus sighed out after another sip of coffee, finishing the second half of his and Alice’s annual refrain.

If Remus was being honest with himself, there was another reason this year why Valentine’s Day annoyed him: caught up with work as he was, he hadn’t seen Sirius at all that week. The shift he’d felt between them when he slept at Sirius’s flat the month before had firmly stuck around. There was something simmering under the surface of their friendship, and Remus suspected Sirius might feel it, too, no matter how many times his insecure brain tried to talk him down, telling him that Sirius flirted with everyone, that didn’t mean he wanted Remus the way Remus wanted him.

“Should be a chill day today, though, yeah?” Alice said, tired but cheerful, as she sipped her own drink. Her grin turned sly as she added pointedly, “Good day to visit the neighbors.”

Remus knew he didn’t wipe the stupid resulting grin off his face fast enough for Alice not to catch it. He shook his head and rolled his eyes up at the ceiling like he was giving up the game. “Yes, I’ve been thinking about him, shut up.”

“Atta boy,” Alice teased as he set her cup down on the counter to start sorting the register. Her voice roused him from checking their emails on his phone a few minutes later. “Have you told him your idea yet?”

Ah. His idea. That was something else the extra holiday work had forced Remus to put on the backburner. “Not yet,” he said evasively, chewing his bottom lip as he thought it over again. He glanced at the phone in his hand. Now was as good a time as any. He texted Sirius as he worked, the light foot traffic into the shop finally giving him time to have a proper conversation with the other man.

\textit{Sorry I haven’t been around this week, it’s been mad here with St. Valentine’s orders.
}

\textbf{It’s a wonder that guy has enough money to spend on all these flowers.
}

\textit{Ha. I’m happy for the business, obviously, but I am getting sick of red roses.
}

\textbf{I mean, red roses are kinda romantic. No?
}

\textit{I’ve nothing against roses, it’s just—all the blokes coming in here asking for them at the last minute, you know? // Which reminds me, James called. Wants to put something together for Lily.
}

\textbf{Oooh. Yeah, I’ve got Harry on Saturday while they have their big date. What are you going to do for her?
}

\textit{Not exactly sure yet, but I’ll arm him with something nice. No roses, no lilies.
}

\textbf{No petunias.
}

\textit{No petunias?
}

\textbf{Her sister’s name is Petunia. They don’t exactly see eye to eye.
}

\textit{Ah, got it. I think I’ll use some sweet peas, some verbena. Cornflower, maybe.
}

\textbf{Sweet. Yeah. // What’s your favorite flower? Don’t think I’ve ever asked.
}

\textit{Hmm. It’s hard to choose a favorite. I actually do like lupines, ironically.
}

\textbf{Did you know there’s a kind of cactus called Sirius that only blooms at night?
}

\textit{Really?
}

\textbf{Mhm. Pretty badass.
}

\textit{Sounds fitting. I’ll look them up. // What about you, then? Got a lot of couples asking for tattoos of each other’s faces?
}

\textbf{No, thank god. Just a lot of hearts and eternity symbols, like it’s still 2001. Boring as hell, seriously. I don’t think people even look at my work before they choose to come here this time of year, they just turn up because they know I’m ready and willing to mark them for life.
}

\textit{Maybe some people, but most know exactly who you are and happily join your waitlist. Are you up to 3 million Instagram followers, or 4?
}

\textbf{Hmm...3 and a half?
}

\textit{Sometimes I forget I have a genuine celebrity next door.
}

\textbf{You’re making your mark. I keep doodling flowers lately. I don’t know what’s wrong with me. Maybe it’s that I can smell roses CONSTANTLY.
}

\textit{Flowers make for nice tattoos. Especially when the color work is as nice as yours.
}

\textbf{I’ll put some on my social, I think. See if there’s any interest. // Hey, maybe we could get some kind of collaborative project going. They buy flowers from you, and I’ll discount a tattoo of them. Partners in crime!
}

\textit{Mm, I’m sure all my church ladies would be into that.
}

\textbf{Okay, you’re right. We have totally different clientele.
}

\textit{Alice has been dying to go to you, at any rate.
}

\textbf{Oh, she has?
}

\textit{Yep. You’ve charmed everyone, apparently. Even the church ladies.
}

\textbf{Nah. You’ve probably just been bragging about me :)
}

\textit{I don’t need to say a word when you saunter in here with that smirk. Mrs. Gadsby from the historical society is ready to leave her husband for you, I think.
}

\textbf{I think Mr. Gadsby is probably more my type, though I’d make a great trophy husband.
}

\textit{Into 70-year-old pensioners, are you?
}

\textbf{Why do you think I’m over so often? Just can’t stay away.
}

\textit{And here I thought you came for the tea.
}

\textbf{You do make a mean cuppa. // Send Alice my way if she decides she wants to chat about ideas. I could bump a few people down the list.
}

\textit{You don’t have to do that.
}

\textbf{I know.
}

\textit{I’ll let her know. Thank you. // I do have one more referral for you, actually.
}

\textbf{Did Mrs. Lawrence finally change her mind about letting me do her ankle?
}

\textit{You’ll have to put in a bit more work with her before that happens, I think. Sorry.
}

\textbf{Damn}.

\textit{I was wondering if you had some time for me to come in? When you have a mo’.
}

\textbf{You want a tattoo?
}

\textit{Well, I don’t want that foreign substance Andy brews in the back that she calls “coffee.” // Anyway, I know you’re busy, I’ve seen the waiting list, so no rush. Really.
}

\textbf{You can have a consultation whenever you want if you provide the hot drinks.
}

\textit{I’ll ask Andy when you have free time, she’ll be honest.
}

\textbf{Oh please, Remus, I would have done this from day one when you brought me those “welcome to the street” brownies. I’ll find time.
}

\textit{Do you do a lot of scar coverups?
}

\textbf{Yeah. A few. Is that what you’re interested in?
}

\textit{I was hoping you could do something with one of the nastier ones. Starts at the top of my shoulder and hooks down my back below the shoulder blade.
}

\textbf{Sounds like a big project.
}

\textit{Like I said, it can wait. I don’t want to monopolize you.
}

\textbf{No. If it’s what you want, I’ll do it for you. I’ll fit you in, easy.
}

\textit{Thanks, Sirius.
}

\textbf{Sure. What else are friends for? // Can’t believe you’re going to let me ink you up.
}

\textit{I trust you.
}

\textbf{Thank you. // Come by with a mug of tea this afternoon and we can look at designs.
}

\textit{Alright. After I close at 4, yeah?
}

\textbf{Four’s great.
}

And just like that, Remus had plans to visit Black Dog Tattoos not to hang out, but to have a consultation—one that would involve being shirtless on his part and more than likely a few pointed questions about his scarring from Sirius. God, Sirius would be touching him, for ages, as he inked Remus’s skin with whatever intricate and beautiful design he came up with. Fucking hell, Remus thought. Why did he ever think this was a good idea?

The workday stayed just busy enough to keep Remus from obsessing too much about his upcoming appointment next door, and for that he was grateful. At five minutes past four he made two cups of tea and poured them in to-go mugs, carrying them out the door with him as he said goodnight to a smirking, knowing Alice.

He walked into the tattoo parlor and found Andromeda up front, greeting her warmly. He looked around and took a deep breath, trying to steady himself against the not-entirely unpleasant fluttering in his stomach. Alerted by the noise of the bell above the door, Sirius poked his head out from one of the private rooms.

“Be with you in ten, Remus!” he called, flashing a smile before turning his attention back to his client.

Remus chatted with Andromeda as he waited, setting the tea down on the long coffee table. Andromeda answered the phone after a few minutes and Remus thumbed idly through the portfolio binders on the table, recognizing some of the pieces that Andromeda had posted on the shop's Instagram.

Sirius knew his craft: twelve minutes after he’d said hello to Remus, he emerged from the side room with his client. The young woman was smiling, and Remus spotted fresh ink on her ankle as she paid her bill and thanked Sirius profusely. Sirius saw her to the door and, once it was closed, turned to look at Remus from his spot on the sofa.

“Hey there,” Sirius said as he sidled over and plucked one of the cups up from the table. Remus’s heart sped up as Sirius chose the mug Remus always brought over for him (the old one, pale green and slightly chipped, that Sirius had picked up himself all those months ago in Remus’s shop). Sirius sat down on the coffee table in front of him, frowned as Andromeda shouted “Sit on a chair, Sirius!”, and moved to sit next to Remus on the sofa instead.

“Can’t believe this isn’t a social call,” he said, nudging Remus’s shoulder playfully. “Finally letting me get my hands on you.”

Whatever witty retort Remus had been opening his mouth to say died on his lips at Sirius’s last remark. Get my hands on you. He was in trouble. He could feel heat prickling at the tips of his ears as a series of entirely unwelcome, entirely inappropriate images flashed through his mind. Remus took a long sip from his own cup to bide himself time to come up with a suitable reply. “Only if you can sell me on a design,” he said once he was confident his voice wouldn’t waver.

Sirius waggled his eyebrows in reply, taking a long sip of tea. “Shall we go somewhere where I’m actually allowed to sit where I want to in my own shop?” He threw Andromeda a pointed, dramatic look. She didn’t even glance up—simply raised a middle finger with the hand not filling out paperwork and threw out a casual “Fuck off.”

Sirius seemed happy to oblige her. He stood and nodded in the direction of one of the side rooms to Remus before leading the way toward it. He’d once told Remus that was one of his favorite things about the premises—the privacy it afforded—and Remus understood why as he stepped into the room and Sirius closed the door between them and the reception. Thanks to the abundance of side rooms, even consultations could be very personal. The room they were in was small but light, airy. Comforting. Remus felt his nerves soothed just a bit by the space.

Sirius pulled out a chair for Remus before perching on the edge of another stool, crossing his legs underneath himself and settling into the seat. “How was business today?” he asked, pulling his long, dark hair down out of its tie. “Got any ideas for Lily’s flowers yet?”

Remus sat in the chair offered to him, watching Sirius shake out his newly freed hair and resisting the urge to run a hand through his own curls. “Steady, but less of a rush,” he replied, crossing his ankles. “Finally seeing the dropoff after the holiday orders.”

He pulled out his phone, swiping through his camera roll for a photo of the bouquet he’d started working on that afternoon for James to give to Lily. “I’ve nearly got it how I want it,” he said, turning the phone to Sirius to show him. The picture showed a loosely constructed wildflower bouquet with blue cornflower, purple delphinium, white and yellow chamomile, white daisies, blue hydrangea, queen anne's lace, and several varieties of greenery and foliage. “Might need a touch more yellow,” Remus mused as he eyed it critically. He was a notorious perfectionist with his arrangements; that, combined with his extensive knowledge and knack for reading people, had earned him many a loyal patron.

Sirius leaned forward to peer at the screen and gave a soft, pleased sound. “God, that’s gorgeous,” he said, shaking his head and looking up at Remus with a smile. “Yeah. You’ve aced it. She’ll love that.” He looked back down at the photo and smiled even more. It always made Remus's heart seize up when Sirius directed that smile toward him. It was a soft, warm, slightly goofy thing that turned his mouth a bit crooked and reached his eyes, crinkling them a little. It was different from the polite grins he gave to customers or the flirtatious smirks he used on just about everyone; it meant Remus had surprised him, pleasantly so, and Remus always felt like preening under the glow of it.

“So, you wanna talk tattoos?” Sirius said, straightening his back. “It's my second favorite subject, after how much I appreciate your tea-making skills.”

Remus glanced over at the table where clients sat when they were being worked on by Sirius, feeling that prickle of nerves again. “I reckon we should,” he agreed. “Did you have any design ideas, or...did you want to have a look at the location first?”

“Depends what kind of tattoo you want,” Sirius replied, sitting back with his hands on his knees. “Do you want me to ink around the scar, or do you want me to fill it in?” He slid an art pad toward himself across the table and shot Remus a kind smile. “Either way, I’ll want to see it at some point. Know what we’re working with, here.”

Shaking his head at the question, Remus replied, “I...don't know, really. To be honest, I’m not exactly sure I even know the difference in what those would look like.” His fingers toyed with the hem of his jumper for a moment before he let out a breath, straightened his posture, and looked Sirius in the eye. He’d have to get it over with eventually, and delaying would only make him more nervous. “Why don’t I show you, and you can tell me what you think, alright?” He said.

He tugged the jumper over his head, then the gray cotton t-shirt underneath, leaving both in a semi-folded stack on the table. He was left in a pair of well-fitted but slightly faded tan trousers and his old, reliable white Converse which he often wore to the shop. Despite his self-consciousness, Remus resisted the urge to curl in on himself and kept his back straight, meeting Sirius’s gaze once again. The scars were indeed everywhere; in addition to the long, diagonal slash across his nose and cheek, there were similar white lines that criss-crossed over his chest, arms, and back. Some of them looked more purposeful, surgical, like the one at his breastbone and another above his kidneys. The one he’d described to Sirius—the one that started at the top of his right shoulder and curved down his back over his wing bone—was thicker and more mottled than the rest.

Sirius looked at Remus’s bare upper half for a long time, leaning in carefully to get a closer look at the scar in question. Remus was silent and still as Sirius examined the shapes and colors that littered his skin, only letting himself close his eyes when Sirius had gotten up to circle behind him, examining his back. He was tense, but not because he didn’t trust Sirius. In fact, he trusted Sirius enormously; he doubted he’d let any other person permanently ink his skin, no matter how frustrated with his scars he became.

When Sirius sat back down, he raised his eyes to Remus again and nodded slowly. “Okay,” he said, then brought his foot up onto his chair.

Before Remus could do more than raise an eyebrow in question, Sirius removed his boot, then his sock. On his ankle there was a long, narrow scar that curved underneath his foot. “Stepped on some broken glass as a kid,” he explained as he tilted his foot to show Remus a tattoo of a tiny black safety pin, positioned as if it were keeping the two sides of the scar knitted together. He glanced up and grinned. “See? I’m a pro. We’ll find something that fits you.”

Remus blew out a breath that turned into a laugh, mouth tilting up in a crooked grin. “You’d need quite a few of those safety pins for me,” he joked, but his eyes showed sincere appreciation as they held Sirius’s own.

Sirius's answering smile was warm and fond. “You wanna talk through some ideas?” Sirius asked as he tugged his sock back on and started lacing up his boot.

Remus felt significantly more at ease now that the most vulnerable part was over. His shoulders slowly relaxed as they talked and he stopped focusing on his own body. “I was thinking about some flowers, at first—unsurprising, I know. Wildflowers have always been my favorites; a lot of the varieties I used in that bouquet for Lily, for example. And...maybe an iris in there somewhere for my mum? Irises are supposed to represent hope, and that was her name. Hope.” He paused, thinking about different images that came to mind. It was a novel thing for Remus to think of his scar not as a scar, but as a canvas, a combination of shapes and textures to embellish with ink.

“I thought you’d say something like that,” Sirius nodded, turning on his stool to pull out a folder with NATURE scrawled on the front in block lettering. He placed the folder on the table between them but kept it to the side for the time being, picking up his sketchbook instead and flipping to a page near the back. Remus’s pulse doubled in time as Sirius slid the book toward him and his eyes fell on the paper. Sirius had doodled dozens of floral designs—designs for Remus.

“I think wildflowers are a good idea,” Sirius continued as Remus tried in vain to get his heart rate under control. “It would be flexible, you know? They grow where the wind takes them. We could have climbers, or bunches.” He glanced up to watch Remus’s face as he continued. “It’s a big area to cover, on your back. We’ll have to be careful not to overcrowd it. I think decoration, rather than total coverage, is really where we want to go. What do you think?”

Remus’s eyes lit up as he thumbed through the pages of Sirius’s sketchbook, taking in the beautiful designs that had been drawn there. “These are gorgeous, Sirius,” he murmured, fingertips dancing lightly over the graphite lines, tracing patterns. He felt like he was getting a peek inside Sirius’s head. He could picture the designs on his skin, and he gave Sirius a warm, excited smile. “And that makes sense, yeah—decoration.”

They spent the next twenty minutes hashing out ideas, Sirius sketching as they talked. Sirius pointed out that Remus’s scar was the shape of a crescent moon after he’d drawn the outline of it on a fresh page, and they’d built the design from there, giving the moon lavender stems, blue cosmos and cornflower, and purple-and-green irises growing over and around it. Sirius jotted down each flower name in the margins as he worked.

Remus couldn’t help but get excited as the nebulous ideas being thrown out between them began to take shape on paper. Sirius was a keen listener, able to really hear what Remus was trying to get at and use his talent to turn it into art. He found himself, not for the first time, impressed by how well Sirius knew his craft. His experience was obvious in how he was handling the consultation, guiding Remus along without taking the wheel out of his hands.

“Some chamomile could do the trick,” Remus suggested as they considered ways to break up the largely purple and blue color scheme. “They’re small, white petals, big yellow center. Maybe…” without thinking about it, he covered Sirius’s hand with his own, guiding him to an empty spot in the drawing. “Just there?”

Sirius’s eyes followed Remus’s hand as it guided him across the paper and when their hands stilled, he looked up. “Yeah,” he said, grinning and slightly breathless, his eyes darting between Remus’s. “Just there.”

Remus knew he should probably move his hand away, give Sirius some measure of his personal space back, but when those gray eyes held his own for a long, tender moment, it was as if a spell had fallen over the room. After an indiscriminate amount of time—seconds, maybe, or hours, Remus couldn’t rightly answer which—Sirius moved his hand first, but not enough to break contact, just enough to draw in some chamomile stems. It was shockingly intimate, holding Sirius’s hand while he drew; Remus could feel each shift of muscle and bone beneath his skin as he glided the pencil across the paper.

“So—um—” Sirius said as he finished, but kept his hand resting underneath Remus’s. “Like that, you think? Climbing it?”

Sirius’s voice came out hushed, and Remus’s was equally so as he replied, “That’s lovely, yes.” His honey-brown eyes flickered from the paper to Sirius’s own. Remus was suddenly, acutely aware of every millimeter of space between their bodies.

His breath hitched as Sirius shifted his hand, knotting their fingers together. “Thank you for trusting me with this,” Sirius said quietly. “Really. It’s such a huge compliment.”

Remus felt the familiar fluttering he’d come to associate with being this close to Sirius. Being this close and holding hands— and while he was half-naked, no less—was definitely the most intimate scenario they’d been in thus far, and Remus felt a bit dizzy with it. He hadn’t let himself hope that Sirius could be interested in more than friendship with him up until this point, but now...Sirius was leaning in close, not only keeping Remus’s hand on his but entwining them even more so.

“It’ll be a long job,” Sirius continued. “Lots of one-on-one time where you’ll have to put up with me.” He cracked a small grin. “Think you can manage it?”

Remus breathed into the electric space between them, mustering courage enough to bring his free hand up against Sirius’s cheek.

“I think I could manage quite a lot of things with you, Sirius,” Remus admitted. He couldn’t help himself now that they were finally this close; he brushed his thumb across a sharp cheekbone, heat pooling in his gut as he felt the smoothness of Sirius’s skin.

And then they were both tipping forward in their chairs, the distance between them closing and closing and closing until—

“Sirius!” Andromeda called as she knocked on the door. Both men froze, faces inches apart. “Sorry love, but your next client is here and you’ve run way over your appointment time.”

Remus reluctantly pulled both his hands away, rolling his eyes up at the ceiling and huffing out a laugh, face burning. Sirius sat back in his chair, grumbling under his breath before he called out, “Two minutes, Andy!”

His eyes fell back on Remus’s. “Well,” he said slowly, getting to his feet and running a hand through his hair. “I hope you found that consultation...useful.”

“Um—yeah. Yes,” Remus stammered, standing up and pulling his t-shirt and jumper back on. There were so many other things he wanted to say, but they were out of time. After glancing down at himself and giving a cursory tug at his jumper, Remus looked at Sirius with a regretful half-grin and walked over to the door, opening it.

Andromeda was back at the front desk, sketching in a notepad; she glanced up at the pair of men as they joined her, an oddly knowing smile on her face. “Sorry to interrupt, Remus,” she said, not unkindly. “I’m sure Sirius would be happy to continue your discussion another time. Isn’t that right, cuz?”

Sirius shot Andromeda a glare as Remus cleared his throat, ducking his beet-red face to stare hard at his shoes for a moment. When he looked back up, Sirius’s eyes were on him. “I’ll, um. I’ll see you later, Sirius.”

Sirius opened his mouth to say something, but glanced at Andromeda and his client who was waiting off to the side of the front desk. “Yeah. Later, Remus,” he said at last, looking very much like he wanted to add something more.

Remus didn’t give him a chance to. He turned away, hearing Sirius greet his customer as the door swung shut behind him.

~

Sirius finished his last session at half past six, coming out of the back room in just a t-shirt and his jeans, his hair tied up in a messy bun at the back of his head. He said goodbye to his client and wandered over to where Andromeda was packing up her things.

“That was a late one,” she commented, then looked up and smirked at him. “Something tells me that client wasn’t the only thing on your mind.”

“When did you know?” Sirius asked Andromeda with playfully narrowed eyes.

“About six months ago,” she replied dryly. Sirius swatted her arm and went to pick up his own bag.

“Really, come on. Come on. Be fair to me.”

“That’s just so not in my job description,” Andromeda laughed. “So? Was I right?”

“About what?” Sirius asked evasively.

“About the two of you nearly fucking over all our sanitary equipment back there!”

“Whoa,” Sirius choked out. “Nothing happened,” he explained quickly.

Andromeda threw her bag over her shoulder and walked out from behind the counter. “Shame. Anyway, I’m off. Have a good evening.” She pressed a kiss to his cheek. “Do everything I would do. He’s a dish."

“Fuck off,” Sirius laughed and watched her go. He locked the door after her and let out a soft sigh, eyes unfocused as he touched his fingers to the high of his cheek. He laughed again, this time to himself, before heading up the back stairs to his flat.

~

Remus had spent the past hour stewing in his own flat. Every time he’d talked himself into believing he and Sirius hadn’t almost kissed, he’d remember the flash of heat in Sirius’s eyes, or the way their fingers held tightly to the other’s, and he was back to square one. He felt like a live wire. He kept pacing around his bed. He’d tugged at his hair so many times that it was sticking out wildly; he caught his reflection in a mirror and saw that it was approaching James Potter levels of untidiness.

“This is ridiculous,” he huffed aloud to his empty flat. He was going to get out of his winter clothes, reheat some dinner, have a spectacular wank in the shower while thinking about the heat of Sirius’s eyes on his bare back, curl up in bed, and sleep this whole thing off. Sirius would text him something stupid in the morning, Remus would hold himself together as he got the tattoo done, and they’d go back to the way they were. No harm done.

He had almost reached the fridge, scarf in hand and jacket half-unbuttoned, when he stopped dead in his tracks. Lying on the table, folded but clearly visible, was the note Sirius had written Remus to include in his Christmas gift. Remus stared hard at it—his resolve cracked. He picked it up and read the neatly scrawled words for the hundredth time, running the pad of his thumb over the ink like he had over Sirius’s cheek. His resolve shattered at his feet.

Remus threw his scarf back around his neck and grabbed his keys, doing up his coat as he hurried over to his bike. It was dark, but the roads were clear of ice or snow—besides, he knew the route so well it was just a matter of muscle memory. Which was lucky for him, distracted as he was with his pounding heart and spinning head that was full of nothing except a frantic refrain of Sirius, Sirius, Sirius .

If he’d been paying more attention, Remus would have noticed he’d made record time getting to Fedelius Flowers from his flat. As it was, though, he was totally unaware of how long the journey had taken him; he didn’t check the time before he left or after he arrived. All he knew was he’d pedaled as fast as his legs would allow. He threw his bike against the side of his shop and strode over to Black Dog Tattoos, looking in the windows. To his dismay, the lights were off and the door was locked. Remus swore under his breath, on the verge of feeling supremely stupid for the stunt he’d just pulled when, out of the corner of his eye, he noticed something sleek and black in the parking space out front—Sirius’s motorbike, shining under the glow of an overhead lamp post.

His heart leapt. He ran around back, taking the stairs two at a time and firmly ignoring the protesting burn of his thighs. He’d already knocked before his head cleared enough for him to start panicking. There were a thousand ways this could go wrong, but he needed to see Sirius, he needed to know —

The door opened and Remus was suddenly standing face to face with Sirius, still dressed with his hair tied up from working. Sirius’s look of confusion turned into plain surprise as he saw who’d knocked.

“Remus?” he said. “What—?”

And right there on Sirius’s doorstep as the February wind blew into the flat, Remus closed the distance between them, cupping the sides of Sirius’s face and kissing him hard on the mouth.

For a brief moment, Sirius was frozen against him. Remus opened his eyes and was about to pull back, dread lurching in his stomach, when he felt Sirius’s body spring into action, his arms coming up to wrap around Remus’s waist as he kissed him back soundly.

Remus let out a soft, involuntary noise into the kiss, half out of desperation, and closed his eyes again as Sirius’s lips worked against his: pulling, pushing, prying, applying the perfect amount of pressure to keep it gentle but meaningful. When they broke apart, they stared at each other for a moment, both of them breathing hard. Sirius’s kiss-red lips spread into a wide, disbelieving grin.

“I can’t believe I didn’t get to kiss you first,” he finally murmured. “You bastard . Always outdoing me.”

That smile and the low pitch of Sirius’s voice sent a shiver of want all the way down Remus’s spine as he tried to commit the sight to memory. He beamed at Sirius, his cheeks flushed pink as he slid his hands down to rest on Sirius’s shoulders. All his nerves were alight with sheer pleasure—he never wanted to be farther apart from Sirius than he was right now. He couldn’t believe he’d gone so long without knowing what this felt like.

“Shut up,” Remus said, bumping his nose playfully against Sirius’s. “And keep kissing me, Sirius Black.”

Sirius was quick to comply. They stumbled through the threshold and into the warmth of the flat, Remus kicking the door shut behind them without breaking their embrace.

Remus’s lips were quietly demanding against Sirius’s own, and when the kiss deepened to include teeth and tongues as well as lips, Remus’s toes honest-to-god curled in his shoes. Sirius pushed his hands up into Remus’s curls and Remus knew he was done for. Licking his way into Sirius’s mouth, he decided he didn’t care. There was freedom in this kind of surrender.

“You,” Remus gasped against Sirius’s lips after an eternity, freeing his hands so he could undo Sirius’s bun and finally run his fingers through the long, dark hair, “are so fucking beautiful.”

Remus’s head tipped back helplessly as Sirius tilted his head to work his lips along his jawline. His kisses were hot, wet, open-mouthed, and when he reached Remus’s ear, he breathed into it. “I’ve been waiting for you to say that for months, handsome.”

Jesus. That voice whispering in his ear was something Remus knew he’d never, ever get used to. His hands slid out of Sirius’s hair to find purchase on his waist, holding him steady (or maybe steadying himself). He laughed breathlessly, turning his face to press his lips to Sirius’s temple. “Been wanting to tell you for months,” he said, giddy with the raw honesty of it.

Remus felt his stomach flip as Sirius gave a soft hum and dragged the pad of his index finger from the tip of Remus’s nose down to his parted mouth. “Such pretty lips,” Sirius mumbled, then leaned in to kiss them sweetly once, then twice, then a third time with more push behind it. Remus could feel the warmth of Sirius’s skin radiating through his t-shirt and it made his chest ache, made him want more heat, more pressure, more skin.

As though Sirius had read his mind, he pulled just far enough away to grin breathlessly at him, tugging on his coat. “I liked this better when you were shirtless.”

Remus kissed him again, hard, as though he couldn’t help it. He opened his darkened eyes slowly so their gazes met. “You’d better take me to your bedroom, then, yeah?”

Sirius pulled back a bit farther to really look at him. “You want that?” he asked, still close enough that Remus could feel his breath against his skin. Remus was being kissed before he could answer—a long, slow drag of tongues that sent heat spiking through him. The grip Remus had on Sirius’s hips tightened and he bit back a loud gasp as Sirius rolled his hips experimentally against his.

When the kiss ended, Sirius pressed his forehead to Remus’s and asked again. “You want to…?”

A part of Remus wanted to laugh, roll his eyes and say of course I want this, you can feel how much against your bloody thigh right now , but those gray eyes were wide open and searching and Remus heard himself say instead, quiet but sure, “Yes.” He brushed feather-light kisses across the bridge of Sirius’s nose, thumbs resuming their circular slide over Sirius's hipbones. “If you want to, yes. I...I’ve wanted this for a while now. You.”

Sirius rolled his hips again, biting his lip as Remus held him close. “Yeah,” he murmured, pushing a hand through his own hair get the long strands out of his face. “God, I want it,” he added with a breathless laugh, then stole one last kiss before pulling away completely.

Remus blinked stupidly as Sirius took a few steps backwards, a smirk tugging at his lips as his hands went to the hem of his t-shirt. He pulled it off slowly and Remus felt the breath punch out of his lungs. He’d never seen so much of Sirius’s body before—his eyes raked over his broad shoulders, the lean muscles of his chest and abs, the obscene v-shaped cut of his hips, and the tattoos . They were everywhere, winding and caressing over Sirius’s skin. Remus wanted to catalog every dot of ink with his fingers and then again with his mouth.

Remus was helpless but to follow—his feet carried him to Sirius as though magnetized. He skated his hands down Sirius’s chest as he stared at the intricate designs. “God, you...these are.” He swallowed, laughed, pushing a hand through his curls as he met Sirius’s gaze. “I want to know the story behind all of these. But...maybe not just now.”

“Another time,” Sirius promised softly, unwinding the scarf from around Remus’s neck. “I’ll tell you everything,” he pushed Remus’s jacket off his shoulders, throwing it over a nearby chair, “another time.”

As Remus watched him walk off in the direction of the bedroom, he made the same promise to himself: later, after, he was going to tell Sirius everything. He was going to make them tea and toast in the morning, bring it into bed to eat while tucked up against Sirius’s side. He was going to do the same thing the next morning, and the next. One morning, Remus would tell him about the scars, about the accident, even about Michael. He was going to let Sirius love him; he was going to let himself love Sirius back.

He smiled as Sirius reached the end of the hall and turned to face him. “Come on, then,” Sirius teased, his voice low and full of promise. “You’re falling behind.”

Remus was in Sirius’s arms before he could say anything more.

\newpage

%Epilogue I
\fancychapter{Epilogue I}{Our boys, one(-ish) year later.}

IT’S HARRY WHO SPOTS THEM FIRST.

“Hi!” he shrieks excitedly, tearing barefoot through the garden as fast as his little legs can carry him. He barrels straight into Sirius, who lets out an oof as he’s almost knocked out of his crouching position (otherwise known as his Harry-Catching Stance).

“Hang on, who’s this?” Sirius says, keeping hold of Harry’s shoulders as he pulls back to scrutinize the little face in front of him. “I don’t remember someone so tall living here. How old are you, kid? Sixteen? Twenty-five?”

“It’s Harry,” the toddler says, planting his hands on his hips in a frighteningly good imitation of his mother. “I’m three!”

Sirius hums and tilts his head to one side, then the other, as if weighing the truth of his godson’s claim. It’s only another moment before he breaks into a wide grin and gathers Harry up in his arms for another hug.

“Ah! Course you are, silly me.”

It’s a scene Remus has gotten used to over the past year—Sirius’s awful dad jokes, Harry’s squeals of laughter—but the swell of fondness he feels as he watches them is just as strong every time. It still takes his breath away, just how much he loves this man.

Remus kneels beside Sirius to ruffle Harry’s hair, which is already mussed beyond redemption. “Hello, Harry. Are you having fun?”

“Yeah. We’re playing superheroes!” Harry looks this way and that, and Remus sees him find a group of children with his eyes. Remus squints, looking harder, and makes out the ginger heads of Ron and Ginny. (Remus has no idea how many kids Lily and James’s neighbors actually have—he’s never seen all the Weasleys at once—but he knows Ron is Harry’s best friend and Ginny is the only girl among many, many brothers.)

Harry runs off after another minute to rejoin his playmates, and Sirius smoothly gets to his feet, offering a hand to Remus. His fingers linger against Remus’s after they’re both standing, and his smile is one step away from an outright leer.

“Don’t start,” Remus warns, trying to sound stern as Sirius presses a slow kiss to the hollow of his sun-warmed throat. His eyes flutter closed at how good it feels, how full of promise, but he’s determined to make his point. “There must be fifty people here, Padfoot, including your parents.” Fleamont and Euphemia have been nothing but effusively, aggressively kind to him since he and Sirius first paid them a visit as a couple, but he’s not sure how well they’d take to seeing Remus pawing at one of their sons in the middle of their garden during their daughter-in-law’s baby shower.

Sirius kisses a trail up to Remus’s Adam’s apple before pulling back. They aren’t touching anymore, but his eyes rake slowly over Remus from head to toe and back again. “Can they really blame me, though, when you’re wearing that?”

“Wh—it’s just a shirt and trousers, Sirius, I—”

Sirius just smiles, wide enough to make Remus’s heart flip. “You look positively edible, Remus.”

Flustered, Remus opens his mouth as he tries to form a response. He’s torn between emphasizing that, although he’s wearing the nicest button-down he owns for the occasion, it really is just a shirt and trousers, and turning the compliment back on Sirius—because honestly, has he seen himself?

“Hm, well, I try,” Sirius says, sounding more than a bit pleased with himself as he adjusts the dark blazer layered over his t-shirt, and it’s only then that Remus realizes he’s said that last part out loud. Smug bastard, he thinks fondly. Smug, hot bastard who really should not be allowed to wear that outfit and those earrings and have his hair up all at once. It’s extremely distracting.

James’s voice snaps Remus out of his train of thought. “Oi, you two! Quit snogging and join the party!” he teases, hands in his pockets as he ambles across the lawn to greet them.

His brown skin is flushed from an afternoon of May sunshine and he’s practically beaming as he pulls each of them into a hug, and Remus feels a wave of fondness for this man who’s so obviously thrilled that his family is expanding. They deserve it, James and Lily, Remus thinks as he receives a jovial thump to the back. Harry’s such a great kid, after all—he can see why they’d want more.

“What’s new, lads?” James says even though it can’t be more than a week since he’s seen them last. He eyes Remus up. “Sirius finish that rib piece for you yet, Moony?”

As it turns out, Remus quite likes getting tattoos. He doesn’t think he’ll ever be as covered in them as Sirius is, but after Sirius had finished the flower-filled crescent moon on his back—earning him the “Moony” moniker from James, who’d decided he absolutely must have a name like Prongs and Padfoot—Remus found himself dreaming up ideas for other scars. He has a few daffodils tied together at the stems on his left thigh, and Sirius is working on a constellation along Remus’s ribcage. Canis Major.

“Line work’s done,” Remus says, running his fingers along his side briefly. “Now it’s just a matter of finding time to sit down and have it colored.”

Things are a bit of a blur after that. James leads Remus and Sirius along the side of his parents’ house (well, mansion, really) through their extensive garden, where dozens of friends and relatives are gathered at tables and near a food and drink spread that could feed triple the number of people there. Remus ends up with a plate of sandwiches forced lovingly onto him by Euphemia and Fleamont and a red smudge on his cheek after a lipsticked kiss from Andromeda. He says hello to her and Ted, the Prewett brothers, and Molly Weasley, who cheerily tells him she’s only on the hook for two children today, as Arthur’s home with the others.

He’s happy to see Peter and Mary chatting with Marlene and Dorcas by the punch bowl. He still feels vaguely guilty for using the open invitation from the Potters to bring along whomever he liked to this party, but he knows if he hadn’t, Euphemia wouldn’t have let him hear the end of it. It’s something he’s still getting used to, this immediate and wholehearted acceptance from Sirius’s family; he often feels undeserving of their love for him, overwhelmed by the sheer ferocity of it all.

He’d said as much to Alice once, months ago, and she’d succinctly told him he was being an idiot. (“You love Sirius, don’t you?” she asked as they stocked shelves before the shop opened for the day. He said yes without hesitation. “And you love his family?” she asked. He said yes again, and she nodded, spreading her hands in front of her like he’d missed something obvious. “There’s your answer, Re. You adore them—why shouldn’t they feel the same for you?”)

It takes a while, but they finally do reach Lily, who’s sitting on a bench with flowers strewn into her long hair. She looks radiant in a yellow sundress, her hands folded and resting on her belly. She presses a kiss to Sirius’s cheek, then Remus’s, laughing as she swipes a thumb over the mark Andy’s lipstick left on his skin.

“You better not have brought something,” she says, narrowing her eyes playfully at them. Even Remus isn’t completely sure how many baby gifts Sirius has snuck into the Potters’ flat over the past few weeks—only that it was enough to warrant a ban.

“I’m empty-handed,” Sirius declares, raising his hands to emphasize the point. “The pony doesn’t come ‘til next Saturday.”

Remus sighs, rubbing his temple. “I want to believe you’re joking, but…”

“Re, Sirius, hey!” Remus turns around and smiles as he sees Alice and Frank heading their way. They greet Lily warmly, setting their gift down in the massive pile at Lily’s feet.

“Thank you so much for having us,” Alice says to her. “This is absolutely lovely.”

“Neville’s thrilled to meet a new group of kids his age,” Frank adds, and Remus glances over to see four toddlers racing each other in the grass.

After a few minutes, Remus puts a hand on Alice’s elbow. “Can I borrow you a moment?” he asks. They leave James and Frank deep in football conversation and Sirius tucked up on the bench, chatting to Lily as she idly braids flowers into his hair.

They move to a quiet spot on the edge of the garden, and Alice cocks her head at him, brow furrowed. “What’s up?”

Remus has been thinking it over for a while, this conversation. He knows it’s what he wants—he just hopes Alice wants it, too. “Has the school set a date yet?” he asks.

“They did, finally. It’s next month—the sixteenth.” Alice’s expression turns suspicious. “Why, what are you planning?”

“Baked goods, obviously.”

“Aren’t you busy making your almond fudge for Lily, like, once a week? Or has she moved on to a new craving?”

“She’s still on the fudge, but that’s not the point.” Alice can be stubborn about letting Remus do nice things for her, but he can be stubborn, too. “I’m making you a cake. You’re graduating, and that warrants a cake.”

“I am, aren’t I? Yeah, alright, cake.” Alice smiles like she can’t help it, and Remus feels a swell of pride for her. She’s worked so hard for this, he thinks, and for so long, and in a few short weeks, she’ll be holding her diploma.

He clears his throat, looking off at the rest of the party as he chooses his next words. “It’ll be good to have one person in the shop who’s actually studied business management.”

Alice laughs. “Thank you. But don’t sell yourself short, you’ve managed things well enough without one.”

“About that.” Remus looks back at Alice, meeting her gaze. “Having your degree, it’ll open a lot of doors, and I’d understand if you want to move on to bigger things.”

“Remus...” Alice starts, frowning.

“But,” Remus continues before she can protest, “But. If you find yourself wanting to stay where you are...there’s no better person I could ask to run Fedelius with me than you.”

Alice’s blue eyes go wide as she processes what he’s said. “Remus. Do you mean…?”

A slow smile spreads over Remus’s face as he nods. “You’d be co-owner of the shop, and my full business partner. If that’s something you’d want.”

The breath is knocked out of his lungs as Alice throws her arms around him in a fierce hug. “Whoa, hey,” Remus laughs, patting her back. When she doesn’t move away, he asks softly, “Alright?”

When she finally steps back, her eyelashes are wet, but she’s smiling. Remus doesn’t expect the punch to the arm, and lets out a surprised “ow!” as she dabs at her cheeks with the sleeve of her blouse.

“How can you think I’d want to get another job?” she chides. “You idiot.”

“It’s not an insane notion,” Remus says, rubbing his arm.

But Alice shakes her head at him like he’s just suggested she join the circus. “Yes, it is,” she says. Then she beams at him. “Of course, Remus! Of course. I don’t know how to tha—”

“Don’t thank me yet,” Remus cuts in, smiling back at her. “You’re in charge of hiring a new salesperson.” He doesn’t want her thinking it’s a favor when it isn’t. There isn’t anyone more qualified for this than Alice; she’s been keeping the place running for years.

“Deal,” Alice says, laughing, and gives his shoulder a squeeze before they make their way back to the party.

He’s surveying the desserts at the end of the buffet table when he feels a pair of familiar arms snake around his waist. “Hi, lovely,” Sirius hums, pressing his lips to the sensitive skin below Remus’s ear, and Remus forgets all about the tray of eclairs. He sighs at the kiss, scraping his nails lightly up and down Sirius’s forearm. “She took it, didn’t she?”

“Yeah, she did,” Remus says, leaning back against Sirius’s warm chest. He has his chin hooked over Remus’s shoulder, and Remus pulls a couple of daisy petals out from his hair.

Sirius hums, his cheek catching against the stubble at Remus’s jaw as he speaks. “Knew she would.” He sounds every bit as confident as he had every time Remus brought up the idea to him over the past month. Remus sighs, closing his eyes for a moment and letting himself be held. He snaps out of it when Sirius continues, “I have something to ask you, actually, now that you aren’t panicking about Alice quitting on you.”

“I wasn’t panicking,” Remus lies, turning in Sirius’s arms to look at him properly. Sirius just grins at him, cocking an eyebrow. “I was...marginally concerned. Anyway. What is it?”

“Not here,” he says in lieu of explanation. Remus frowns at that—is something wrong?—but before he can really finish the thought, Sirius kisses him. “I’ll tell you when it’s just us. Back at mine. Yeah?”

He’s still slightly worried—what would make Sirius wait until they had privacy to say to him?—but he doesn’t push the issue. If Remus knows one thing about his boyfriend, it’s that he’s pants at hiding his feelings. He’s reasonably sure he’d know if Sirius had been sitting on bad news.

Remus puts the thought aside for the moment. “At yours, hm?” he teases. “I’ve got to say, I don’t think anyone’s tried to pick me up at a baby shower before.”

His stomach flips as Sirius laughs and crowds into his space again. A flower falls onto his shoulder as Sirius tilts his head, breathing into Remus’s ear. “I could drive you home instead, love, but we both know my bed’s bigger, and I plan to get you in it as soon as possible.”

Remus covers the noise he almost makes at that with a cough, stepping back to put a respectable distance between them. Sirius grins wickedly at him, and he knows his face has gone pink.

“You’re going to pay for that, you know.” He says it mildly, but they both know Remus always makes good on his promises.

Sirius licks his lips, his eyes alight. “Oh, I’m counting on it.”

It’s hours before Remus thinks about Sirius’s unasked question again. The sun is sinking fast on the horizon, its last golden rays peeking through the half-open slats on Sirius’s bedroom window. It’s the only light in the room; it joins the sounds of breathing and rustling sheets coming from inside and the more distant sounds of the city beyond. Remus lays his cheek on Sirius’s bare chest, listening to his slowing heartbeat, and remembers.

He makes himself ask before he gives in to the pull of sleep. “Weren’t you going to ask me something?”

Instead of answering, Sirius shifts so he can put his arms around Remus and kiss him, soft and slow. Remus loves him like this, warm and pliant in his post-coital haze, his lips bitten red and his hair a mess from Remus pulling at it. Remus pushes a few dark locks away from where they’re sticking to Sirius’s forehead, meeting hooded gray eyes with his own.

Sirius opens his mouth, then—hesitates, laughing quietly at himself and chewing at his bottom lip. Remus’s eyebrows raise, then furrow; was Sirius Black nervous? “Padfoot?”

“Sorry, I—fuck, this is stupid. I should just. Right,” Sirius huffs. He sits up, propping his back against the headboard, and Remus mirrors him. Remus tugs the sheet over his lower half, feeling exposed given the sudden change in mood. “So,” he starts, trailing off.

“Okay, you're freaking me out a bit, now.”

Sirius pushes his hair out of his eyes. “Dora,” he says suddenly.

Remus’s furrow deepens. “Dora?”

“Yeah, you know, my little cousin. Pink hair, foul mouth, main source of Andy’s stress?”

“Well, sure. I know her.” Remus has seen her once or twice in the shop, fluttering in after school to talk music with Sirius or explain away a detention to Andromeda. “Is she...okay?”

“She’s fine, yeah. She’s off to uni in the autumn—just got into this top criminology program.” Sirius grins. “Kind of hilarious, really, given what a little punk she is.” He slides a hand up Remus’s arm, then down his side, fingers tracing the cluster of stars he put there. “She told me she’s looking for a flat that’ll be closer to her classes.”

He gives Remus a one-shouldered shrug, but isn’t quite meeting his eyes anymore. “The lease on this place is up in a few months, and it’s the right size for her, if she can stand living above her mum’s shop.”

Remus is very awake now.

“You’re going to move,” he says with a sinking feeling in his gut. They’d fallen into such an easy rhythm over the past year: Remus would pack an overnight bag and take it into work in the morning, meeting Sirius next door at the end of the day and walking up to his flat together. These days, he doesn’t even need a bag most of the time; Sirius’s bedroom drawers are full of Remus’s clothes, and he can’t even remember how long ago the spare toothbrush appeared in Sirius’s bathroom and stayed there. He knows that, realistically, Sirius won’t be moving too far—the shop’s staying put, after all. But he still hates the idea of putting more distance between them.

Sirius’s thumb tracing his cheekbone brings Remus’s focus back to the conversation. “We’re going to move,” he says. He still sounds nervous, but he’s looking right at Remus and giving him a small, hopeful smile. “We’ll find a new place, a bigger place—somewhere with enough room for all your dusty old books. If you want."

Oh. Oh.

Remus kisses him hard, threading his fingers through Sirius's hair as his chest swells. Sirius...wants to move in with him. He wants them to live together. Remus feels dizzy with the sudden rush of joy he's feeling at the very idea. He laughs against Sirius’s lips, releasing some pent-up nervous energy.

Sirius pulls back just far enough to search Remus's eyes. “Okay, that wasn’t a, 'Fuck off, Sirius, you’re mad if you think I want to see your face every day.'"

"I already see you every day, you git." Remus's smile is stupidly wide, but he doesn't care, couldn't help it even if he wanted to.

“You know what I mean, Lupin.”

“Yeah. I…” Remus swallows, raking a hand through his curls. “You want to see me every day?” Remus wants to say yes—he wants to say yes so badly—but part of him can’t quite believe this is what Sirius wants, too.

Sirius raises an eyebrow at him. His hands are steady on Remus's back, keeping him close. "I think I just asked you for that, yeah."

Remus makes himself drag the fear out from the back of his throat and name it. “What if you get sick of me?” he asks, quietly.

Sirius huffs out a small laugh, brushing the pad of his thumb very gently across Remus's bottom lip. "I really don't think that's gonna happen, Moons. But if you don't want to, that's...fine, obviously. I can find a flat nearby."

Remus's reply is immediate. "No."

"No?"

"I don't want you to find your own place," Remus says, because it's true. He knows what he wants; he just needs to shove his fear aside long enough to voice it. He lays his hands flat on Sirius's chest, feeling the reassuring thump of his heartbeat under his palms as he focuses on his love and lets his doubt fall away. "I want to be with you."

It's Sirius's turn to kiss him. Remus is breathless with it, winding his arms around Sirius's neck as he closes his eyes and gives himself to the embrace, trying to pour everything he's feeling into the way he's kissing Sirius back. He thinks about how good Sirius always looks in the morning, his hair a tousled mess and his skin so warm under Remus's fingers. He thinks about their lazy showers and takeaway dinners and records playing at half past midnight. He thinks about their kisses: quick and cheerful as a greeting in the shops, hungry and biting while stripping off clothes and pressing each other into the mattress, soft and slow in between apologies after an argument. He wants to keep kissing Sirius for the rest of his life, and that's enormous and terrifying, but it's also right, and true, and wonderful.

"I love you," Sirius says at last, breathing it against Remus's lips.

"I love you, too."

"Live with me."

Remus smiles, kissing the corner of Sirius's mouth. "Yes."

The sun sets outside the four walls of the bedroom, but Remus can see the flash of Sirius's teeth as he beams before leaning in to kiss him again.

\newpage

%Epilogue II
\fancychapter{15 February}{After a kid-filled trip to the zoo and far too many scoops of ice cream, Remus and Sirius discuss their future. It looks a lot like their present.}


“UNCLE MOONY,” Harry shouted from his perch atop Sirius’s shoulders, his wide smile showing off the space where he was missing a front tooth. “Hi!”

Remus walked through the zoo’s entrance and picked up a map before making his way over to where Sirius was waiting for him. Sirius had one hand on Harry’s leg to steady him and the other pushing a pram, but he looked happy and relaxed as he tilted his head up to greet Remus with a kiss.

“Hi, love,” Remus said, kissing him back. “Hi, Harry.”

A tiny, round face framed by dark curls popped up from the depths of the pram. “Moo!”

Remus crouched down to meet the two-year-old’s eyes. “And hello, Emily, I haven’t forgotten about you.”

It was late summer, and London felt more like the tropics, the air thick and the pavement shimmering. All around them, locals and tourists of all ages fanned themselves with their folded maps, white streaks of sunscreen visible on their skin. Remus hated the heat but was riding the high of a precious two-week holiday; it had taken Sirius ages to convince him to take so much time off, even recruiting Alice to double down on the persuasion, but in the end, Remus was infinitely grateful for his boyfriend’s stubbornness.

“You were right,” he said as he took over pram duty, leading them toward the reptile house. “We needed this.”

Sirius just smiled at him, readjusting Harry on his shoulders as they walked. “You don’t have to keep saying that. But hey, I’m not complaining. Could get used to a daily dose of ‘You were right, Sirius. You’re a genius.’”

Remus quirked an eyebrow as he cast a sidelong glance at Sirius. “I don’t recall ever saying that last part,” he said, but he was smiling, too. He felt lighter and calmer than he had in months, even saddled with Potter babies as he was. He knew Sirius felt the same way, could see it in the bounce in his step, the twinkle in his eyes. He was pulled out of his thoughts when Emily chucked her doll onto the floor and promptly started wailing to have it back. “Okay, let’s find some nice, scaly creatures to distract you, Em,” Remus said as he bent to rescue Astronaut Barbie from becoming a full-time resident of the London Zoo.

There was minimal chaos after that, to Remus’s pleasant surprise. Emily wasn’t a fan of the reptiles, but Harry had a grand old time saying hello to the snakes; it could have been the heat getting the better of him, but Remus swore the pythons and cobras were watching the little boy as closely as he was watching them. Harry was less of a fish fan, but his sister was mesmerized by them as they swam past her wide eyes. All of them loved the big cat enclosure. Sirius wound up roaring on demand for the duration of their walk back to the exit, getting more and more into it each time, which sent the kids into fits.

“That was the funnest day ever,” Harry declared as he jabbed a spoon into a cup of banana ice cream, a newly purchased stuffed lion resting on his lap.

“What, really?” Sirius said, raising his eyebrows as he pulled a high chair over to their (blessedly shaded) cafe table and got Emily and her new dolphin plushie comfortable in it. “Even more fun than the day we drove out to the beach with your mum and dad?”

Harry’s dark brows drew together on his face as he considered this. “That was the funnest, too,” he said after a moment. “But Uncle Moony got sunburn and you called him a lobster!”

“I got no sympathy from Uncle Padfoot that day, you’re right,” Remus said, shaking his head. Sirius dove in for a lick of his double-chocolate cone, but Remus pulled it out of reach, nudging him away with his foot. “Nope, eat your own. This is too good to share.”

Sirius sat down with an affected air that made Harry giggle. “Do you see how horrible he is to me?” he groused to the kids. He ate an enormous spoonful of his coffee-flavored scoop before feeding Emily a bite of her vanilla. “Sharing is caring, Moons. And I rubbed aloe all over you once we got home, if memory serves.”

The tips of Remus’s ears went red and he shot Sirius his not-in-front-of-the-kids look, but before he could reply, an elderly woman walked over to their table. “Excuse me,” she said with a kind smile. “I don’t mean to interrupt, but I wanted to say that you have a beautiful family.”

Remus blinked in surprise, following her gaze across the table to where Sirius was fitting his dark sunglasses over Harry’s too-small ears to make him laugh, Emily kicking her feet happily beside him and offering her dolphin a fistful of melting ice cream. He realized what they must look like in the absence of Lily, whose green eyes were identical to her kids’, and James, whom Harry was the spitting image of in every other way.

Sirius just grinned broadly at the woman, leaning back with an arm around Harry’s chair. “Thank you,” he said with no intention of correcting her assumption, apparently, and Remus—Remus didn’t know how he felt about that, but it flustered him enough that he hadn’t found his voice yet as the woman continued.

“You remind me of my grandson and his husband,” she said, looking down fondly at Remus. “They keep promising me grandchildren. Oh, look at these little dears. How old is the baby?”

Remus, even more flustered than a moment ago, glanced over at Sirius. His expression didn’t falter. “Year and a half,” he replied easily. “Got quite the inner teenager, though. She’ll be sneaking out of the house and stealing the car soon, won’t you, Doe?” As if emphasizing her godfather’s point, Emily grabbed Sirius’s keys off the table and shook them, making everyone laugh.

The woman bid them goodbye after another minute. Remus’s heart was still pounding crazily in his chest as he gathered their spoons and napkins and took them to the bin. Husband, he thought as he pushed the lid open and tipped his trash inside. She thought that he was my husband. That those were our kids.

The word was still repeating itself in his mind as he walked back over to the table, where Sirius had cleaned up the kids and had Emily fastened into her pram seat. They were all looking at Remus, and Harry held out his hand, and Remus drew in a sharp breath, momentarily overwhelmed. He smiled down at Harry after a second’s pause and took his hand, but as they started to walk, he realized Sirius was still looking at him. He was smiling a little, but he had a puzzled expression, his head cocked slightly to the side and a crease between his brows.

“Okay?” he asked softly as they made their way down the sidewalk.

“Yeah, I’m fine,” Remus said. He gave Sirius’s hand a brief squeeze with the one not holding Harry’s, which smoothed the worry out of his boyfriend’s face. “Really, Pads.”

After they’d dropped Harry and Emily off to their exceedingly grateful parents and washed the sweat and sunscreen off themselves, they ended up lounging half-dressed on their bed, Sirius editing some social media posts for the parlor while Remus worked on his latest crossword. That’s what he intended to do, anyway, but he found himself unable to stay focused on the puzzle in front of him. His mind kept going back to earlier that day at the cafe, what that woman had said. What Sirius had said, and what he hadn’t.

A foot nudging his ribs snapped him back to the present. He looked over at Sirius, who was watching him with that same sort of puzzled fondness from before.

“Oi,” he said softly. “Penny for your thoughts?”

“Hm?” Remus said, still a little distracted. “Oh. Just, ah, crossword. Tough one.”

Sirius raised an eyebrow. “You’ve been staring into space for the last five minutes.”

“Really tough one.”

Sirius fixed him with a look that let Remus know he wasn’t getting out of this that easily. He shut his laptop and twisted so he could set it on the nightstand. “Right, come on,” he said, holding an arm up. “C’mere.”

Abandoning his crossword at the edge of the bed, Remus settled into the space beside Sirius, the other man’s arm coming down around his shoulders. Sirius’s fingers stroked lightly over his bare skin, and Remus relaxed into it, closing his eyes and sighing. A long few moments passed like this, Sirius’s gentle touches unwinding Remus’s body and slowing his mind, until finally Sirius murmured, “Want to tell me what you’ve been thinking about?”

Remus let out a disgruntled noise as the spell of silence in the room was broken—Sirius knew just where to touch him with just the right pressure, he’d been just on the edge of sleep—but he opened his eyes to meet Sirius’s. “It’s nothing,” he said, but Sirius didn’t reply, watching him skeptically. “No, really. Just—earlier, when we got ice cream. That grandmother thought we were a family.”

“Oh,” Sirius said, sounding surprised. “Yeah. She was sweet.”

“She was,” Remus agreed. A few seconds ticked by before he added quietly, “You didn’t correct her.”

Sirius looked even more surprised at that. “Well...no,” he answered slowly. “I mean, we sort of are, right? Not quite the way she was thinking, but.” He searched Remus’s face, the crease in his brow making a reappearance. His voice was more careful when he said, “Should I have?”

“No,” Remus said quickly, sitting up and facing Sirius with his legs tucked under himself. Sirius followed suit, his back against the headboard. He looked less than reassured. “No, it’s fine that you didn’t.”

“You sure about that?” Sirius was frowning now, and there was something guarded in his eyes that Remus wanted to fix immediately. “Because you seem...I don’t know. You’re doing that thing when you want to tell me something, but you’re overthinking it so it just seems like you’re freaking out.”

"I’m not freaking out.” Remus ignored the quickening of his pulse that said otherwise. “I sort of did, earlier, but not in a bad way. I don't think."

“Now I’m freaked out.”

Remus raked a hand through his still-damp curls, exasperated with himself. Why was this scaring him so much? He took a deep breath, willing his brain to catch up with his mouth. “Sorry. Just...words are hard right now, for some reason.”

He took another deep breath in, let it out slowly. Sirius reached out and started tracing the lines of a tattoo between Remus’s knee and the hem of his boxers, his fingers gentle, comforting. His eyes were on Remus’s own, hot-bright with equal parts concern and an open, honest love that made Remus’s breath catch.

“Oh,” he breathed, realizing with sudden clarity that he wasn’t afraid of Sirius being his husband, of raising children together. He brought his hands up to cup Sirius’s face, closing the distance between them with a slow kiss. For a split-second, Sirius hesitated, hands unsure on Remus’s hips, but Remus kissed him with steady pressure, still nervous but no longer confused about what he was feeling. Sirius melted into it, gave over to it, and Remus sighed in relief, pressing his lips to Sirius’s one last time before pulling back to look at him.

“I was freaked out today, when we were called a family. When you were called my husband,” Remus admitted. Sirius stiffened, but Remus stroked his hands down Sirius’s shoulders soothingly. “It took me a while to work out why. It scared me because I realized I want that. I really want that.” He licked his suddenly dry lips, his gaze falling to the ruby-studded locket against Sirius’s breastbone. “So much so that I can’t imagine what my life would look like without it. You and me, Harry and Emily, and—and kids of our own.”

He waited for Sirius’s response. When nothing came, he looked up, a trickle of panic running through him. Had he ruined it?

Sirius’s eyes were wide, his lips parted. And then—a smile tugged at the corners of his mouth, slowly spreading until it lit up his entire face.

“Remus Lupin,” he said incredulously. “Did you just propose to me?”

“I—” Remus stammered, hands faltering where they were still petting over Sirius’s shoulders. “I don’t have a—a ring or anything, but is that—would you—?”

He cut himself off with a rather undignified noise as Sirius pounced on him, pinning Remus flat against the mattress and kissing him within an inch of his life. When he pulled back, he was laughing, breathing hard. “Ask me,” he said, catching Remus’s hands where they lay above his head, lacing their fingers together. “Ask me again, Moons.”

Remus’s heart leapt, and his voice was sure this time as he said, “Will you marry me, Sirius Black?”

Sirius bit his lip, still beaming, and squeezed Remus’s hands. “Yeah, I really fucking will,” he said in a rush of breath before kissing Remus again soundly.

The evening dissolved into a hazy blur as they shed the rest of their clothes, both desperate to be close, skin against skin. When they were finally connected, Remus buried himself deep inside Sirius, their bodies pressed as closely together as possible. A choked half-sob wrenched its way out of Remus's chest as he lost himself in the other man completely.

Pressed together like this, they moved like they’d known each other for a hundred lifetimes and would do this dance for a hundred more. Remus moaned deeply at the joining of it. The belonging of it. At the wonder of knowing this was precisely where he belonged—who he belonged to. At the world of possibilities unfurling behind his eyes as he thought of his future, their future together. The feeling of it like wind rushing through his hair as he and Sirius streaked through the city at midnight, his laughter and the bike’s engine roaring in his ears.

“Love you, husband,” Sirius whispered. It was that more than anything that sent Remus careening over the edge. His fingernails dug into Sirius’s thighs as he started to come, ten little half-moons bitten into his skin. He rocked forward, Sirius meeting him with shallow thrusts of his own as they worked through it, coming undone in each other’s arms.

He held Sirius’s flushed, sweat-slick body tightly against him through the aftershocks, not quite ready to pull out or away. Sirius groaned as he pumped the last of his climax between them, their stomachs a mess, their skin damp, their hair tangled in knots. It was perfect. Sirius was perfect, and Remus couldn't have stopped the breathless "I love you" from leaving his lips if he tried. He nuzzled Sirius’s temple, brushing strands of dark hair back from his forehead with a gentle, shaky hand.

The kiss he pressed against Sirius’s mouth was sloppy, uncoordinated, and at some point they gave up to just laugh against each other’s lips. "I love you," Sirius said, voice low and full of wonder. "Fuck, I love you so much, Remus. Since we met."

Remus hummed, blissed-out and drowsy and so full of love he could burst with it. He gathered Sirius in his arms, holding him close, and pressed his lips against the man’s temple. “We’re doing this, then? Getting married, having kids?”

“Mhm.” The sound left Sirius as a rumble of pleasure, almost a purr, and he stroked rhythmically along Remus’s arm, down and up. “Well. More kids. Don’t forget Riff and Magenta.”

“Oh, of course.”

“Human kids.”

“Exactly. Cousins for Em and Harry.”

Sirius buried his face against Remus’s neck at that, kissing the skin there. “Fuck,” he said, the sound muffled. “Yeah, I want that. James is gonna flip.”

Remus laughed, letting himself imagine it. All of it. He’d always known he wanted Sirius, loved him, but now that he could see the rest of their lives in his mind’s eye, he knew he’d do everything in his power to protect that future, to make it the happy one he knew it could be.

“I can’t wait,” he murmured, tracing along Sirius’s finger where a wedding band might be. He kissed the other man’s forehead, breathing him in. “I can’t wait.”
